### 2022-12-14 manuscript.Rmd
Preprocessing code added

---
title: "Uncanny Valley"
author: "Daniel Baker"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: yes
  word_document: default
  pdf_document:
    toc: no
  html_document: default
bibliography: references.bib
csl: elife.csl
---

```{r setup, include=FALSE}

processdata <- 3  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data (requires XMB of storage)
# 2 - perform multivariate pattern analysis on individual participants (requires 25GB of storage, and takes X hours)
# 3 - download all raw data and do preprocessing (requires ~60GB of storage)

niterations <- 100  # number of iterations for MVPA

# check which packages are installed, install the missing ones, and activate
packagelist <- c('knitr','e1071','signal','osfr') # list of CRAN packages
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

rawdir <- 'local/raw/'
rawdir <- '/Volumes/USB128/UncannyValley/'
processeddir <- 'local/processed/'
processeddir <- '/Volumes/USB128/UncannyValley/'

knitr::opts_chunk$set(echo = TRUE)
```

# Abstract

# Introduction

# Materials & Methods

## Participants

## Apparatus & stimuli

## Procedure

### Experiment 1: robots

### Experiment 2: hyper-realistic masks

## Data analysis

## Data and code availability

Raw data, processed data, and all analysis scripts are available through the project repository at: https://.

# Results

## Experiment 1

```{r include=FALSE, results='hide'}

# (download and) analyse individual participant data for experiment 1

if (processdata > 2){

  legaltriggers <- 101:103
  sublist <- dir(paste0(rawdir,'Robots'),full.names=FALSE)
  subdirs <- dir(paste0(rawdir,'Robots'),full.names=TRUE)

  for (s in 1:length(sublist)){

   if (!file.exists(paste0(processeddir,'RobotsP/R',s,'_processed.RData'))){
    datafiles <- dir(subdirs[s],pattern='*.csv.gz',full.names=TRUE)

    trialcounter <- legaltriggers*0
    alltrials <- array(0,dim=c(3,180,64,1200))
    for (block in 1:length(datafiles)){

      EEGdata <- read.csv(datafiles[block])
      electrodes <- colnames(EEGdata)[3:68]

      # bandpass filter data
      filt <- butter(10,1/16.666,type='low')
      for (ch in 1:66){
        temp <- EEGdata[,ch+2]
        ftemp <- signal::filter(filt,temp)
        EEGdata[,ch+2] <- ftemp
      }

    triggertimes <- NULL
    counter <- 0
    lasttrigger <- -10000
    for (n in 1:nrow(EEGdata)){
      if (EEGdata$Trigger[n] %in% legaltriggers){
        if (n>(lasttrigger+100)){
        counter <- counter + 1
        triggertimes[counter] <- n
        lasttrigger <- n
      }}
    }

    for (trial in 1:counter){
      thiscond <- which(legaltriggers==EEGdata$Trigger[triggertimes[trial]])
      trialcounter[thiscond] <- trialcounter[thiscond] + 1

      for (ch in 1:64){
       temp <- EEGdata[triggertimes[trial]+(-200:999),ch+2]
       temp <- temp - mean(temp[1:200])
       alltrials[thiscond,trialcounter[thiscond],ch,] <- temp
      }
    }

    }

    save(file=paste0(processeddir,'RobotsP/R',s,'_processed.RData'),list=c('trialcounter','alltrials'))
   }
  }

}

```

```{r include=FALSE, results='hide'}

# do MVPA for experiment 1

if (processdata > 1){

}

```

```{r include=FALSE, results='hide'}

# create figures for experiment 1

if (processdata > 0){

}

```

## Experiment 2

```{r include=FALSE, results='hide'}

# (download and) analyse individual participant data for experiment 2

if (processdata > 2){

  # 100: asian, 200: western
  # 11: halloween, 12: silicone, 23: real
  legaltriggers <- c(111,112,123,211,212,223)
  sublist <- dir(paste0(rawdir,'Masks'),full.names=FALSE)
  subdirs <- dir(paste0(rawdir,'Masks'),full.names=TRUE)

  for (s in 1:length(sublist)){

    if (!file.exists(paste0(processeddir,'MasksP/M',s,'_processed.RData'))){
    datafiles <- dir(subdirs[s],pattern='*.csv.gz',full.names=TRUE)

    trialcounter <- matrix(0,nrow=3,ncol=6)
    alltrials <- array(0,dim=c(3,6,76,64,1200))
    for (block in 1:3){

      EEGdata <- read.csv(datafiles[block])
      electrodes <- colnames(EEGdata)[3:68]

      # bandpass filter data
      filt <- butter(10,1/16.666,type='low')
      for (ch in 1:66){
        temp <- EEGdata[,ch+2]
        ftemp <- signal::filter(filt,temp)
        EEGdata[,ch+2] <- ftemp
      }

    triggertimes <- NULL
    counter <- 0
    lasttrigger <- -10000
    for (n in 1:nrow(EEGdata)){
      if (EEGdata$Trigger[n] %in% legaltriggers){
        if (n>(lasttrigger+100)){
        counter <- counter + 1
        triggertimes[counter] <- n
        lasttrigger <- n
      }}
    }

    for (trial in 1:counter){
      thiscond <- which(legaltriggers==EEGdata$Trigger[triggertimes[trial]])
      trialcounter[block,thiscond] <- trialcounter[block,thiscond] + 1

      for (ch in 1:64){
       temp <- EEGdata[triggertimes[trial]+(-200:999),ch+2]
       temp <- temp - mean(temp[1:200])
       alltrials[block,thiscond,trialcounter[block,thiscond],ch,] <- temp
      }
    }

    }

    save(file=paste0(processeddir,'MasksP/M',s,'_processed.RData'),list=c('trialcounter','alltrials'))
  }
  }
}

```

```{r include=FALSE, results='hide'}

# do MVPA for experiment 2

if (processdata > 1){

}

```

```{r include=FALSE, results='hide'}

# create figures for experiment 2

if (processdata > 0){

}

```

```{r pupildata, fig.cap="Caption.", fig.align="center", echo=FALSE}

# knitr::include_graphics(paste0('Figures/pupildata.pdf'))

```
# Discussion

# Conclusions

# Acknowledgements

# References

### 2023-02-01 manuscript.Rmd
Interim commit when switching computers

@@
 ---
-title: "Uncanny Valley"
-author: "Daniel Baker"
+title: |
+  | Neural correlates of the uncanny valley effect
+  | for robots and hyper-realistic masks 
+  | (for submission to Computers in Human Behavior)
+author: |
+  | Shona Fitzpatrick, Ailish K. Byrne, Alex Headley, Jet G. Sanders,
+  | Helen Petrie, Rob Jenkins & Daniel H. Baker
 date: "`r Sys.Date()`"
@@
 
-processdata <- 3  # this flag determines the amount of processing, with 4 levels:
+processdata <- 2  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
 # 1 - generate figures using the processed group data (requires XMB of storage)
+
 # 2 - perform multivariate pattern analysis on individual participants (requires 25GB of storage, and takes X hours)
 # 3 - download all raw data and do preprocessing (requires ~60GB of storage)
+niterations <- 50   # number of iterations for MVPA
+nsplits <- 5        # number of partitions of EEG trials
+dowhitening <- 1    # optionally pre-whiten the data for MVPA
 
-niterations <- 100  # number of iterations for MVPA
+nbootstraps <- 1000
+targetelectrodes <- c(28,54,58,64)
 
 # check which packages are installed, install the missing ones, and activate
-packagelist <- c('knitr','e1071','signal','osfr') # list of CRAN packages
+packagelist <- c('knitr','e1071','signal','osfr','tictoc','BayesFactor','reshape2','powerplus','R.matlab') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
@@
 rawdir <- '/Volumes/USB128/UncannyValley/'
-processeddir <- 'local/processed/'
-processeddir <- '/Volumes/USB128/UncannyValley/'
+processeddir <- 'local/RobotsProcessed/'
+# processeddir <- '/Volumes/USB128/UncannyValley/'
+
+if (!dir.exists('local/')){dir.create('local/')}
+if (!dir.exists('local/robotsmvpa/')){dir.create('local/robotsmvpa/')}
+if (!dir.exists('local/masksmvpa/')){dir.create('local/masksmvpa/')}
+
+collist <- c('red','green','blue')
+colfunc <- colorRampPalette(c("darkgreen", "darkblue"))
+colvect <- colfunc(29)
+addalpha <- function(col, alpha=1){apply(sapply(col, col2rgb)/255, 2, function(x) rgb(x[1], x[2], x[3], alpha=alpha))}
+
+getstartstop <- function(linestartstop){
+  xpairs <- matrix(0, nrow = 1200, ncol = 2)
+  paircounter <- 1
+  startval <- linestartstop[1]
+  lastval <- linestartstop[1]
+  for (n in 2:length(linestartstop)){
+    if ((linestartstop[n] - lastval) > 1){
+      xpairs[paircounter, ] <- c(startval, lastval)
+      startval <- linestartstop[n]
+      paircounter <- paircounter + 1
+    }
+    lastval <- linestartstop[n]
+  }
+  xpairs[paircounter,] <- c(startval,lastval)
+  xpairs <- xpairs[1:(paircounter+1),1:2]
+  return(xpairs)}
+
+# two functions used in prewhitening prior to MVPA
+# data must be in the format sensor x time x trials
+cov1para <- function(x){
+
+  s <- dim(x)
+  ti <- s[1]
+  n <- s[2]
+  meanx <- colMeans(x)
+  x <- x - matrix(rep(meanx,ti),nrow=ti,ncol=n,byrow=TRUE)
+
+  sample <- (1/ti)*(t(x)%*%x)
+
+  meanvar <- sum(diag(sample))/n
+  prior <- meanvar * diag(n)
+
+  y <- x^2
+  phiMat <- t(y) %*% y/ti - sample^2
+  phi <- sum(phiMat)
+
+  gamma <- sample - prior
+  gamma <- sum(gamma^2)
+
+  kappa <- phi/gamma
+  shrinkage <- max(0,min(1,kappa/ti))
+
+  sigma <- shrinkage * prior + (1-shrinkage) * sample
+
+  return(sigma)}
+
+whitenmatrix <- function(data,condid){
+
+  # set up variables
+  s <- dim(data)
+  nvar <- s[1]
+  ntimes <- s[2]
+  ncond <- max(condid)
+  Cov <- matrix(0,nrow=nvar,ncol=nvar)
+
+  # compute whitening matrix
+  for (cond in 1:ncond){
+    dat <- data[,,which(condid==cond)]
+    for (time in 1:ntimes){
+      sigma <- cov1para(t(dat[,time,]))
+      Cov <- Cov + sigma
+    }
+  }
+  Cov <- Cov/(ncond*ntimes)
+  W <- powerplus::Matpow(Cov,-0.5)
+return(W)}
 
 knitr::opts_chunk$set(echo = TRUE)
+
 ```
@@
 
+Many people report an aversion to entities that are human-like, but on closer inspection are actually artificial.
+Examples include humanoid robots (androids), puppets, realistic computer-generated images, and hyper-realistic masks.
+The term 'uncanny valley' [@Mori1970; English translation in @Mori2012] describes the idea that entities that are clearly human or clearly artificial do not evoke unease, whereas artificial entities that are human-like are disconcerting.
+Understanding these experiences is increasingly important as artificial entities become more integrated into our everyday lives, however at present relatively little is known about the neural underpinnings of the uncanny valley effect.
+
+Neural responses to faces and bodies in general are well-characterised, and there appear to be specialised brain regions devoted to both [reviewed in @Hu2020].
+For example, areas of the occipital lobe [@Gauthier2000] and fusiform gyrus [@Kanwisher1997] respond more to faces than non-face stimuli, and sections of extrastriate cortex are responsive to bodies [@Downing2001].
+There are also event-related potential (ERP) signals associated with face and body stimuli, though their precise purpose is still debated [@Thierry2007].
+It seems highly likely that 'uncanny' images will activate these same processes, yet it is unclear whether the sense of unease they produce occurs at bottom-up sensory stages, or is modulated by more top-down cognitive factors.
+
+One previous study has measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
+@Saygin2012 found repetition suppression effects in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
+These effects were stronger than for movies of humans or mechanical robots performing the same actions.
+A more recent electroencephalography (EEG) study [@Urgen2018] identified a difference in the N400 component between dynamic and static conditions using the same stimuli.
+Although this difference was strongest over frontal electrodes, source reconstruction of the N400 itself suggested a left-lateralised source in temporo-parietal cortex, consistent with the fMRI results [@Saygin2012].
+The authors interpret both of these findings as being due to the discrepancy between the human-like appearance and the clearly non-biological motion of the robot.
+
+Our aim here was to further investigate neural correlates of the uncanny valley effect.
+We achieve this through two EEG experiments, in which we measure neural responses to static images.
+In the first experiment, the stimuli were humans, machine-like robots, and human-like robots.
+In the second experiment we aimed to generalise the finding by using images of people wearing no masks, wearing obvious masks (e.g.
+carnival or halloween masks), and wearing hyper-realistic silicone masks [@Sanders2017].
+Rather than focus on specific ERP components, we use a non-parametric cluster correction procedure to compare conditions.
+We also apply a pattern classification approach to identify time windows in which information in the EEG signal can be used to distinguish between pairs of conditions.
+
 # Materials & Methods
@@
 
+A total of 29 participants completed Experiment 1 (12 male, 17 female), and 30 participants completed Experiment 2 (7 male, 23 female).
+None of the participants had previously taken part in a study using these stimuli, and all were naïve to the hypotheses and wore their normal optical correction if required.
+Written informed consent was collected before each experiment began, and all procedures were approved by the Ethics committee of the Department of Psychology at the University of York.
+
 ## Apparatus & stimuli
+
+In Experiment 1, the stimulus set consisted of a total of 90 images, evenly split between three categories: real faces, human-like robots, and mechanical robots.
+Images all showed the head and shoulders of the subject, had white backgrounds, and were sourced from the internet.
+In Experiment 2, the stimulus set consisted of a total of 296 images, comprising real faces (148 images), people wearing silicone masks (74 images), and people wearing Halloween masks (74 images).
+The backgrounds of these images were more heterogeneous, and showed the natural surroundings of the subject.
+In both experiments, images involved examples of both genders, and of varied ethnic backgrounds.
+
+All stimuli were displayed on a ViewPixx display running at 120Hz, controlled by an Apple Macintosh computer.
+The display was gamma corrected using a photometer to ensure that the luminance output was linear.
+EEG data were collected using a 64-channel Waveguard cap and an ANT Neuroscan system, sampling at 1kHz.
+Low latency digital triggers were sent between the display and the EEG amplifier using an 8-bit parallel cable.
 
@@
 
+Each participant completed three blocks of the first experiment.
+Within each block, all 90 stimulus images were presented twice in a random order.
+Stimuli subtended $11\times11$ degrees at the viewing distance of 57cm, and were shown against a mid-grey background, with a black central fixation cross displayed throughout.
+The presentation duration was 500ms, and participants were asked to press a mouse button to indicate if they believed each image was of a human or of a robot.
+After each response there was a random duration blank period with a mean duration of 1000ms and a standard deviation of 200ms.
+Each block lasted around 6 minutes.
+
 ### Experiment 2: hyper-realistic masks
+
+Participants were shown all 296 images in a random order in each of three blocks.
+In the first block, stimuli subtended $5.5\times7.5$ degrees of visual angle when viewed at a distance of 57cm.
+In the second block, stimuli doubled in size (width and height), and subtended $11\times15$ degrees at the same viewing distance.
+In the third block, stimuli doubled in size again, and subtended $22\times30$ degrees.
+Stimuli were presented for 250ms, and participants indicated whether they thought each image contained a real face or a mask, using a two-button trackball.
+The button assignment (whether the left button indicated a face or a mask, and vice versa) was determined randomly for each participant, but remained constant throughout the whole experiment.
+Text reminding the participant of the button assignment was present continuously in the lower right corner of the screen, far from the area of the screen where the stimuli were presented.
+A central fixation cross was also present throughout.
+After each response there was a random duration blank period with a mean duration of 1000ms and a standard deviation of 200ms.
+Each block lasted around 8 minutes.
 
@@
 
+EEG signals were recorded during each block, and saved to disc for subsequent offline analysis.
+We used a component of the EEGlab toolbox [@Delorme2004] to convert the continuous data from a proprietary file format to a compressed csv text file.
+All subsequent analyses were conducted in R using these files.
+
+For each block, data at each electrode were low-pass filtered at 30Hz with a $10^{th}$ order Butterworth filter, and then epoched using the stimulus onset triggers.
+A pre-stimulus baseline (average voltage of the 200ms before stimulus onset) was subtracted from each waveform.
+We rejected ERPs that showed evidence of excessive noise or movement artefacts on a per-electrode basis by excluding trials where the standard deviation across the time window from 200ms before to 1000ms after stimulus onset exceeded $40\mu V$.
+ERPs were averaged across trials for each participant, and then across participants to calculate group averages.
+
+We performed univariate analyses by conducting Bayesian t-tests [@Rouder2009] between ERPs from pairs of conditions at each time point using a JZS prior.
+The resulting Bayes factor score is a summary of the evidence in favour of either the null hypothesis (that the waveforms are equal) or the alternative hypothesis (that they differ).
+We use the heuristics proposed by @Jeffreys1961 that Bayes factors >3 constitute some evidence supporting the alternative hypothesis, factors >10 constitute strong evidence, and factors >30 constitute very strong evidence.
+
+Multivariate pattern analysis was conducted by training a linear support vector machine algorithm to discriminate between patterns of activity across electrodes at a specific time point.
+The patterns came from the real face condition and one of the mask conditions at a single stimulus size, and for a single participant.
+Examples of each pattern were calculated by averaging over random subsets of 36 trials from a given condition, and using these to train the classifier.
+The accuracy of the classifier was tested on the averaged remaining trials (that were not used in training) for each condition.
+This process was repeated 1000 times with different trial permutations to obtain an average accuracy, where chance performance is at 50\% correct.
+The analysis was carried out at all time points, and also for all participants.
+We then averaged classifier accuracy across participants, and calculated one sample Bayesian t-tests at each time point as described above.
+
 ## Data and code availability
 
-Raw data, processed data, and all analysis scripts are available through the project repository at: https://.
+Raw data, processed data, and analysis scripts are freely available through the project repository at: https://osf.io/5nz2h/
 
@@
   legaltriggers <- 101:103
+  responsetriggers <- c(10,20)
   sublist <- dir(paste0(rawdir,'Robots'),full.names=FALSE)
@@
 
-   if (!file.exists(paste0(processeddir,'RobotsP/R',s,'_processed.RData'))){
+   if (!file.exists(paste0(processeddir,'RobotsP/',sublist[s],'_processed.RData'))){
     datafiles <- dir(subdirs[s],pattern='*.csv.gz',full.names=TRUE)
@@
     alltrials <- array(0,dim=c(3,180,64,1200))
+    allresps <- array(0,dim=c(3,180))
+    allresptimes <- allresps
+
     for (block in 1:length(datafiles)){
@@
         EEGdata[,ch+2] <- ftemp
+      }
+
+    responsetimes <- NULL
+    counter <- 0
+    lasttrigger <- -10000
+    for (n in 1:nrow(EEGdata)){
+      if (EEGdata$Trigger[n] %in% responsetriggers){
+        if (n>(lasttrigger+100)){
+        counter <- counter + 1
+        responsetimes[counter] <- n
+        lasttrigger <- n
+      }}
     }
@@
       }
+
+      allresps[thiscond,trialcounter[thiscond]] <- EEGdata$Trigger[responsetimes[trial]]/10
+      allresptimes[thiscond,trialcounter[thiscond]] <- responsetimes[trial] - triggertimes[trial]
     }
@@
 
-    save(file=paste0(processeddir,'RobotsP/R',s,'_processed.RData'),list=c('trialcounter','alltrials'))
+    save(file=paste0(processeddir,'RobotsP/',sublist[s],'_processed.RData'),list=c('trialcounter','alltrials','allresps','allresptimes'))
    }
@@
 
-# do MVPA for experiment 1
+# do MVPA and subject averaging for experiment 1
 
 if (processdata > 1){
+datafiles <- dir(paste0(processeddir,'RobotsP'),pattern='*.RData',full.names=TRUE)
+totaliterations <- niterations
+
+for (s in 1:1){   #length(datafiles)){
+  tic()
+  print(s)
+  load(datafiles[s])
+
+  subjmvpa <- array(0,dim=c(3,1200))
+  subjmeans <- array(0,dim=c(3,64,1200))
+
+  sdtime <- apply(alltrials,1:3,sd)
+  cutoff <- quantile(sdtime,0.95)
+  includetrials <- sdtime*0
+  includetrials[which(sdtime<cutoff)] <- 1
+  for (cond in 1:3){
+    temp <- alltrials[cond,,,]
+    for (ch in 1:64){
+      if (sum(includetrials[cond,,ch])>1){
+    subjmeans[cond,ch,] <- apply(temp[which(includetrials[cond,,ch]>0),ch,],2,mean)
+    }}
+  }
+
+  normdata <- alltrials*0
+  for (ch in 1:64){
+    for (t in 1:1200){
+      meanV <- (mean(alltrials[1,1:trialcounter[1],ch,t]) + mean(alltrials[2,1:trialcounter[2],ch,t]) + mean(alltrials[3,1:trialcounter[3],ch,t]))/3
+      for (cond in 1:3){
+      normdata[cond,1:trialcounter[cond],ch,t] <- alltrials[cond,1:trialcounter[cond],ch,t] - meanV
+      }
+    }
+  }
+
+  comparisons <- matrix(c(1,2,1,3,2,3),nrow=3,ncol=2,byrow=TRUE)
+  for (comp in 1:nrow(comparisons)){
+    allaccuracy <- matrix(0,nrow=niterations,ncol=1200)
+  for (n in 1:totaliterations){
+
+    # random shuffling of the trial order
+    mintrials <- min(trialcounter[comparisons[comp,1:2]])
+    tempA <- normdata[comparisons[comp,1],sample(1:trialcounter[comparisons[comp,1]],mintrials),,]
+    tempB <- normdata[comparisons[comp,2],sample(1:trialcounter[comparisons[comp,2]],mintrials),,]
+
+    # create averaged subsets of trials
+    condA <- array(0,dim=c(64,1200,nsplits))
+    condB <- array(0,dim=c(64,1200,nsplits))
+    ntrialspermeanA <- floor(dim(tempA)[1]/nsplits)
+    ntrialspermeanB <- floor(dim(tempB)[1]/nsplits)
+    for (i in 1:nsplits){
+      condA[,,i] <- apply(tempA[(1+((i-1)*ntrialspermeanA)):(i*ntrialspermeanA),,],2:3,mean)
+      condB[,,i] <- apply(tempB[(1+((i-1)*ntrialspermeanB)):(i*ntrialspermeanB),,],2:3,mean)
+    }
+
+    if (dowhitening > 0){
+      towhiten <- array(0,dim=c(64,1200,8))
+      towhiten[,,1:4] <- condA[,,1:(nsplits-1)]
+      towhiten[,,5:8] <- condB[,,1:(nsplits-1)]
+      traininglabels <- rep(1:2,each=nsplits-1)
+      W <- whitenmatrix(towhiten,traininglabels)
+      d <- dim(condA)
+      temp <- W %*% matrix(as.vector(condA),nrow=d[1],ncol=d[2]*d[3])
+      condA <- array(as.vector(temp),d)
+      d <- dim(condB)
+      temp <- W %*% matrix(as.vector(condB),nrow=d[1],ncol=d[2]*d[3])
+      condB <- array(as.vector(temp),d)
+    }
+
+    for (t in 1:1200){
+      trainingdata <- t(cbind(condA[,t,1:(nsplits-1)],condB[,t,1:(nsplits-1)]))
+      traininglabels <- gl(2,nsplits-1)
+      testingdata <- t(cbind(condA[,t,nsplits],condB[,t,nsplits]))
+      testinglabels <- gl(2,1)
+      model <- e1071::svm(trainingdata,traininglabels,scale=FALSE,kernel='linear')
+      pred <- predict(model,newdata = testingdata)
+      allaccuracy[n,t] <- sum(pred==testinglabels)/length(testinglabels)
+    }
+  }
+
+    subjmvpa[comp,] <- colMeans(allaccuracy)
+  }
+  save(file=paste0('local/robotsmvpa/R',s,'_mvpa.RData'),list=c('subjmvpa','subjmeans','totaliterations','allresps','allresptimes','trialcounter'))
+
+toc()  
+}
+
+}
+
+```
+
+```{r include=FALSE, results='hide'}
+
+# statistical analysis for experiment 1
+
+if (processdata > 0){
+
+  if (!file.exists('local/GroupDataRobots.RData')){
+
+datafiles <- dir(processeddir,pattern='*decoding.mat',full.names=TRUE)    
+allmvpa <- array(0,dim=c(length(datafiles),3,1201))  
+for (s in 1:length(datafiles)){
+  data <- readMat(datafiles[s])
+  allmvpa[s,,] <- data$Value/100
+}    
+times <- data$Time
+
+datafiles1 <- dir(processeddir,pattern='*_101.mat',full.names=TRUE)    
+datafiles2 <- dir(processeddir,pattern='*_102.mat',full.names=TRUE)    
+datafiles3 <- dir(processeddir,pattern='*_103.mat',full.names=TRUE)    
+allmeans <- array(0,dim=c(length(datafiles1),3,66,1201))
+for (s in 1:length(datafiles1)){
+  data <- readMat(datafiles1[s])
+  allmeans[s,1,,] <- data$F*10^6
+  data <- readMat(datafiles2[s])
+  allmeans[s,2,,] <- data$F*10^6
+  data <- readMat(datafiles3[s])
+  allmeans[s,3,,] <- data$F*10^6
+}
+
+# datafiles <- dir(paste0('local/robotsmvpa'),pattern='*.RData',full.names=TRUE)
+# allmvpa <- array(0,dim=c(length(datafiles),3,1200))
+# allmeans <- array(0,dim=c(length(datafiles),3,64,1200))
+# allRT <- matrix(0,nrow=length(datafiles),ncol=3)
+# prophuman <- matrix(0,nrow=length(datafiles),ncol=3)
+# alldprime <- matrix(0,nrow=length(datafiles),ncol=3)
+# for (s in 1:length(datafiles)){
+#   load(datafiles[s])
+#   allmvpa[s,,] <- subjmvpa
+#   allmeans[s,,,] <- subjmeans
+#   
+#   hits <- NULL
+#   misses <- NULL
+#   for (cond in 1:3){
+#   allRT[s,cond] <- mean(20*log10(allresptimes[cond,which(allresptimes[cond,]>0)]))
+#   prophuman[s,cond] <- sum(allresps[cond,1:trialcounter[cond]]-1)/trialcounter[cond]
+#   
+#   if (cond<3){
+#   hits[cond] <- trialcounter[cond]-sum(allresps[cond,1:trialcounter[cond]]-1)
+#   misses[cond] <- sum(allresps[cond,1:trialcounter[cond]]-1)
+#   }
+#   if (cond==3){
+#   hits[cond] <- sum(allresps[cond,1:trialcounter[cond]]-1)
+#   misses[cond] <- trialcounter[cond]-sum(allresps[cond,1:trialcounter[cond]]-1)
+#   }
+#   }
+#   
+#   hitrate <- hits/(hits + misses) 
+#   for (cond in 1:3){
+#     if (cond<3){falsealarms <- misses[3]/ (misses[3] + hits[3])}
+#     if (cond==3){falsealarms <- sum(misses[1:2]) / (sum(misses[1:2]) + sum(hits[1:2]))}
+#   alldprime[s,cond] <- qnorm(hitrate[cond]) - qnorm(falsealarms)
+#   }
+# }
+# 
+# alldprime[which(is.infinite(alldprime))] <- 5
+# 
+# dataforANOVA <- melt(alldprime)
+# colnames(dataforANOVA) <- c('Participant','Condition','dprime')
+# dataforANOVA$Participant <- as.factor(dataforANOVA$Participant)
+# dataforANOVA$Condition <- as.factor(dataforANOVA$Condition)
+# bfdprime <- extractBF(anovaBF(dprime ~ Condition,dataforANOVA,whichRandom='Participant'))$bf
+# 
+# dataforANOVA <- melt(allRT)
+# colnames(dataforANOVA) <- c('Participant','Condition','RT')
+# dataforANOVA$Participant <- as.factor(dataforANOVA$Participant)
+# dataforANOVA$Condition <- as.factor(dataforANOVA$Condition)
+# bfRT <- extractBF(anovaBF(RT ~ Condition,dataforANOVA,whichRandom='Participant'))$bf
+
+subjmeanERP <- apply(allmeans,c(1,3,4),mean)
+meanERP <- apply(allmeans,2:4,mean)
+meanMVPA <- apply(allmvpa,2:3,mean)
+grandmeanERP <- apply(subjmeanERP[,targetelectrodes,],3,mean)
+subjERPs <- apply(subjmeanERP[,targetelectrodes,],c(1,3),mean)
+condERPs <- apply(allmeans[,,targetelectrodes,],c(1,2,4),mean)
+
+mlimits <- matrix(0,nrow=6,ncol=1201)
+mBF <- matrix(0,nrow=3,ncol=1201)
+bspop <- 1:nbootstraps
+for (n in 1:1201){
+
+  for (cond in 1:3){
+  for (b in 1:nbootstraps){
+    bspop[b] <- mean(sample(allmvpa[,cond,n],replace=TRUE))
+  }
+mlimits[(1:2)+((cond-1)*2),n] <- quantile(bspop,probs=c(0.025,0.975)) 
+mBF[cond,n] <- extractBF(ttestBF(allmvpa[,cond,n],mu=0.5))$bf
+  }
+}
+
+comparisons <- matrix(c(1,2,1,3,2,3),nrow=3,ncol=2,byrow=TRUE)
+limits <- matrix(0,nrow=8,ncol=1201)
+ERP_BF <- matrix(0,nrow=3,ncol=1201)
+bspop <- 1:nbootstraps
+for (n in 1:1201){
+
+  for (b in 1:nbootstraps){
+    bspop[b] <- mean(sample(subjERPs[,n],replace=TRUE))
+  }
+  limits[1:2,n] <- quantile(bspop,probs=c(0.025,0.975))
+
+  for (cond in 1:3){
+  for (b in 1:nbootstraps){
+    bspop[b] <- mean(sample(condERPs[,cond,n],replace=TRUE))
+  }
+  limits[(1:2)+(cond*2),n] <- quantile(bspop,probs=c(0.025,0.975)) 
+  ERP_BF[cond,n] <- extractBF(ttestBF(condERPs[,comparisons[cond,1],n],condERPs[,comparisons[cond,2],n],paired=TRUE))$bf
+  }
+}
+
+save(file='local/GroupDataRobots.RData',list=c('allmeans','allmvpa','mlimits','subjmeanERP','limits','grandmeanERP','subjERPs','condERPs','meanMVPA','meanERP','mBF','ERP_BF'))
+}
 
@@
 
+if (file.exists('local/GroupDataRobots.RData')){load('local/GroupDataRobots.RData')}  
 if (processdata > 0){
 
+pdf(paste0('Figures/RobotsData.pdf'), bg="transparent", height = 12, width = 12)
+
+par(mfrow=c(2,2))
+
+  plotlims <- c(0,5,0.5,3.5)  
+  ticklocsy <- c(0.5,1,2,3,3.5)    
+  ticklocsx <- 0:5    # locations of tick marks on y axis
+  ticklabelsy <- c("","Robot","Android","Human","")       
+  ticklabelsx <- ticklocsx    # set labels for y ticks
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  mtext(text = ticklabelsx, side = 1, at=ticklocsx)     
+  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=3) 
+  title(xlab="d prime", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+  # a <- density(alldprime[,1],cut=6)
+  # a$y <- 0.35*a$y/max(a$y)
+  # polygon(a$x,1.1+a$y,border=NA,col=collist[1])
+  # 
+  #   a <- density(alldprime[,2])
+  # a$y <- 0.35*a$y/max(a$y)
+  # polygon(a$x,2.1+a$y,border=NA,col=collist[2])
+  # 
+  #   a <- density(alldprime[,3])
+  # a$y <- 0.35*a$y/max(a$y)
+  # polygon(a$x,3.1+a$y,border=NA,col=collist[3])
+  # 
+  # xvals <- seq(-0.1,0.1,length=nrow(alldprime))
+  # points(alldprime[,1],1+xvals-0.2,pch=16)
+  # points(alldprime[,2],2+xvals-0.2,pch=15)
+  # points(alldprime[,3],3+xvals-0.2,pch=18)
+  # 
+  # for (cond in 1:3){
+  # bs <- NULL
+  # for (n in 1:nbootstraps){bs[n] <- mean(sample(alldprime[,cond],replace=TRUE))}
+  # ci <- quantile(bs,c(0.025,0.975))
+  # arrows(mean(alldprime[,cond]),cond,ci[1],cond,angle=90,length=0.1,lwd=3)
+  # arrows(mean(alldprime[,cond]),cond,ci[2],cond,angle=90,length=0.1,lwd=3)
+  # }
+  # 
+  # points(mean(alldprime[,1]),1,pch=21,cex=2,lwd=2,bg=collist[1])
+  # points(mean(alldprime[,2]),2,pch=22,cex=2,lwd=2,bg=collist[2])
+  # points(mean(alldprime[,3]),3,pch=23,cex=2,lwd=2,bg=collist[3])
+  #
+
+  plotlims <- c(52,64,0.5,3.5)  
+  ticklocsy <- c(0.5,1,2,3,3.5)    
+  ticklocsx <- c(52,58,64)    
+  ticklabelsy <- c("","Robot","Android","Human","")       
+  ticklabelsx <- c(400,800,1600)    # set labels for y ticks
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  mtext(text = ticklabelsx, side = 1, at=ticklocsx)     
+  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=3) 
+  title(xlab="Reaction time (ms)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+  # a <- density(allRT[,1],cut=6)
+  # a$y <- 0.35*a$y/max(a$y)
+  # polygon(a$x,1.1+a$y,border=NA,col=collist[1])
+  # 
+  #   a <- density(allRT[,2])
+  # a$y <- 0.35*a$y/max(a$y)
+  # polygon(a$x,2.1+a$y,border=NA,col=collist[2])
+  # 
+  #   a <- density(allRT[,3])
+  # a$y <- 0.35*a$y/max(a$y)
+  # polygon(a$x,3.1+a$y,border=NA,col=collist[3])
+  # 
+  # xvals <- seq(-0.1,0.1,length=nrow(allRT))
+  # points(allRT[,1],1+xvals-0.2,pch=16)
+  # points(allRT[,2],2+xvals-0.2,pch=15)
+  # points(allRT[,3],3+xvals-0.2,pch=18)
+  # 
+  # for (cond in 1:3){
+  # bs <- NULL
+  # for (n in 1:nbootstraps){bs[n] <- mean(sample(allRT[,cond],replace=TRUE))}
+  # ci <- quantile(bs,c(0.025,0.975))
+  # arrows(mean(allRT[,cond]),cond,ci[1],cond,angle=90,length=0.1,lwd=3)
+  # arrows(mean(allRT[,cond]),cond,ci[2],cond,angle=90,length=0.1,lwd=3)
+  # }
+  # points(mean(allRT[,1]),1,pch=21,cex=2,lwd=2,bg=collist[1])
+  # points(mean(allRT[,2]),2,pch=22,cex=2,lwd=2,bg=collist[2])
+  # points(mean(allRT[,3]),3,pch=23,cex=2,lwd=2,bg=collist[3])
+
+plotlims <- c(-200,1000,0,1) 
+ticklocsx <- seq(-200,1000,200)  
+ticklocsy <- seq(0,1,0.25)    
+ticklabelsx <- ticklocsx      
+ticklabelsy <- ticklocsy*100
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)  
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  #}    
+title(ylab="Classifier accuracy (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(c(-200, 1000),c(0.5, 0.5), col='black', lty=2)
+lines(c(0,0),c(0,1), col='black')
+
+polygon(c(-200:1000,1000:-200), c(mlimits[1,],mlimits[2,1201:1]), col=addalpha('black',0.3),border=NA)
+polygon(c(-200:1000,1000:-200), c(mlimits[3,],mlimits[4,1201:1]), col=addalpha('blue',0.3),border=NA)
+polygon(c(-200:1000,1000:-200), c(mlimits[5,],mlimits[6,1201:1]), col=addalpha('green',0.3),border=NA)
+
+lines(-200:1000,meanMVPA[1,], col='black', lwd=3, cex=0.5)     
+lines(-200:1000,meanMVPA[2,], col='blue', lwd=3, cex=0.5)     
+lines(-200:1000,meanMVPA[3,], col='green', lwd=3, cex=0.5)
+
+plotlims <- c(-200,1000,-12,12)  
+ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
+ticklocsy <- seq(-12,12,4)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2, cex=1.5)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1.5)  
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.8)   
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1.8)
+
+lines(c(-200,1000),c(0,0),lty=1)
+lines(c(0,0),c(-20,20),lty=1)
+
+polygon(c(-200:1000,1000:-200), c(limits[3,],limits[4,1201:1]), col=addalpha(collist[1],0.3),border=NA)
+polygon(c(-200:1000,1000:-200), c(limits[5,],limits[6,1201:1]), col=addalpha(collist[2],0.3),border=NA)
+polygon(c(-200:1000,1000:-200), c(limits[7,],limits[8,1201:1]), col=addalpha(collist[3],0.3),border=NA)
+
+lines(-200:1000, colMeans(meanERP[1,targetelectrodes,]), lwd=3, col=collist[1])     
+lines(-200:1000, colMeans(meanERP[2,targetelectrodes,]), lwd=3, col=collist[2])     
+lines(-200:1000, colMeans(meanERP[3,targetelectrodes,]), lwd=3, col=collist[3])
+
+dev.off()
+
+pdf(paste0('Figures/RobotsMVPA.pdf'), bg="transparent", height = 12, width = 12)
+
+par(mfrow=c(2,2))
+
+times <- -199:1200
+
+plotlims <- c(-200,1000,-12,12)  
+ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
+ticklocsy <- seq(-12,12,4)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2, cex=1.5)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1.5)  
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.8)   
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1.8)
+
+lines(c(-200,1000),c(0,0),lty=1)
+lines(c(0,0),c(-20,20),lty=1)
+
+polygon(c(-200:1000,1000:-200), c(limits[3,],limits[4,1201:1]), col=addalpha(collist[1],0.3),border=NA)
+polygon(c(-200:1000,1000:-200), c(limits[7,],limits[8,1201:1]), col=addalpha(collist[3],0.3),border=NA)
+
+lines(-200:1000, colMeans(meanERP[1,targetelectrodes,]), lwd=3, col=collist[1])     
+lines(-200:1000, colMeans(meanERP[3,targetelectrodes,]), lwd=3, col=collist[3])
+
+plotlims <- c(-200,1000,-12,12)  
+ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
+ticklocsy <- seq(-12,12,4)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2, cex=1.5)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1.5)  
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.8)   
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1.8)
+
+lines(c(-200,1000),c(0,0),lty=1)
+lines(c(0,0),c(-20,20),lty=1)
+
+polygon(c(-200:1000,1000:-200), c(limits[5,],limits[6,1201:1]), col=addalpha(collist[2],0.3),border=NA)
+polygon(c(-200:1000,1000:-200), c(limits[7,],limits[8,1201:1]), col=addalpha(collist[3],0.3),border=NA)
+
+lines(-200:1000, colMeans(meanERP[2,targetelectrodes,]), lwd=3, col=collist[2])     
+lines(-200:1000, colMeans(meanERP[3,targetelectrodes,]), lwd=3, col=collist[3])
+
+plotlims <- c(-200,1000,0,1) 
+ticklocsx <- seq(-200,1000,200)  
+ticklocsy <- seq(0,1,0.25)    
+ticklabelsx <- ticklocsx      
+ticklabelsy <- ticklocsy*100
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)  
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  #}    
+title(ylab="Classifier accuracy (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(c(-200, 1000),c(0.5, 0.5), col='black', lty=2)
+lines(c(0,0),c(0,1), col='black')
+
+polygon(c(-200:1000,1000:-200), c(mlimits[3,],mlimits[4,1201:1]), col=addalpha('blue',0.3),border=NA)
+
+lines(-200:1000,meanMVPA[2,], col='blue', lwd=3, cex=0.5)
+
+allbfs <- mBF[2,]
+lowsig <- 0.5 + (1:1201)*0
+midsig <- 0.5 + (1:1201)*0
+hisig <- 0.5 + (1:1201)*0
+for (t in 1:1201){
+ if (allbfs[t]>=3 & allbfs[t]<10){lowsig[t] <- allmeans[t]}
+ if (allbfs[t]>=10 & allbfs[t]<30){midsig[t] <- allmeans[t]}
+ if (allbfs[t]>=30){hisig[t] <- allmeans[t]}
 }
+
+linestartstop <- times[allbfs>=3 & allbfs<10]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.34,0.34,0.36,0.36), col=rgb(1,1,0,alpha=1),border=NA)}}
+
+linestartstop <- times[allbfs>=10 & allbfs<30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.34,0.34,0.36,0.36), col=rgb(1,0.5,0,alpha=1),border=NA)}}
+
+linestartstop <- times[allbfs>=30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.34,0.34,0.36,0.36), col=rgb(1,0,0,alpha=1),border=NA)}}
+
+plotlims <- c(-200,1000,0,1) 
+ticklocsx <- seq(-200,1000,200)  
+ticklocsy <- seq(0,1,0.25)    
+ticklabelsx <- ticklocsx      
+ticklabelsy <- ticklocsy*100
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)  
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  #}    
+title(ylab="Classifier accuracy (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(c(-200, 1000),c(0.5, 0.5), col='black', lty=2)
+lines(c(0,0),c(0,1), col='black')
+
+polygon(c(-200:1000,1000:-200), c(mlimits[5,],mlimits[6,1201:1]), col=addalpha('green',0.3),border=NA)
+
+lines(-200:1000,meanMVPA[3,], col='green', lwd=3, cex=0.5)
+
+allbfs <- mBF[3,]
+lowsig <- 0.5 + (1:1201)*0
+midsig <- 0.5 + (1:1201)*0
+hisig <- 0.5 + (1:1201)*0
+for (t in 1:1201){
+ if (allbfs[t]>=3 & allbfs[t]<10){lowsig[t] <- allmeans[t]}
+ if (allbfs[t]>=10 & allbfs[t]<30){midsig[t] <- allmeans[t]}
+ if (allbfs[t]>=30){hisig[t] <- allmeans[t]}
+}
+
+linestartstop <- times[allbfs>=3 & allbfs<10]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.34,0.34,0.36,0.36), col=rgb(1,1,0,alpha=1),border=NA)}}
+
+linestartstop <- times[allbfs>=10 & allbfs<30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.34,0.34,0.36,0.36), col=rgb(1,0.5,0,alpha=1),border=NA)}}
+
+linestartstop <- times[allbfs>=30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.34,0.34,0.36,0.36), col=rgb(1,0,0,alpha=1),border=NA)}}
+
+dev.off()
+
+}
+
+```
+
+```{r RobotsData, fig.cap="I.", fig.align="center", echo=FALSE, fig.width=12, fig.height=12}
+
+knitr::include_graphics('Figures/RobotsData.pdf')
+
+```
+
+```{r RobotsMVPA, fig.cap="I.", fig.align="center", echo=FALSE, fig.width=12, fig.height=12}
+
+knitr::include_graphics('Figures/RobotsMVPA.pdf')
 
@@
   legaltriggers <- c(111,112,123,211,212,223)
+  responsetriggers <- c(10,20)
   sublist <- dir(paste0(rawdir,'Masks'),full.names=FALSE)
@@
 
-    if (!file.exists(paste0(processeddir,'MasksP/M',s,'_processed.RData'))){
+if (!file.exists(paste0(processeddir,'MasksP/',sublist[s],'_processed.RData'))){
     datafiles <- dir(subdirs[s],pattern='*.csv.gz',full.names=TRUE)
@@
     alltrials <- array(0,dim=c(3,6,76,64,1200))
+    allresps <- array(0,dim=c(3,6,76))
+    allresptimes <- allresps
     for (block in 1:3){
@@
 
+          responsetimes <- NULL
+    counter <- 0
+    lasttrigger <- -10000
+    for (n in 1:nrow(EEGdata)){
+      if (EEGdata$Trigger[n] %in% responsetriggers){
+        if (n>(lasttrigger+100)){
+        counter <- counter + 1
+        responsetimes[counter] <- n
+        lasttrigger <- n
+      }}
+    }
+    print(counter)
+
+    # fix a weird bug where there is a missing trigger
+    if (s==10){if (block==1){responsetimes <- responsetimes[2:counter]}}
+    if (s==16){if (block==2){responsetimes <- responsetimes[2:counter]}}
+    if (s==18){if (block==3){responsetimes <- responsetimes[2:counter]}}
+    if (s==25){if (block==2){responsetimes <- responsetimes[2:counter]}}
+
     triggertimes <- NULL
@@
 
+   if (s==17){if (block==3){counter <- counter - 1
+      triggertimes <- triggertimes[1:counter]}}
+
+        print(counter)
+
     for (trial in 1:counter){
@@
       }
+            allresps[block,thiscond,trialcounter[block,thiscond]] <- EEGdata$Trigger[responsetimes[trial]]/10
+      allresptimes[block,thiscond,trialcounter[block,thiscond]] <- responsetimes[trial] - triggertimes[trial]
     }
@@
 
-    save(file=paste0(processeddir,'MasksP/M',s,'_processed.RData'),list=c('trialcounter','alltrials'))
+    save(file=paste0(processeddir,'MasksP/',sublist[s],'_processed.RData'),list=c('trialcounter','alltrials','allresps','allresptimes'))
   }
@@
 if (processdata > 1){
+datafiles <- dir(paste0(processeddir,'MasksP'),pattern='*.RData',full.names=TRUE)
+totaliterations <- niterations
+
+for (s in 1:length(datafiles)){
+  tic()
+  print(s)
+  load(datafiles[s])
+
+  subjmvpa <- array(0,dim=c(3,1200))
+  subjmeans <- array(0,dim=c(3,64,1200))
+
+  # collapse trials across block and ethnicity
+  temptrials <- array(0,dim=c(3,444,64,1200))
+  tempRT <- array(0,dim=c(3,444))
+  tempresp <- array(0,dim=c(3,444))
+  condcount <- c(0,0,0)
+  for (cond in 1:3){
+    for (block in 1:3){
+      temp <- alltrials[block,cond,1:trialcounter[block,cond],,]
+      i <- condcount[cond] + (1:trialcounter[block,cond])
+    temptrials[cond,i,,] <- temp
+    tempresp[cond,i] <- allresps[block,cond,1:trialcounter[block,cond]]
+    tempRT[cond,i] <- allresptimes[block,cond,1:trialcounter[block,cond]]
+    condcount[cond] <- condcount[cond] + trialcounter[block,cond]
+
+      temp <- alltrials[block,cond+3,1:trialcounter[block,cond+3],,]
+      i <- condcount[cond] + (1:trialcounter[block,cond+3])
+    temptrials[cond,i,,] <- temp
+        tempresp[cond,i] <- allresps[block,cond+3,1:trialcounter[block,cond+3]]
+    tempRT[cond,i] <- allresptimes[block,cond+3,1:trialcounter[block,cond+3]]
+    condcount[cond] <- condcount[cond] + trialcounter[block,cond+3]    
+    }
+  }
+  trialcounter <- condcount
+  allresps <- tempresp
+  allresptimes <- tempRT
+  alltrials <- temptrials
+  rm(temptrials)
+  rm(tempresp)
+  rm(tempRT)
+
+  for (cond in 1:3){
+  sdtime <- apply(alltrials[cond,1:trialcounter[cond],,],1:2,sd)
+  cutoff <- quantile(sdtime,0.95)
+  includetrials <- sdtime*0
+  includetrials[which(sdtime<cutoff)] <- 1
+
+    temp <- alltrials[cond,,,]
+    for (ch in 1:64){
+      if (sum(includetrials[,ch])>1){
+    subjmeans[cond,ch,] <- apply(temp[which(includetrials[,ch]>0),ch,],2,mean)
+    }}
+  }
+
+  normdata <- alltrials*0
+  for (ch in 1:64){
+    for (t in 1:1200){
+      meanV <- mean(alltrials[,1:trialcounter[cond],ch,t])
+      for (cond in 1:3){
+      normdata[cond,1:trialcounter[cond],ch,t] <- alltrials[cond,1:trialcounter[cond],ch,t] - meanV
+      }
+    }
+  }
+
+  comparisons <- matrix(c(1,2,1,3,2,3),nrow=3,ncol=2,byrow=TRUE)
+  for (comp in 1:nrow(comparisons)){
+    allaccuracy <- matrix(0,nrow=niterations,ncol=1200)
+  for (n in 1:totaliterations){
+
+    mintrials <- min(trialcounter[comparisons[comp,1:2]])
+    # random shuffling of the trial order
+    tempA <- normdata[comparisons[comp,1],sample(1:trialcounter[comparisons[comp,1]],mintrials),,]
+    tempB <- normdata[comparisons[comp,2],sample(1:trialcounter[comparisons[comp,2]],mintrials),,]
+
+    # create averaged subsets of trials
+    condA <- array(0,dim=c(nsplits,64,1200))
+    condB <- array(0,dim=c(nsplits,64,1200))
+    ntrialspermeanA <- floor(dim(tempA)[1]/nsplits)
+    ntrialspermeanB <- floor(dim(tempB)[1]/nsplits)
+    for (i in 1:nsplits){
+      condA[i,,] <- apply(tempA[(1+((i-1)*ntrialspermeanA)):(i*ntrialspermeanA),,],2:3,mean)
+      condB[i,,] <- apply(tempB[(1+((i-1)*ntrialspermeanB)):(i*ntrialspermeanB),,],2:3,mean)
+    }
+
+    for (t in 1:1200){
+      trainingdata <- rbind(condA[1:(nsplits-1),,t],condB[1:(nsplits-1),,t])
+      traininglabels <- gl(2,nsplits-1)
+      testingdata <- rbind(condA[nsplits,,t],condB[nsplits,,t])
+      testinglabels <- gl(2,1)
+      model <- e1071::svm(trainingdata,traininglabels,scale=FALSE)
+      pred <- predict(model,newdata = testingdata)
+      allaccuracy[n,t] <- sum(pred==testinglabels)/length(testinglabels)
+    }
+  }
+
+    subjmvpa[comp,] <- colMeans(allaccuracy)
+  }
+  save(file=paste0('local/masksmvpa/M',s,'_mvpa.RData'),list=c('subjmvpa','subjmeans','totaliterations','allresps','allresptimes','trialcounter'))
+
+toc()  
+}
+
+}
+
+```
+
+```{r include=FALSE, results='hide'}
+
+# statistical analysis for experiment 2
+
+processeddir <- 'local/MasksProcessed/'
+
+if (processdata > 0){
+
+  if (!file.exists('local/GroupDataMasks.RData')){
+
+datafiles <- dir(processeddir,pattern='*decoding.mat',full.names=TRUE)    
+allmvpa <- array(0,dim=c(length(datafiles),3,1201))  
+for (s in 1:length(datafiles)){
+  data <- readMat(datafiles[s])
+  allmvpa[s,,] <- data$Value/100
+}    
+times <- data$Time
+
+datafiles1 <- dir(processeddir,pattern='*_101.mat',full.names=TRUE)    
+datafiles2 <- dir(processeddir,pattern='*_102.mat',full.names=TRUE)    
+datafiles3 <- dir(processeddir,pattern='*_103.mat',full.names=TRUE)    
+allmeans <- array(0,dim=c(length(datafiles1),3,66,1201))
+for (s in 1:length(datafiles1)){
+  data <- readMat(datafiles1[s])
+  allmeans[s,1,,] <- data$F*10^6
+  data <- readMat(datafiles2[s])
+  allmeans[s,2,,] <- data$F*10^6
+  data <- readMat(datafiles3[s])
+  allmeans[s,3,,] <- data$F*10^6
+}
+
+# datafiles <- dir(paste0('local/robotsmvpa'),pattern='*.RData',full.names=TRUE)
+# allmvpa <- array(0,dim=c(length(datafiles),3,1200))
+# allmeans <- array(0,dim=c(length(datafiles),3,64,1200))
+# allRT <- matrix(0,nrow=length(datafiles),ncol=3)
+# prophuman <- matrix(0,nrow=length(datafiles),ncol=3)
+# alldprime <- matrix(0,nrow=length(datafiles),ncol=3)
+# for (s in 1:length(datafiles)){
+#   load(datafiles[s])
+#   allmvpa[s,,] <- subjmvpa
+#   allmeans[s,,,] <- subjmeans
+#   
+#   hits <- NULL
+#   misses <- NULL
+#   for (cond in 1:3){
+#   allRT[s,cond] <- mean(20*log10(allresptimes[cond,which(allresptimes[cond,]>0)]))
+#   prophuman[s,cond] <- sum(allresps[cond,1:trialcounter[cond]]-1)/trialcounter[cond]
+#   
+#   if (cond<3){
+#   hits[cond] <- trialcounter[cond]-sum(allresps[cond,1:trialcounter[cond]]-1)
+#   misses[cond] <- sum(allresps[cond,1:trialcounter[cond]]-1)
+#   }
+#   if (cond==3){
+#   hits[cond] <- sum(allresps[cond,1:trialcounter[cond]]-1)
+#   misses[cond] <- trialcounter[cond]-sum(allresps[cond,1:trialcounter[cond]]-1)
+#   }
+#   }
+#   
+#   hitrate <- hits/(hits + misses) 
+#   for (cond in 1:3){
+#     if (cond<3){falsealarms <- misses[3]/ (misses[3] + hits[3])}
+#     if (cond==3){falsealarms <- sum(misses[1:2]) / (sum(misses[1:2]) + sum(hits[1:2]))}
+#   alldprime[s,cond] <- qnorm(hitrate[cond]) - qnorm(falsealarms)
+#   }
+# }
+# 
+# alldprime[which(is.infinite(alldprime))] <- 5
+# 
+# dataforANOVA <- melt(alldprime)
+# colnames(dataforANOVA) <- c('Participant','Condition','dprime')
+# dataforANOVA$Participant <- as.factor(dataforANOVA$Participant)
+# dataforANOVA$Condition <- as.factor(dataforANOVA$Condition)
+# bfdprime <- extractBF(anovaBF(dprime ~ Condition,dataforANOVA,whichRandom='Participant'))$bf
+# 
+# dataforANOVA <- melt(allRT)
+# colnames(dataforANOVA) <- c('Participant','Condition','RT')
+# dataforANOVA$Participant <- as.factor(dataforANOVA$Participant)
+# dataforANOVA$Condition <- as.factor(dataforANOVA$Condition)
+# bfRT <- extractBF(anovaBF(RT ~ Condition,dataforANOVA,whichRandom='Participant'))$bf
+
+subjmeanERP <- apply(allmeans,c(1,3,4),mean)
+meanERP <- apply(allmeans,2:4,mean)
+meanMVPA <- apply(allmvpa,2:3,mean)
+grandmeanERP <- apply(subjmeanERP[,targetelectrodes,],3,mean)
+subjERPs <- apply(subjmeanERP[,targetelectrodes,],c(1,3),mean)
+condERPs <- apply(allmeans[,,targetelectrodes,],c(1,2,4),mean)
+
+mlimits <- matrix(0,nrow=6,ncol=1201)
+mBF <- matrix(0,nrow=3,ncol=1201)
+bspop <- 1:nbootstraps
+for (n in 1:1201){
+
+  for (cond in 1:3){
+  for (b in 1:nbootstraps){
+    bspop[b] <- mean(sample(allmvpa[,cond,n],replace=TRUE))
+  }
+mlimits[(1:2)+((cond-1)*2),n] <- quantile(bspop,probs=c(0.025,0.975)) 
+mBF[cond,n] <- extractBF(ttestBF(allmvpa[,cond,n],mu=0.5))$bf
+  }
+}
+
+comparisons <- matrix(c(1,2,1,3,2,3),nrow=3,ncol=2,byrow=TRUE)
+limits <- matrix(0,nrow=8,ncol=1201)
+ERP_BF <- matrix(0,nrow=3,ncol=1201)
+bspop <- 1:nbootstraps
+for (n in 1:1201){
+
+  for (b in 1:nbootstraps){
+    bspop[b] <- mean(sample(subjERPs[,n],replace=TRUE))
+  }
+  limits[1:2,n] <- quantile(bspop,probs=c(0.025,0.975))
+
+  for (cond in 1:3){
+  for (b in 1:nbootstraps){
+    bspop[b] <- mean(sample(condERPs[,cond,n],replace=TRUE))
+  }
+  limits[(1:2)+(cond*2),n] <- quantile(bspop,probs=c(0.025,0.975)) 
+  ERP_BF[cond,n] <- extractBF(ttestBF(condERPs[,comparisons[cond,1],n],condERPs[,comparisons[cond,2],n],paired=TRUE))$bf
+  }
+}
+
+save(file='local/GroupDataMasks.RData',list=c('allmeans','allmvpa','mlimits','subjmeanERP','limits','grandmeanERP','subjERPs','condERPs','meanMVPA','meanERP','mBF','ERP_BF'))
+}
 
@@
 
+if (file.exists('local/GroupDataMasks.RData')){load('local/GroupDataMasks.RData')}  
 if (processdata > 0){
+
+pdf(paste0('Figures/MaskData.pdf'), bg="transparent", height = 12, width = 12)
+
+par(mfrow=c(2,2))
+
+  plotlims <- c(0,5,0.5,3.5)  
+  ticklocsy <- c(0.5,1,2,3,3.5)    
+  ticklocsx <- 0:5    # locations of tick marks on y axis
+  ticklabelsy <- c("","Halloween","Silicone","Human","")       
+  ticklabelsx <- ticklocsx    # set labels for y ticks
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  mtext(text = ticklabelsx, side = 1, at=ticklocsx)     
+  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=3) 
+  title(xlab="d prime", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+  # a <- density(alldprime[,1],cut=6)
+  # a$y <- 0.35*a$y/max(a$y)
+  # polygon(a$x,1.1+a$y,border=NA,col=collist[1])
+  # 
+  #   a <- density(alldprime[,2])
+  # a$y <- 0.35*a$y/max(a$y)
+  # polygon(a$x,2.1+a$y,border=NA,col=collist[2])
+  # 
+  #   a <- density(alldprime[,3])
+  # a$y <- 0.35*a$y/max(a$y)
+  # polygon(a$x,3.1+a$y,border=NA,col=collist[3])
+  # 
+  # xvals <- seq(-0.1,0.1,length=nrow(alldprime))
+  # points(alldprime[,1],1+xvals-0.2,pch=16)
+  # points(alldprime[,2],2+xvals-0.2,pch=15)
+  # points(alldprime[,3],3+xvals-0.2,pch=18)
+  # 
+  # for (cond in 1:3){
+  # bs <- NULL
+  # for (n in 1:nbootstraps){bs[n] <- mean(sample(alldprime[,cond],replace=TRUE))}
+  # ci <- quantile(bs,c(0.025,0.975))
+  # arrows(mean(alldprime[,cond]),cond,ci[1],cond,angle=90,length=0.1,lwd=3)
+  # arrows(mean(alldprime[,cond]),cond,ci[2],cond,angle=90,length=0.1,lwd=3)
+  # }
+  # 
+  # points(mean(alldprime[,1]),1,pch=21,cex=2,lwd=2,bg=collist[1])
+  # points(mean(alldprime[,2]),2,pch=22,cex=2,lwd=2,bg=collist[2])
+  # points(mean(alldprime[,3]),3,pch=23,cex=2,lwd=2,bg=collist[3])
+  #
+
+  plotlims <- c(52,64,0.5,3.5)  
+  ticklocsy <- c(0.5,1,2,3,3.5)    
+  ticklocsx <- c(52,58,64)    
+  ticklabelsy <- c("","Halloween","Silicone","Human","")       
+  ticklabelsx <- c(400,800,1600)    # set labels for y ticks
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  mtext(text = ticklabelsx, side = 1, at=ticklocsx)     
+  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=3) 
+  title(xlab="Reaction time (ms)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+  # a <- density(allRT[,1],cut=6)
+  # a$y <- 0.35*a$y/max(a$y)
+  # polygon(a$x,1.1+a$y,border=NA,col=collist[1])
+  # 
+  #   a <- density(allRT[,2])
+  # a$y <- 0.35*a$y/max(a$y)
+  # polygon(a$x,2.1+a$y,border=NA,col=collist[2])
+  # 
+  #   a <- density(allRT[,3])
+  # a$y <- 0.35*a$y/max(a$y)
+  # polygon(a$x,3.1+a$y,border=NA,col=collist[3])
+  # 
+  # xvals <- seq(-0.1,0.1,length=nrow(allRT))
+  # points(allRT[,1],1+xvals-0.2,pch=16)
+  # points(allRT[,2],2+xvals-0.2,pch=15)
+  # points(allRT[,3],3+xvals-0.2,pch=18)
+  # 
+  # for (cond in 1:3){
+  # bs <- NULL
+  # for (n in 1:nbootstraps){bs[n] <- mean(sample(allRT[,cond],replace=TRUE))}
+  # ci <- quantile(bs,c(0.025,0.975))
+  # arrows(mean(allRT[,cond]),cond,ci[1],cond,angle=90,length=0.1,lwd=3)
+  # arrows(mean(allRT[,cond]),cond,ci[2],cond,angle=90,length=0.1,lwd=3)
+  # }
+  # points(mean(allRT[,1]),1,pch=21,cex=2,lwd=2,bg=collist[1])
+  # points(mean(allRT[,2]),2,pch=22,cex=2,lwd=2,bg=collist[2])
+  # points(mean(allRT[,3]),3,pch=23,cex=2,lwd=2,bg=collist[3])
+
+plotlims <- c(-200,1000,0,1) 
+ticklocsx <- seq(-200,1000,200)  
+ticklocsy <- seq(0,1,0.25)    
+ticklabelsx <- ticklocsx      
+ticklabelsy <- ticklocsy*100
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)  
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  #}    
+title(ylab="Classifier accuracy (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(c(-200, 1000),c(0.5, 0.5), col='black', lty=2)
+lines(c(0,0),c(0,1), col='black')
+
+polygon(c(-200:1000,1000:-200), c(mlimits[1,],mlimits[2,1201:1]), col=addalpha('black',0.3),border=NA)
+polygon(c(-200:1000,1000:-200), c(mlimits[3,],mlimits[4,1201:1]), col=addalpha('blue',0.3),border=NA)
+polygon(c(-200:1000,1000:-200), c(mlimits[5,],mlimits[6,1201:1]), col=addalpha('green',0.3),border=NA)
+
+lines(-200:1000,meanMVPA[1,], col='black', lwd=3, cex=0.5)     
+lines(-200:1000,meanMVPA[2,], col='blue', lwd=3, cex=0.5)     
+lines(-200:1000,meanMVPA[3,], col='green', lwd=3, cex=0.5)
+
+plotlims <- c(-200,1000,-12,12)  
+ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
+ticklocsy <- seq(-12,12,4)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2, cex=1.5)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1.5)  
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.8)   
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1.8)
+
+lines(c(-200,1000),c(0,0),lty=1)
+lines(c(0,0),c(-20,20),lty=1)
+
+polygon(c(-200:1000,1000:-200), c(limits[3,],limits[4,1201:1]), col=addalpha(collist[1],0.3),border=NA)
+polygon(c(-200:1000,1000:-200), c(limits[5,],limits[6,1201:1]), col=addalpha(collist[2],0.3),border=NA)
+polygon(c(-200:1000,1000:-200), c(limits[7,],limits[8,1201:1]), col=addalpha(collist[3],0.3),border=NA)
+
+lines(-200:1000, colMeans(meanERP[1,targetelectrodes,]), lwd=3, col=collist[1])     
+lines(-200:1000, colMeans(meanERP[2,targetelectrodes,]), lwd=3, col=collist[2])     
+lines(-200:1000, colMeans(meanERP[3,targetelectrodes,]), lwd=3, col=collist[3])
+
+dev.off()
+
+pdf(paste0('Figures/MaskMVPA.pdf'), bg="transparent", height = 12, width = 12)
+
+par(mfrow=c(2,2))
+
+times <- -199:1200
+
+plotlims <- c(-200,1000,-12,12)  
+ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
+ticklocsy <- seq(-12,12,4)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2, cex=1.5)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1.5)  
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.8)   
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1.8)
+
+lines(c(-200,1000),c(0,0),lty=1)
+lines(c(0,0),c(-20,20),lty=1)
+
+polygon(c(-200:1000,1000:-200), c(limits[3,],limits[4,1201:1]), col=addalpha(collist[1],0.3),border=NA)
+polygon(c(-200:1000,1000:-200), c(limits[7,],limits[8,1201:1]), col=addalpha(collist[3],0.3),border=NA)
+
+lines(-200:1000, colMeans(meanERP[1,targetelectrodes,]), lwd=3, col=collist[1])     
+lines(-200:1000, colMeans(meanERP[3,targetelectrodes,]), lwd=3, col=collist[3])
+
+plotlims <- c(-200,1000,-12,12)  
+ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
+ticklocsy <- seq(-12,12,4)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2, cex=1.5)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1.5)  
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.8)   
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1.8)
+
+lines(c(-200,1000),c(0,0),lty=1)
+lines(c(0,0),c(-20,20),lty=1)
+
+polygon(c(-200:1000,1000:-200), c(limits[5,],limits[6,1201:1]), col=addalpha(collist[2],0.3),border=NA)
+polygon(c(-200:1000,1000:-200), c(limits[7,],limits[8,1201:1]), col=addalpha(collist[3],0.3),border=NA)
+
+lines(-200:1000, colMeans(meanERP[2,targetelectrodes,]), lwd=3, col=collist[2])     
+lines(-200:1000, colMeans(meanERP[3,targetelectrodes,]), lwd=3, col=collist[3])
+
+plotlims <- c(-200,1000,0,1) 
+ticklocsx <- seq(-200,1000,200)  
+ticklocsy <- seq(0,1,0.25)    
+ticklabelsx <- ticklocsx      
+ticklabelsy <- ticklocsy*100
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)  
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  #}    
+title(ylab="Classifier accuracy (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(c(-200, 1000),c(0.5, 0.5), col='black', lty=2)
+lines(c(0,0),c(0,1), col='black')
+
+polygon(c(-200:1000,1000:-200), c(mlimits[3,],mlimits[4,1201:1]), col=addalpha('blue',0.3),border=NA)
+
+lines(-200:1000,meanMVPA[2,], col='blue', lwd=3, cex=0.5)
+
+allbfs <- mBF[2,]
+lowsig <- 0.5 + (1:1201)*0
+midsig <- 0.5 + (1:1201)*0
+hisig <- 0.5 + (1:1201)*0
+for (t in 1:1201){
+ if (allbfs[t]>=3 & allbfs[t]<10){lowsig[t] <- allmeans[t]}
+ if (allbfs[t]>=10 & allbfs[t]<30){midsig[t] <- allmeans[t]}
+ if (allbfs[t]>=30){hisig[t] <- allmeans[t]}
+}
+
+linestartstop <- times[allbfs>=3 & allbfs<10]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.34,0.34,0.36,0.36), col=rgb(1,1,0,alpha=1),border=NA)}}
+
+linestartstop <- times[allbfs>=10 & allbfs<30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.34,0.34,0.36,0.36), col=rgb(1,0.5,0,alpha=1),border=NA)}}
+
+linestartstop <- times[allbfs>=30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.34,0.34,0.36,0.36), col=rgb(1,0,0,alpha=1),border=NA)}}
+
+plotlims <- c(-200,1000,0,1) 
+ticklocsx <- seq(-200,1000,200)  
+ticklocsy <- seq(0,1,0.25)    
+ticklabelsx <- ticklocsx      
+ticklabelsy <- ticklocsy*100
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)  
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  #}    
+title(ylab="Classifier accuracy (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(c(-200, 1000),c(0.5, 0.5), col='black', lty=2)
+lines(c(0,0),c(0,1), col='black')
+
+polygon(c(-200:1000,1000:-200), c(mlimits[5,],mlimits[6,1201:1]), col=addalpha('green',0.3),border=NA)
+
+lines(-200:1000,meanMVPA[3,], col='green', lwd=3, cex=0.5)
+
+allbfs <- mBF[3,]
+lowsig <- 0.5 + (1:1201)*0
+midsig <- 0.5 + (1:1201)*0
+hisig <- 0.5 + (1:1201)*0
+for (t in 1:1201){
+ if (allbfs[t]>=3 & allbfs[t]<10){lowsig[t] <- allmeans[t]}
+ if (allbfs[t]>=10 & allbfs[t]<30){midsig[t] <- allmeans[t]}
+ if (allbfs[t]>=30){hisig[t] <- allmeans[t]}
+}
+
+linestartstop <- times[allbfs>=3 & allbfs<10]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.34,0.34,0.36,0.36), col=rgb(1,1,0,alpha=1),border=NA)}}
+
+linestartstop <- times[allbfs>=10 & allbfs<30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.34,0.34,0.36,0.36), col=rgb(1,0.5,0,alpha=1),border=NA)}}
+
+linestartstop <- times[allbfs>=30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.34,0.34,0.36,0.36), col=rgb(1,0,0,alpha=1),border=NA)}}
+
+dev.off()
 
@@
 
-```{r pupildata, fig.cap="Caption.", fig.align="center", echo=FALSE}
+```{r MasksData, fig.cap="I.", fig.align="center", echo=FALSE, fig.width=12, fig.height=12}
 
-# knitr::include_graphics(paste0('Figures/pupildata.pdf'))
+knitr::include_graphics('Figures/MaskData.pdf')
 
 ```
+
+```{r MasksMVPA, fig.cap="I.", fig.align="center", echo=FALSE, fig.width=12, fig.height=12}
+
+knitr::include_graphics('Figures/MaskMVPA.pdf')
+
+```
+
 # Discussion

### 2023-02-01 manuscript.tex
Interim commit when switching computers

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Neural correlates of the uncanny valley effect\\
for robots and hyper-realistic masks\\
(for submission to Computers in Human Behavior)}
\author{Shona Fitzpatrick, Ailish K. Byrne, Alex Headley, Jet G. Sanders,\\
Helen Petrie, Rob Jenkins \& Daniel H. Baker}
\date{2023-01-02}

\begin{document}
\maketitle

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Many people report an aversion to entities that are human-like, but on closer inspection are actually artificial. Examples include humanoid robots (androids), puppets, realistic computer-generated images, and hyper-realistic masks. The term `uncanny valley' (Mori, 1970; English translation in Mori et al., 2012) describes the idea that entities that are clearly human or clearly artificial do not evoke unease, whereas artificial entities that are human-like are disconcerting. Understanding these experiences is increasingly important as artificial entities become more integrated into our everyday lives, however at present relatively little is known about the neural underpinnings of the uncanny valley effect.

Neural responses to faces and bodies in general are well-characterised, and there appear to be specialised brain regions devoted to both (reviewed in Hu et al., 2020). For example, areas of the occipital lobe (Gauthier et al., 2000) and fusiform gyrus (Kanwisher et al., 1997) respond more to faces than non-face stimuli, and sections of extrastriate cortex are responsive to bodies (Downing et al., 2001). There are also event-related potential (ERP) signals associated with face and body stimuli, though their precise purpose is still debated (Thierry et al., 2007). It seems highly likely that `uncanny' images will activate these same processes, yet it is unclear whether the sense of unease they produce occurs at bottom-up sensory stages, or is modulated by more top-down cognitive factors.

One previous study has measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect. Saygin et al. (2012) found repetition suppression effects in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion. These effects were stronger than for movies of humans or mechanical robots performing the same actions. A more recent electroencephalography (EEG) study (Urgen et al., 2018) identified a difference in the N400 component between dynamic and static conditions using the same stimuli. Although this difference was strongest over frontal electrodes, source reconstruction of the N400 itself suggested a left-lateralised source in temporo-parietal cortex, consistent with the fMRI results (Saygin et al., 2012). The authors interpret both of these findings as being due to the discrepancy between the human-like appearance and the clearly non-biological motion of the robot.

Our aim here was to further investigate neural correlates of the uncanny valley effect. We achieve this through two EEG experiments, in which we measure neural responses to static images. In the first experiment, the stimuli were humans, machine-like robots, and human-like robots. In the second experiment we aimed to generalise the finding by using images of people wearing no masks, wearing obvious masks (e.g.~carnival or halloween masks), and wearing hyper-realistic silicone masks (Sanders et al., 2017). Rather than focus on specific ERP components, we use a non-parametric cluster correction procedure to compare conditions. We also apply a pattern classification approach to identify time windows in which information in the EEG signal can be used to distinguish between pairs of conditions.

\hypertarget{materials-methods}{%
\section{Materials \& Methods}\label{materials-methods}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

A total of 29 participants completed Experiment 1 (12 male, 17 female), and 30 participants completed Experiment 2 (7 male, 23 female). None of the participants had previously taken part in a study using these stimuli, and all were naïve to the hypotheses and wore their normal optical correction if required. Written informed consent was collected before each experiment began, and all procedures were approved by the Ethics committee of the Department of Psychology at the University of York.

\hypertarget{apparatus-stimuli}{%
\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}

In Experiment 1, the stimulus set consisted of a total of 90 images, evenly split between three categories: real faces, human-like robots, and mechanical robots. Images all showed the head and shoulders of the subject, had white backgrounds, and were sourced from the internet. In Experiment 2, the stimulus set consisted of a total of 296 images, comprising real faces (148 images), people wearing silicone masks (74 images), and people wearing Halloween masks (74 images). The backgrounds of these images were more heterogeneous, and showed the natural surroundings of the subject. In both experiments, images involved examples of both genders, and of varied ethnic backgrounds.

All stimuli were displayed on a ViewPixx display running at 120Hz, controlled by an Apple Macintosh computer. The display was gamma corrected using a photometer to ensure that the luminance output was linear. EEG data were collected using a 64-channel Waveguard cap and an ANT Neuroscan system, sampling at 1kHz. Low latency digital triggers were sent between the display and the EEG amplifier using an 8-bit parallel cable.

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{experiment-1-robots}{%
\subsubsection{Experiment 1: robots}\label{experiment-1-robots}}

Each participant completed three blocks of the first experiment. Within each block, all 90 stimulus images were presented twice in a random order. Stimuli subtended \(11\times11\) degrees at the viewing distance of 57cm, and were shown against a mid-grey background, with a black central fixation cross displayed throughout. The presentation duration was 500ms, and participants were asked to press a mouse button to indicate if they believed each image was of a human or of a robot. After each response there was a random duration blank period with a mean duration of 1000ms and a standard deviation of 200ms. Each block lasted around 6 minutes.

\hypertarget{experiment-2-hyper-realistic-masks}{%
\subsubsection{Experiment 2: hyper-realistic masks}\label{experiment-2-hyper-realistic-masks}}

Participants were shown all 296 images in a random order in each of three blocks. In the first block, stimuli subtended \(5.5\times7.5\) degrees of visual angle when viewed at a distance of 57cm. In the second block, stimuli doubled in size (width and height), and subtended \(11\times15\) degrees at the same viewing distance. In the third block, stimuli doubled in size again, and subtended \(22\times30\) degrees. Stimuli were presented for 250ms, and participants indicated whether they thought each image contained a real face or a mask, using a two-button trackball. The button assignment (whether the left button indicated a face or a mask, and vice versa) was determined randomly for each participant, but remained constant throughout the whole experiment. Text reminding the participant of the button assignment was present continuously in the lower right corner of the screen, far from the area of the screen where the stimuli were presented. A central fixation cross was also present throughout. After each response there was a random duration blank period with a mean duration of 1000ms and a standard deviation of 200ms. Each block lasted around 8 minutes.

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

EEG signals were recorded during each block, and saved to disc for subsequent offline analysis. We used a component of the EEGlab toolbox (Delorme and Makeig, 2004) to convert the continuous data from a proprietary file format to a compressed csv text file. All subsequent analyses were conducted in R using these files.

For each block, data at each electrode were low-pass filtered at 30Hz with a \(10^{th}\) order Butterworth filter, and then epoched using the stimulus onset triggers. A pre-stimulus baseline (average voltage of the 200ms before stimulus onset) was subtracted from each waveform. We rejected ERPs that showed evidence of excessive noise or movement artefacts on a per-electrode basis by excluding trials where the standard deviation across the time window from 200ms before to 1000ms after stimulus onset exceeded \(40\mu V\). ERPs were averaged across trials for each participant, and then across participants to calculate group averages.

We performed univariate analyses by conducting Bayesian t-tests (Rouder et al., 2009) between ERPs from pairs of conditions at each time point using a JZS prior. The resulting Bayes factor score is a summary of the evidence in favour of either the null hypothesis (that the waveforms are equal) or the alternative hypothesis (that they differ). We use the heuristics proposed by Jeffreys (1961) that Bayes factors \textgreater3 constitute some evidence supporting the alternative hypothesis, factors \textgreater10 constitute strong evidence, and factors \textgreater30 constitute very strong evidence.

Multivariate pattern analysis was conducted by training a linear support vector machine algorithm to discriminate between patterns of activity across electrodes at a specific time point. The patterns came from the real face condition and one of the mask conditions at a single stimulus size, and for a single participant. Examples of each pattern were calculated by averaging over random subsets of 36 trials from a given condition, and using these to train the classifier. The accuracy of the classifier was tested on the averaged remaining trials (that were not used in training) for each condition. This process was repeated 1000 times with different trial permutations to obtain an average accuracy, where chance performance is at 50\% correct. The analysis was carried out at all time points, and also for all participants. We then averaged classifier accuracy across participants, and calculated one sample Bayesian t-tests at each time point as described above.

\hypertarget{data-and-code-availability}{%
\subsection{Data and code availability}\label{data-and-code-availability}}

Raw data, processed data, and analysis scripts are freely available through the project repository at: \url{https://osf.io/5nz2h/}

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{experiment-1}{%
\subsection{Experiment 1}\label{experiment-1}}

\begin{figure}

{\centering \includegraphics{Figures/RobotsData}

}

\caption{I.}\label{fig:RobotsData}
\end{figure}

\begin{figure}

{\centering \includegraphics{Figures/RobotsMVPA}

}

\caption{I.}\label{fig:RobotsMVPA}
\end{figure}

\hypertarget{experiment-2}{%
\subsection{Experiment 2}\label{experiment-2}}

\begin{figure}

{\centering \includegraphics{Figures/MaskData}

}

\caption{I.}\label{fig:MasksData}
\end{figure}

\begin{figure}

{\centering \includegraphics{Figures/MaskMVPA}

}

\caption{I.}\label{fig:MasksMVPA}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Delorme2004}{}}%
Delorme A, Makeig S. 2004. {EEGLAB}: An open source toolbox for analysis of single-trial {EEG} dynamics including independent component analysis. \emph{J Neurosci Methods} \textbf{134}:9--21. doi:\href{https://doi.org/10.1016/j.jneumeth.2003.10.009}{10.1016/j.jneumeth.2003.10.009}

\leavevmode\vadjust pre{\hypertarget{ref-Downing2001}{}}%
Downing PE, Jiang Y, Shuman M, Kanwisher N. 2001. A cortical area selective for visual processing of the human body. \emph{Science} \textbf{293}:2470--3. doi:\href{https://doi.org/10.1126/science.1063414}{10.1126/science.1063414}

\leavevmode\vadjust pre{\hypertarget{ref-Gauthier2000}{}}%
Gauthier I, Tarr MJ, Moylan J, Skudlarski P, Gore JC, Anderson AW. 2000. The fusiform "face area" is part of a network that processes faces at the individual level. \emph{J Cogn Neurosci} \textbf{12}:495--504. doi:\href{https://doi.org/10.1162/089892900562165}{10.1162/089892900562165}

\leavevmode\vadjust pre{\hypertarget{ref-Hu2020}{}}%
Hu Y, Baragchizadeh A, O'Toole AJ. 2020. Integrating faces and bodies: Psychological and neural perspectives on whole person perception. \emph{Neurosci Biobehav Rev} \textbf{112}:472--486. doi:\href{https://doi.org/10.1016/j.neubiorev.2020.02.021}{10.1016/j.neubiorev.2020.02.021}

\leavevmode\vadjust pre{\hypertarget{ref-Jeffreys1961}{}}%
Jeffreys H. 1961. Theory of probability, 3rd ed. Oxford University Press, Clarendon Press.

\leavevmode\vadjust pre{\hypertarget{ref-Kanwisher1997}{}}%
Kanwisher N, McDermott J, Chun MM. 1997. The fusiform face area: A module in human extrastriate cortex specialized for face perception. \emph{J Neurosci} \textbf{17}:4302--11. doi:\href{https://doi.org/10.1523/JNEUROSCI.17-11-04302.1997}{10.1523/JNEUROSCI.17-11-04302.1997}

\leavevmode\vadjust pre{\hypertarget{ref-Mori1970}{}}%
Mori M. 1970. The uncanny valley. \emph{Energy} \textbf{7}:33--35.

\leavevmode\vadjust pre{\hypertarget{ref-Mori2012}{}}%
Mori M, MacDorman KF, Kageki N. 2012. The uncanny valley {[}from the field{]}. \emph{IEEE Robotics \& Automation Magazine} \textbf{19}:98--100. doi:\href{https://doi.org/10.1109/MRA.2012.2192811}{10.1109/MRA.2012.2192811}

\leavevmode\vadjust pre{\hypertarget{ref-Rouder2009}{}}%
Rouder JN, Speckman PL, Sun D, Morey RD, Iverson G. 2009. Bayesian t tests for accepting and rejecting the null hypothesis. \emph{Psychon Bull Rev} \textbf{16}:225--37. doi:\href{https://doi.org/10.3758/PBR.16.2.225}{10.3758/PBR.16.2.225}

\leavevmode\vadjust pre{\hypertarget{ref-Sanders2017}{}}%
Sanders JG, Ueda Y, Minemoto K, Noyes E, Yoshikawa S, Jenkins R. 2017. Hyper-realistic face masks: A new challenge in person identification. \emph{Cognitive Research: Principles and Implications} \textbf{2}. doi:\href{https://doi.org/10.1186/s41235-017-0079-y}{10.1186/s41235-017-0079-y}

\leavevmode\vadjust pre{\hypertarget{ref-Saygin2012}{}}%
Saygin AP, Chaminade T, Ishiguro H, Driver J, Frith C. 2012. The thing that should not be: Predictive coding and the uncanny valley in perceiving human and humanoid robot actions. \emph{Soc Cogn Affect Neurosci} \textbf{7}:413--22. doi:\href{https://doi.org/10.1093/scan/nsr025}{10.1093/scan/nsr025}

\leavevmode\vadjust pre{\hypertarget{ref-Thierry2007}{}}%
Thierry G, Martin CD, Downing P, Pegna AJ. 2007. Controlling for interstimulus perceptual variance abolishes N170 face selectivity. \emph{Nat Neurosci} \textbf{10}:505--11. doi:\href{https://doi.org/10.1038/nn1864}{10.1038/nn1864}

\leavevmode\vadjust pre{\hypertarget{ref-Urgen2018}{}}%
Urgen BA, Kutas M, Saygin AP. 2018. Uncanny valley as a window into predictive processing in the social brain. \emph{Neuropsychologia} \textbf{114}:181--185. doi:\href{https://doi.org/10.1016/j.neuropsychologia.2018.04.027}{10.1016/j.neuropsychologia.2018.04.027}

\end{CSLReferences}

\end{document}

### 2023-02-01 masks1.m

@@ -1,0 +1,117 @@
+% Script generated by Brainstorm (12-Dec-2022)
+rawpath = '/Volumes/USB128/UncannyValley/MasksRaw/';
+procpath = '/Volumes/USB128/UncannyValley/MasksProcessed/';
+dbpath = '/Volumes/USB128/brainstormdb/Masks/data/';
+
+for s = 351:380
+    s
+    tic
+% Input files
+sFiles = [];
+SubjectNames = {num2str(s)};
+RawFiles = {strcat(rawpath,num2str(s),'.set')};
+
+% Process: Create link to raw file
+sFiles = bst_process('CallProcess', 'process_import_data_raw', sFiles, [], ...
+    'subjectname',    SubjectNames{1}, ...
+    'datafile',       {RawFiles{1}, 'EEG-EEGLAB'}, ...
+    'channelreplace', 1, ...
+    'channelalign',   1, ...
+    'evtmode',        'value');
+
+% Process: Band-pass:0.5Hz-48Hz
+sFiles = bst_process('CallProcess', 'process_bandpass', sFiles, [], ...
+    'sensortypes', 'MEG, EEG', ...
+    'highpass',    0.5, ...
+    'lowpass',     30, ...
+    'tranband',    0, ...
+    'attenuation', 'relax', ...  % 40dB
+    'ver',         '2019', ...  % 2019
+    'mirror',      0, ...
+    'read_all',    0);
+
+% merge across asian and western image sets by renaming event triggers
+sFiles = bst_process('CallProcess', 'process_evt_rename', sFiles, [], ...
+    'src',   '111, 211, 112, 212, 123, 223', ...
+    'dest',  '101, 101, 102, 102, 103, 103');
+
+% Process: Import MEG/EEG: Events
+sFiles = bst_process('CallProcess', 'process_import_data_event', sFiles, [], ...
+    'subjectname',   SubjectNames{1}, ...
+    'condition',     '', ...
+    'eventname',     '101, 102, 103', ...
+    'timewindow',    [], ...
+    'epochtime',     [-0.2, 1], ...
+    'split',         0, ...
+    'createcond',    1, ...
+    'ignoreshort',   1, ...
+    'usectfcomp',    1, ...
+    'usessp',        1, ...
+    'freq',          [], ...
[…]

### 2023-02-01 plotindividuals.R

@@ -1,0 +1,180 @@
+
+if (file.exists('local/GroupDataRobots.RData')){load('local/GroupDataRobots.RData')}  
+targetelectrodes <- c(28,54,58,64)
+
+pdf(paste0('Figures/allERProbot.pdf'), bg="transparent", height = 12, width = 10)
+
+par(mfrow=c(6,5))
+
+for (s in 1:28){
+plotlims <- c(-200,1000,-12,12)  
+ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
+ticklocsy <- seq(-12,12,4)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2, cex=1)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1)  
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1)   
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1)
+
+lines(c(-200,1000),c(0,0),lty=1)
+lines(c(0,0),c(-20,20),lty=1)
+
+lines(-200:1000, colMeans(subjmeanERP[s,targetelectrodes,]), lwd=3)     
+
+}
+
+plotlims <- c(-200,1000,-12,12)  
+ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
+ticklocsy <- seq(-12,12,4)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
[…]

### 2023-02-01 robots1.m

@@ -1,0 +1,112 @@
+% Script generated by Brainstorm (12-Dec-2022)
+rawpath = '/Volumes/USB128/UncannyValley/RobotsClean/';
+procpath = '/Volumes/USB128/UncannyValley/RobotsProcessed/';
+dbpath = '/Volumes/USB128/brainstormdb/Robots/data/';
+
+slist = [302 304 305 309 313];
+for sno = 1:length(slist)
+    s = slist(sno)
+    tic
+% Input files
+sFiles = [];
+SubjectNames = {num2str(s)};
+RawFiles = {strcat(rawpath,num2str(s),'.set')};
+
+% Process: Create link to raw file
+sFiles = bst_process('CallProcess', 'process_import_data_raw', sFiles, [], ...
+    'subjectname',    SubjectNames{1}, ...
+    'datafile',       {RawFiles{1}, 'EEG-EEGLAB'}, ...
+    'channelreplace', 1, ...
+    'channelalign',   1, ...
+    'evtmode',        'value');
+
+% Process: Band-pass:0.5Hz-48Hz
+sFiles = bst_process('CallProcess', 'process_bandpass', sFiles, [], ...
+    'sensortypes', 'MEG, EEG', ...
+    'highpass',    0.5, ...
+    'lowpass',     30, ...
+    'tranband',    0, ...
+    'attenuation', 'relax', ...  % 40dB
+    'ver',         '2019', ...  % 2019
+    'mirror',      0, ...
+    'read_all',    0);
+
+% Process: Import MEG/EEG: Events
+sFiles = bst_process('CallProcess', 'process_import_data_event', sFiles, [], ...
+    'subjectname',   SubjectNames{1}, ...
+    'condition',     '', ...
+    'eventname',     '101, 102, 103', ...
+    'timewindow',    [], ...
+    'epochtime',     [-0.2, 1], ...
+    'split',         0, ...
+    'createcond',    1, ...
+    'ignoreshort',   1, ...
+    'usectfcomp',    1, ...
+    'usessp',        1, ...
+    'freq',          [], ...
+    'baseline',      [-0.2, -0.001], ...
+    'blsensortypes', 'MEG, EEG');
+
+d = dir(strcat(dbpath,num2str(s),'/101/data_101_trial*'));
+sFiles1 = {};
+for n = 1:length(d)
[…]

### 2023-02-17 manuscript.Rmd
First draft (excluding discussion)

--- 2022-12-14 manuscript.Rmd
@@
 ---
-title: "Uncanny Valley"
-author: "Daniel Baker"
-date: "`r Sys.Date()`"
+title: |
+  | Neural correlates of the uncanny valley effect
+  | for robots and hyper-realistic masks 
+  | (for submission to Computers in Human Behavior)
+author: |
+  | Shona Fitzpatrick, Ailish K. Byrne, Alex Headley, Jet G. Sanders,
+  | Helen Petrie, Rob Jenkins & Daniel H. Baker (daniel.baker@york.ac.uk)
+date: "University of York"
 output:
+  pdf_document:
+    toc: no
   bookdown::pdf_document2:
@@
   word_document: default
-  pdf_document:
-    toc: no
   html_document: default
@@
 
-processdata <- 3  # this flag determines the amount of processing, with 4 levels:
+processdata <- 0  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
-# 1 - generate figures using the processed group data (requires XMB of storage)
-# 2 - perform multivariate pattern analysis on individual participants (requires 25GB of storage, and takes X hours)
+# 1 - generate figures using the processed group data (requires 120MB of storage)
+# 2 - do statistics and bootstrapping using processed data
 # 3 - download all raw data and do preprocessing (requires ~60GB of storage)
 
-niterations <- 100  # number of iterations for MVPA
+nbootstraps <- 1000
+targetelectrodes <- c(28,54,58,64)
 
 # check which packages are installed, install the missing ones, and activate
-packagelist <- c('knitr','e1071','signal','osfr') # list of CRAN packages
+packagelist <- c('knitr','e1071','signal','osfr','tictoc','BayesFactor','reshape2','powerplus','R.matlab') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
@@
 rawdir <- '/Volumes/USB128/UncannyValley/'
-processeddir <- 'local/processed/'
-processeddir <- '/Volumes/USB128/UncannyValley/'
+processeddir <- 'local/output/'
+# processeddir <- '/Volumes/USB128/UncannyValley/'
+
+if (!dir.exists('local/')){dir.create('local/')}
+# if (!dir.exists('local/robotsmvpa/')){dir.create('local/robotsmvpa/')}
+# if (!dir.exists('local/masksmvpa/')){dir.create('local/masksmvpa/')}
+
+collist <- c('lightsalmon','forestgreen','cornflowerblue')
+bfcols <- c('gold','darkorange','firebrick')
+colfunc <- colorRampPalette(c("darkgreen", "darkblue"))
+colvect <- colfunc(29)
+addalpha <- function(col, alpha=1){apply(sapply(col, col2rgb)/255, 2, function(x) rgb(x[1], x[2], x[3], alpha=alpha))}
+
+getstartstop <- function(linestartstop){
+  xpairs <- matrix(0, nrow = 1200, ncol = 2)
+  paircounter <- 1
+  startval <- linestartstop[1]
+  lastval <- linestartstop[1]
+  for (n in 2:length(linestartstop)){
+    if ((linestartstop[n] - lastval) > 1){
+      xpairs[paircounter, ] <- c(startval, lastval)
+      startval <- linestartstop[n]
+      paircounter <- paircounter + 1
+    }
+    lastval <- linestartstop[n]
+  }
+  xpairs[paircounter,] <- c(startval,lastval)
+  xpairs <- xpairs[1:(paircounter+1),1:2]
+  return(xpairs)}
+
+# two functions used in prewhitening prior to MVPA
+# data must be in the format sensor x time x trials
+cov1para <- function(x){
+
+  s <- dim(x)
+  ti <- s[1]
+  n <- s[2]
+  meanx <- colMeans(x)
+  x <- x - matrix(rep(meanx,ti),nrow=ti,ncol=n,byrow=TRUE)
+
+  sample <- (1/ti)*(t(x)%*%x)
+
+  meanvar <- sum(diag(sample))/n
+  prior <- meanvar * diag(n)
+
+  y <- x^2
+  phiMat <- t(y) %*% y/ti - sample^2
+  phi <- sum(phiMat)
+
+  gamma <- sample - prior
+  gamma <- sum(gamma^2)
+
+  kappa <- phi/gamma
+  shrinkage <- max(0,min(1,kappa/ti))
+
+  sigma <- shrinkage * prior + (1-shrinkage) * sample
+
+  return(sigma)}
+
+whitenmatrix <- function(data,condid){
+
+  # set up variables
+  s <- dim(data)
+  nvar <- s[1]
+  ntimes <- s[2]
+  ncond <- max(condid)
+  Cov <- matrix(0,nrow=nvar,ncol=nvar)
+
+  # compute whitening matrix
+  for (cond in 1:ncond){
+    dat <- data[,,which(condid==cond)]
+    for (time in 1:ntimes){
+      sigma <- cov1para(t(dat[,time,]))
+      Cov <- Cov + sigma
+    }
+  }
+  Cov <- Cov/(ncond*ntimes)
+  W <- powerplus::Matpow(Cov,-0.5)
+return(W)}
 
 knitr::opts_chunk$set(echo = TRUE)
+
 ```
@@
 
+Many people report an aversion to entities that are superficially human-like, but on closer inspection are actually artificial.
+Examples include humanoid robots (androids), puppets, hyper-realistic masks, and computer-generated images or movies.
+The term 'uncanny valley' [@Mori1970; English translation in @Mori2012] describes the idea that entities that are clearly human or clearly artificial do not evoke unease, whereas artificial entities that are human-like are disconcerting.
+Understanding these experiences is increasingly important as artificial entities become more integrated into our everyday lives, however at present relatively little is known about the neural underpinnings of the uncanny valley effect.
+
+Neural responses to faces and bodies in general are well-characterised, and there appear to be specialised brain regions devoted to both [reviewed in @Hu2020].
+For example, areas of the occipital lobe [@Gauthier2000] and fusiform gyrus [@Kanwisher1997] respond more to faces than non-face stimuli, and sections of extrastriate cortex are responsive to bodies [@Downing2001].
+There are also event-related potential (ERP) signals associated with face and body stimuli, though their precise purpose is still debated [@Thierry2007].
+It seems highly likely that 'uncanny' images will activate these same processes, yet it is unclear whether the sense of unease they produce occurs at bottom-up sensory stages, or is modulated by more top-down cognitive factors.
+
+One previous study has measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
+@Saygin2012 found repetition suppression effects in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
+These effects were stronger than for movies of humans or mechanical robots performing the same actions.
+A more recent electroencephalography (EEG) study [@Urgen2018] identified a difference in the N400 component between dynamic and static conditions using the same stimuli.
+Although this difference was strongest over frontal electrodes, source reconstruction of the N400 itself suggested a left-lateralised source in temporo-parietal cortex, consistent with the fMRI results [@Saygin2012].
+The authors interpret both of these findings as being due to the discrepancy between the human-like appearance and the clearly non-biological motion of the robot.
+
+Our aim here was to further investigate neural correlates of the uncanny valley effect.
+We achieve this through two EEG experiments, in which we measure neural responses to static images.
+In the first experiment, the stimuli were humans, machine-like robots, and human-like robots (see Figure \ref{fig:stimexamples}a).
+In the second experiment we aimed to generalise the finding by using images of people wearing no masks, wearing obvious masks (e.g.
+carnival or Halloween masks), and wearing hyper-realistic silicone masks [@Sanders2017] (see Figure \ref{fig:stimexamples}b).
+Rather than focus on specific ERP components, we use a multivariate pattern classification approach to identify time windows in which information in the EEG signal can be used to distinguish between pairs of conditions.
+Our rationale is that timepoints where signals evoked by human faces can be distinguished from those evoked by human-like robots, or hyper-realistic masks, are candidates for a neural signature of the uncanny valley effect.
+
+```{r stimexamples, fig.cap="Illustrative stimuli from the same categories as used in Experiments 1 and 2.
+Row (a) shows a human face, an android and a robot, all against white backgrounds.
+Row (b) shows a human face, a hyper-realistic silicone mask, and a carnival mask, all against natural backgrounds.
+Images were taken from a variety of sources that permit reuse in academic contexts and in most cases were not part of the stimulus set from the experiments.
+The silicone mask image was taken by the authors, and was used in Experiment 2.", fig.align="center", echo=FALSE, fig.width=8, fig.height=8}
+
+knitr::include_graphics('Figures/stimfigure.jpg')
+
+```
+
 # Materials & Methods
@@
 
+A total of 29 participants completed Experiment 1 (12 male, 17 female), and 30 participants completed Experiment 2 (7 male, 23 female).
+None of the participants had previously taken part in a study using these stimuli, and all were naïve to the hypotheses and wore their normal optical correction if required.
+Written informed consent was collected before each experiment began, and all procedures were approved by the Ethics committee of the Department of Psychology at the University of York.
+
 ## Apparatus & stimuli
+
+In Experiment 1, the stimulus set consisted of a total of 90 images, evenly split between three categories: real faces, human-like robots, and mechanical robots.
+Images all showed the head and shoulders of the subject, had white backgrounds, and were sourced from the internet.
+In Experiment 2, the stimulus set consisted of a total of 296 images, comprising real faces (148 images), people wearing silicone masks (74 images), and people wearing obvious masks of the sort typically worn for carnivals and Halloween celebrations (74 images).
+The backgrounds of these images were more heterogeneous, and showed the natural surroundings of the subject.
+In both experiments, images involved examples of both genders, and of varied ethnic backgrounds.
+
+All stimuli were displayed on a ViewPixx display running at 120Hz, controlled by an Apple Macintosh computer.
+The display was gamma corrected using a photometer to ensure that the luminance output was linear.
+EEG data were collected using a 64-channel Waveguard cap and an ANT Neuroscan system, sampling at 1kHz.
+Low latency digital triggers were sent between the display and the EEG amplifier using an 8-bit parallel cable.
 
@@
 
+Each participant completed three blocks of the first experiment.
+Within each block, all 90 stimulus images were presented twice in a random order.
+Stimuli subtended $11\times11$ degrees at the viewing distance of 57cm, and were shown against a mid-grey background, with a black central fixation cross displayed throughout.
+The presentation duration was 500ms, and participants were asked to press a mouse button to indicate if they believed each image was of a human or of a robot.
+After each response there was a random duration blank period with a mean duration of 1000ms and a standard deviation of 200ms.
+Each block lasted around 6 minutes.
+
 ### Experiment 2: hyper-realistic masks
+
+Participants were shown all 296 images in a random order in each of three blocks.
+In the first block, stimuli subtended $5.5\times7.5$ degrees of visual angle when viewed at a distance of 57cm.
+In the second block, stimuli doubled in size (width and height), and subtended $11\times15$ degrees at the same viewing distance.
+In the third block, stimuli doubled in size again, and subtended $22\times30$ degrees.
+The rationale for the size manipulation was to investigate whether increasing levels of detail made the silicone masks more identifiable [@Sanders2017], however as that is not the main focus of the current paper we collapse results across size conditions.
+Stimuli were presented for 250ms, and participants indicated whether they thought each image contained a real face or a mask, using a two-button trackball.
+The button assignment (whether the left button indicated a face or a mask, and vice versa) was determined randomly for each participant, but remained constant throughout the whole experiment.
+Text reminding the participant of the button assignment was present continuously in the lower right corner of the screen, far from the area of the screen where the stimuli were presented.
+A central fixation cross was also present throughout.
+After each response there was a random duration blank period with a mean duration of 1000ms and a standard deviation of 200ms.
+Each block lasted around 8 minutes.
 
@@
 
+We analysed response data by calculating d-prime scores for each condition, derived from the hit rate and false alarm rate [@Macmillan2005].
+For the human conditions, the hit rate was the proportion of human images correctly identified as human, and the false alarm rate was the proportion of robot or mask images that were incorrectly judged as being human.
+For the robot and mask conditions, the hit rate was the proportion of robot/mask images correctly identified as not being human, and the false alarm rate was the proportion of human images that were incorrectly judged as being non-human (note that this means the false alarm rate was the same for the robot and android conditions, and for the silicone and Halloween mask conditions).
+We capped infinite d-prime values (which occur e.g.
+when the hit rate is 1) at an arbitrary ceiling of 5.
+We log transformed the reaction times (which typically have positive skew) and performed all averaging and statistical analysis on the logarithmic values.
+
+EEG signals were recorded during each block, and saved to disc for subsequent offline analysis.
+We used components of the EEGlab toolbox [@Delorme2004] to import the data into Matlab and collate data across blocks.
+We then used Brainstorm [@Tadel2011] to filter the data using a bandpass filter (0.5 to 30Hz), epoch by condition, and subtract a pre-trial baseline (the mean voltage for the 200ms before stimulus onset).
+Five participants were excluded from the EEG analysis of each experiment due to excessive noise.
+Our attempts to clean up the data from these participants using independent components analysis was unsuccessful.
+Their behavioural data were still included in the analysis.
+In Experiment 2 we combined data across all three image sizes, as this was not the main focus of our analysis.
+
+We performed univariate analyses by conducting Bayesian t-tests [@Rouder2009] between ERPs from pairs of conditions at each time point using a JZS prior.
+The resulting Bayes factor score is a summary of the evidence in favour of either the null hypothesis (that the waveforms are equal) or the alternative hypothesis (that they differ).
+We use the heuristics proposed by @Jeffreys1961 that Bayes factors >3 ($log_{10}BF_{10}$ > 0.5) constitute some evidence supporting the alternative hypothesis, factors >10 ($log_{10}BF_{10}$ > 1) constitute strong evidence, and factors >30 ($log_{10}BF_{10}$ > 1.5) constitute very strong evidence.
+
+Multivariate pattern analysis was conducted by training a linear support vector machine algorithm (LibSVM; @Chang2011) to discriminate between patterns of activity across electrodes at a specific time point.
+The patterns came from the human face condition and one of the other conditions, for a single participant.
+Four examples of each pattern were calculated by averaging over random subsets of 20\% of the available trials from a given condition, and using these to train the classifier.
+The accuracy of the classifier was tested on the averaged remaining trials (that were not used in training) for each condition.
+This process was repeated 1000 times with different trial permutations to obtain an average accuracy, where chance performance is at 50\% correct.
+The analysis was carried out at all time points, and also for all participants.
+We then averaged classifier accuracy across participants, and calculated one sample Bayesian t-tests comparing to chance performance at each time point as described above.
+
 ## Data and code availability
 
-Raw data, processed data, and all analysis scripts are available through the project repository at: https://.
+Raw data, processed data, and analysis scripts are freely available through the project repository at: https://osf.io/5nz2h/
 
@@
 
-# (download and) analyse individual participant data for experiment 1
+# statistical analysis for experiment 1
+processeddir <- 'local/robotsmvpa/'
+excludelist <- c(2,4,5,9,13)
 
-if (processdata > 2){
+if (processdata > 1){
 
-  legaltriggers <- 101:103
-  sublist <- dir(paste0(rawdir,'Robots'),full.names=FALSE)
-  subdirs <- dir(paste0(rawdir,'Robots'),full.names=TRUE)
+  comparisons <- matrix(c(1,2,1,3,2,3),nrow=3,ncol=2,byrow=TRUE)
 
-  for (s in 1:length(sublist)){
+datafiles <- dir(processeddir,pattern='*decoding.mat',full.names=TRUE)    
+allmvpa <- array(0,dim=c(length(datafiles),3,1201))  
+for (s in 1:length(datafiles)){
+  data <- readMat(datafiles[s])
+  allmvpa[s,,] <- data$Value/100
+}    
+times <- data$Time
 
-   if (!file.exists(paste0(processeddir,'RobotsP/R',s,'_processed.RData'))){
-    datafiles <- dir(subdirs[s],pattern='*.csv.gz',full.names=TRUE)
-
-    trialcounter <- legaltriggers*0
-    alltrials <- array(0,dim=c(3,180,64,1200))
-    for (block in 1:length(datafiles)){
-
-      EEGdata <- read.csv(datafiles[block])
-      electrodes <- colnames(EEGdata)[3:68]
-
-      # bandpass filter data
-      filt <- butter(10,1/16.666,type='low')
-      for (ch in 1:66){
-        temp <- EEGdata[,ch+2]
-        ftemp <- signal::filter(filt,temp)
-        EEGdata[,ch+2] <- ftemp
+datafiles1 <- dir(processeddir,pattern='*_101.mat',full.names=TRUE)    
+datafiles2 <- dir(processeddir,pattern='*_102.mat',full.names=TRUE)    
+datafiles3 <- dir(processeddir,pattern='*_103.mat',full.names=TRUE)    
+allmeans <- array(0,dim=c(length(datafiles1),3,66,1201))
+for (s in 1:length(datafiles1)){
+  data <- readMat(datafiles1[s])
+  allmeans[s,1,,] <- data$F*10^6
+  data <- readMat(datafiles2[s])
+  allmeans[s,2,,] <- data$F*10^6
+  data <- readMat(datafiles3[s])
+  allmeans[s,3,,] <- data$F*10^6
 }
 
-    triggertimes <- NULL
-    counter <- 0
-    lasttrigger <- -10000
-    for (n in 1:nrow(EEGdata)){
-      if (EEGdata$Trigger[n] %in% legaltriggers){
-        if (n>(lasttrigger+100)){
-        counter <- counter + 1
-        triggertimes[counter] <- n
-        lasttrigger <- n
-      }}
-    }
+allmvpa <- allmvpa[-excludelist,,]
+allmeans <- allmeans[-excludelist,,,]
 
-    for (trial in 1:counter){
-      thiscond <- which(legaltriggers==EEGdata$Trigger[triggertimes[trial]])
-      trialcounter[thiscond] <- trialcounter[thiscond] + 1
+  allRobotRTs <- array(0,dim=c(29,3,180))
+  allRobotaccuracy <- array(0,dim=c(29,3,180))
+  allRobotdprime <- matrix(0,nrow=29,ncol=3)
+  allRobottrialcounts <- matrix(0,nrow=29,ncol=3)
 
-      for (ch in 1:64){
-       temp <- EEGdata[triggertimes[trial]+(-200:999),ch+2]
-       temp <- temp - mean(temp[1:200])
-       alltrials[thiscond,trialcounter[thiscond],ch,] <- temp
+  for (s in 1:29){
+    data <- readMat(paste0('local/RawData/Experiment 1/',s+300,'/',s+300,'trialorderRobots.mat'))
+
+    trialorder <- data$R[5][[1]]
+    responses <- data$R[7][[1]]
+    RTs <- data$R[8][[1]]
+    condlist <- data$R[4][[1]]
+    condcounter <- c(0,0,0)
+    sortedRT <- matrix(0,nrow=3,ncol=180)
+    sortedresp <- matrix(0,nrow=3,ncol=180)
+
+    for (block in 1:3){
+      for (trial in 1:180){
+        cond <- condlist[trialorder[block,trial]]
+        condcounter[cond] <- condcounter[cond] + 1
+        sortedRT[cond,condcounter[cond]] <- 20*log10(RTs[block,trial] * 1000)
+        sortedresp[cond,condcounter[cond]] <- responses[block,trial] - 1
       }
@@
 
+      hits <- NULL
+  misses <- NULL
+  for (cond in 1:3){
+
+  if (cond<3){
+  hits[cond] <- condcounter[cond]-sum(sortedresp[cond,1:condcounter[cond]])
+  misses[cond] <- sum(sortedresp[cond,1:condcounter[cond]])
+  }
+  if (cond==3){
+  hits[cond] <- sum(sortedresp[cond,1:condcounter[cond]])
+  misses[cond] <- condcounter[cond]-sum(sortedresp[cond,1:condcounter[cond]])
   }
 
-    save(file=paste0(processeddir,'RobotsP/R',s,'_processed.RData'),list=c('trialcounter','alltrials'))
+  }
+    hitrate <- hits/(hits + misses)
+  for (cond in 1:3){
+    if (cond<3){falsealarms <- misses[3]/ (misses[3] + hits[3])}
+    if (cond==3){falsealarms <- sum(misses[1:2]) / (sum(misses[1:2]) + sum(hits[1:2]))}
+  allRobotdprime[s,cond] <- qnorm(hitrate[cond]) - qnorm(falsealarms)
+  }
+
+    allRobotRTs[s,,] <- sortedRT
+    allRobotaccuracy[s,,] <- sortedresp
+    allRobottrialcounts[s,] <- condcounter
+  }
+
+allRobotdprime[which(is.infinite(allRobotdprime))] <- 5
+meanRobotRTs <- apply(allRobotRTs,1:2,mean)
+
+dataforANOVA <- melt(allRobotdprime)
+colnames(dataforANOVA) <- c('Participant','Condition','dprime')
+dataforANOVA$Participant <- as.factor(dataforANOVA$Participant)
+dataforANOVA$Condition <- as.factor(dataforANOVA$Condition)
+bfdprime <- extractBF(anovaBF(dprime ~ Condition,dataforANOVA,whichRandom='Participant'))$bf
+
+bfcontrasts <- NULL
+for (comp in 1:3){
+bfcontrasts[comp] <- extractBF(ttestBF(allRobotdprime[,comparisons[comp,1]],allRobotdprime[,comparisons[comp,2]],paired=TRUE))$bf}
+
+dataforANOVA <- melt(meanRobotRTs)
+colnames(dataforANOVA) <- c('Participant','Condition','RT')
+dataforANOVA$Participant <- as.factor(dataforANOVA$Participant)
+dataforANOVA$Condition <- as.factor(dataforANOVA$Condition)
+bfRT <- extractBF(anovaBF(RT ~ Condition,dataforANOVA,whichRandom='Participant'))$bf
+
+bfcontrastsRT <- NULL
+for (comp in 1:3){
+bfcontrastsRT[comp] <- extractBF(ttestBF(meanRobotRTs[,comparisons[comp,1]],meanRobotRTs[,comparisons[comp,2]],paired=TRUE))$bf}
+
+subjmeanERP <- apply(allmeans,c(1,3,4),mean)
+meanERP <- apply(allmeans,2:4,mean)
+meanMVPA <- apply(allmvpa,2:3,mean)
+grandmeanERP <- apply(subjmeanERP[,targetelectrodes,],3,mean)
+subjERPs <- apply(subjmeanERP[,targetelectrodes,],c(1,3),mean)
+condERPs <- apply(allmeans[,,targetelectrodes,],c(1,2,4),mean)
+
+mlimits <- matrix(0,nrow=6,ncol=1201)
+mBF <- matrix(0,nrow=3,ncol=1201)
+bspop <- 1:nbootstraps
+for (n in 1:1201){
+
+  for (cond in 1:3){
+  for (b in 1:nbootstraps){
+    bspop[b] <- mean(sample(allmvpa[,cond,n],replace=TRUE))
+  }
+mlimits[(1:2)+((cond-1)*2),n] <- quantile(bspop,probs=c(0.025,0.975)) 
+mBF[cond,n] <- extractBF(ttestBF(allmvpa[,cond,n],mu=0.5))$bf
   }
@@
 
+limits <- matrix(0,nrow=8,ncol=1201)
+ERP_BF <- matrix(0,nrow=3,ncol=1201)
+bspop <- 1:nbootstraps
+for (n in 1:1201){
+
+  for (b in 1:nbootstraps){
+    bspop[b] <- mean(sample(subjERPs[,n],replace=TRUE))
+  }
+  limits[1:2,n] <- quantile(bspop,probs=c(0.025,0.975))
+
+  for (cond in 1:3){
+  for (b in 1:nbootstraps){
+    bspop[b] <- mean(sample(condERPs[,cond,n],replace=TRUE))
+  }
+  limits[(1:2)+(cond*2),n] <- quantile(bspop,probs=c(0.025,0.975)) 
+  ERP_BF[cond,n] <- extractBF(ttestBF(condERPs[,comparisons[cond,1],n],condERPs[,comparisons[cond,2],n],paired=TRUE))$bf
+  }
 }
 
-```
+chlist <- readMat('local/channel.mat')
+chanlabels <- unlist(chlist$HeadPoints[[2]])
+chanlocs <- read.csv('local/channeldata.csv')
 
-```{r include=FALSE, results='hide'}
-
-# do MVPA for experiment 1
-
-if (processdata > 1){
+save(file='local/GroupDataRobots.RData',list=c('allmeans','allmvpa','mlimits','subjmeanERP','limits','grandmeanERP','subjERPs','condERPs','meanMVPA','meanERP','mBF','ERP_BF','allRobotdprime','meanRobotRTs','bfdprime','bfRT','bfcontrasts','bfcontrastsRT','chanlocs','chanlabels'))
 
@@
 
+if (file.exists('local/GroupDataRobots.RData')){load('local/GroupDataRobots.RData')}  
 if (processdata > 0){
+
+pdf(paste0('Figures/RobotsData.pdf'), bg="transparent", height = 12, width = 12)
+
+par(mfrow=c(2,2))
+
+  plotlims <- c(0,5,0.5,3.5)  
+  ticklocsy <- c(0.5,1,2,3,3.5)    
+  ticklocsx <- 0:5    # locations of tick marks on y axis
+  ticklabelsy <- c("","Robot","Android","Human","")       
+  ticklabelsx <- ticklocsx    # set labels for y ticks
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  mtext(text = ticklabelsx, side = 1, at=ticklocsx,line=0.5,cex=1.5)     
+  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=3,cex=1.5) 
+  title(xlab="d prime", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.8)
+
+  text(0.15,3.3,'(a)',cex=3)
+
+  a <- density(allRobotdprime[,1],cut=6)
+  a$y <- 0.35*a$y/max(a$y)
+  polygon(a$x,1.1+a$y,border=NA,col=addalpha(collist[1],0.5))
+
+    a <- density(allRobotdprime[,2])
+  a$y <- 0.35*a$y/max(a$y)
+  polygon(a$x,2.1+a$y,border=NA,col=addalpha(collist[2],0.5))
+
+    a <- density(allRobotdprime[,3])
+  a$y <- 0.35*a$y/max(a$y)
+  polygon(a$x,3.1+a$y,border=NA,col=addalpha(collist[3],0.5))
+
+  xvals <- seq(-0.1,0.1,length=nrow(allRobotdprime))
+  points(allRobotdprime[,1],1+xvals-0.2,pch=16,col=collist[1])
+  points(allRobotdprime[,2],2+xvals-0.2,pch=15,col=collist[2])
+  points(allRobotdprime[,3],3+xvals-0.2,pch=18,col=collist[3])
+
+  for (cond in 1:3){
+  bs <- NULL
+  for (n in 1:nbootstraps){bs[n] <- mean(sample(allRobotdprime[,cond],replace=TRUE))}
+  ci <- quantile(bs,c(0.025,0.975))
+  arrows(mean(allRobotdprime[,cond]),cond,ci[1],cond,angle=90,length=0.1,lwd=3)
+  arrows(mean(allRobotdprime[,cond]),cond,ci[2],cond,angle=90,length=0.1,lwd=3)
+  }
+
+  points(mean(allRobotdprime[,1]),1,pch=21,cex=2,lwd=2,bg=collist[1])
+  points(mean(allRobotdprime[,2]),2,pch=22,cex=2,lwd=2,bg=collist[2])
+  points(mean(allRobotdprime[,3]),3,pch=23,cex=2,lwd=2,bg=collist[3])
+
+  plotlims <- c(52,64,0.5,3.5)  
+  ticklocsy <- c(0.5,1,2,3,3.5)    
+  ticklocsx <- c(52,58,64)    
+  ticklabelsy <- c("","Robot","Android","Human","")       
+  ticklabelsx <- c(400,800,1600)    # set labels for y ticks
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.5, cex=1.5)     
+  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=3,cex=1.5) 
+  title(xlab="Reaction time (ms)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.8)
+
+    text(20*log10(420),3.3,'(b)',cex=3)
+
+  a <- density(meanRobotRTs[,1],cut=6)
+  a$y <- 0.35*a$y/max(a$y)
+  polygon(a$x,1.1+a$y,border=NA,col=addalpha(collist[1],0.5))
+
+    a <- density(meanRobotRTs[,2])
+  a$y <- 0.35*a$y/max(a$y)
+  polygon(a$x,2.1+a$y,border=NA,col=addalpha(collist[2],0.5))
+
+    a <- density(meanRobotRTs[,3])
+  a$y <- 0.35*a$y/max(a$y)
+  polygon(a$x,3.1+a$y,border=NA,col=addalpha(collist[3],0.5))
+
+  xvals <- seq(-0.1,0.1,length=nrow(meanRobotRTs))
+  points(meanRobotRTs[,1],1+xvals-0.2,pch=16,col=collist[1])
+  points(meanRobotRTs[,2],2+xvals-0.2,pch=15,col=collist[2])
+  points(meanRobotRTs[,3],3+xvals-0.2,pch=18,col=collist[3])
+
+  for (cond in 1:3){
+  bs <- NULL
+  for (n in 1:nbootstraps){bs[n] <- mean(sample(meanRobotRTs[,cond],replace=TRUE))}
+  ci <- quantile(bs,c(0.025,0.975))
+  arrows(mean(meanRobotRTs[,cond]),cond,ci[1],cond,angle=90,length=0.1,lwd=3)
+  arrows(mean(meanRobotRTs[,cond]),cond,ci[2],cond,angle=90,length=0.1,lwd=3)
+  }
+  points(mean(meanRobotRTs[,1]),1,pch=21,cex=2,lwd=2,bg=collist[1])
+  points(mean(meanRobotRTs[,2]),2,pch=22,cex=2,lwd=2,bg=collist[2])
+  points(mean(meanRobotRTs[,3]),3,pch=23,cex=2,lwd=2,bg=collist[3])
+
+par(mfrow=c(2,1),mfg=c(2,1))
+
+plotlims <- c(-200,1000,-12,12)  
+ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
+ticklocsy <- seq(-12,12,4)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.5, cex=1.5)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1.5)  
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.8)   
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1.8)
+
+  text(-200,10,'(c)',cex=3)
+
+lines(c(-200,1000),c(0,0),lty=1)
+lines(c(0,0),c(-20,20),lty=1)
+polygon(c(0,500,500,0),c(-13,-13,-11,-11),col=rgb(0,0,0,0.3),border=NA)
+
+polygon(c(-200:1000,1000:-200), c(limits[1,],limits[2,1201:1]), col=rgb(0,0,0,0.1),border=NA)
+
+lines(-200:1000, grandmeanERP, lwd=3)
+
+  text(105,9.5,'P100',cex=2)
+  text(155,-4,'N170',cex=2)
+  text(250,4,'P200',cex=2)
+
+chanindex <- match(toupper(chanlabels),toupper(chanlocs$Electrode))
+chanxy <- chanlocs[chanindex,2:3]
+lines(150*chanlocs$OutlineX-100,7.5*chanlocs$OutlineY + 6, lwd=2)
+lines(150*chanlocs$NoseX-100,7.5*chanlocs$NoseY + 6, lwd=2)
+lines(150*chanlocs$LearX-100,7.5*chanlocs$LearY + 6, lwd=2)
+lines(150*chanlocs$RearX-100,7.5*chanlocs$RearY + 6, lwd=2)
+points(150*chanlocs$X_position[1:64]-100,7.5*chanlocs$Y_position[1:64] + 6, pch=16,col='lightgrey')
+points(150*chanlocs$X_position[chanindex[targetelectrodes]]-100,7.5*chanlocs$Y_position[chanindex[targetelectrodes]] + 6, pch=16,col='black')
+
+dev.off()
+
+pdf(paste0('Figures/RobotsMVPA.pdf'), bg="transparent", height = 12, width = 24)
+
+par(mfrow=c(2,2))
+
+times <- -199:1200
+
+plotlims <- c(-200,1000,-12,12)  
+ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
+ticklocsy <- seq(-12,12,4)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)    
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.5, cex=1.5)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1.5)  
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.8)   
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1.8)
+
+lines(c(-200,1000),c(0,0),lty=1)
+lines(c(0,0),c(-20,20),lty=1)
+polygon(c(0,500,500,0),c(-13,-13,-11,-11),col=rgb(0,0,0,0.3),border=NA)
+
+polygon(c(-200:1000,1000:-200), c(limits[3,],limits[4,1201:1]), col=addalpha(collist[1],0.3),border=NA)
+polygon(c(-200:1000,1000:-200), c(limits[7,],limits[8,1201:1]), col=addalpha(collist[3],0.3),border=NA)
+
+lines(-200:1000, colMeans(meanERP[1,targetelectrodes,]), lwd=3, col=collist[1])     
+lines(-200:1000, colMeans(meanERP[3,targetelectrodes,]), lwd=3, col=collist[3])
+
+chanindex <- match(toupper(chanlabels),toupper(chanlocs$Electrode))
+chanxy <- chanlocs[chanindex,2:3]
+lines(150*chanlocs$OutlineX-100,7.5*chanlocs$OutlineY + 6, lwd=2)
+lines(150*chanlocs$NoseX-100,7.5*chanlocs$NoseY + 6, lwd=2)
+lines(150*chanlocs$LearX-100,7.5*chanlocs$LearY + 6, lwd=2)
+lines(150*chanlocs$RearX-100,7.5*chanlocs$RearY + 6, lwd=2)
+points(150*chanlocs$X_position[1:64]-100,7.5*chanlocs$Y_position[1:64] + 6, pch=16,col='lightgrey')
+points(150*chanlocs$X_position[chanindex[targetelectrodes]]-100,7.5*chanlocs$Y_position[chanindex[targetelectrodes]] + 6, pch=16,col='black')
+
+allbfs <- ERP_BF[2,]
+
+linestartstop <- times[allbfs>=3 & allbfs<10]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], -c(8.5,8.5,7.5,7.5), col=bfcols[1],border=NA)}}
+
+linestartstop <- times[allbfs>=10 & allbfs<30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], -c(8.5,8.5,7.5,7.5), col=bfcols[2],border=NA)}}
+
+linestartstop <- times[allbfs>=30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], -c(8.5,8.5,7.5,7.5), col=bfcols[3],border=NA)}}
+
+legend(700,12,c('Human','Robot'),lty=1,lwd=3,col=collist[c(3,1)],cex=1.8,box.lwd=2)
+text(-190,11,'(a)',cex=3)
+
+legend(-200,-6,c('BF>3','BF>10','BF>30'),lwd=5,col=bfcols, box.lwd=2, cex=1.5)
+
+plotlims <- c(-200,1000,-12,12)  
+ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
+ticklocsy <- seq(-12,12,4)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.5, cex=1.5)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1.5)  
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.8)   
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1.8)
+
+lines(c(-200,1000),c(0,0),lty=1)
+lines(c(0,0),c(-20,20),lty=1)
+polygon(c(0,500,500,0),c(-13,-13,-11,-11),col=rgb(0,0,0,0.3),border=NA)
+
+polygon(c(-200:1000,1000:-200), c(limits[5,],limits[6,1201:1]), col=addalpha(collist[2],0.3),border=NA)
+polygon(c(-200:1000,1000:-200), c(limits[7,],limits[8,1201:1]), col=addalpha(collist[3],0.3),border=NA)
+
+lines(-200:1000, colMeans(meanERP[2,targetelectrodes,]), lwd=3, col=collist[2])     
+lines(-200:1000, colMeans(meanERP[3,targetelectrodes,]), lwd=3, col=collist[3])
+
+chanindex <- match(toupper(chanlabels),toupper(chanlocs$Electrode))
+chanxy <- chanlocs[chanindex,2:3]
+lines(150*chanlocs$OutlineX-100,7.5*chanlocs$OutlineY + 6, lwd=2)
+lines(150*chanlocs$NoseX-100,7.5*chanlocs$NoseY + 6, lwd=2)
+lines(150*chanlocs$LearX-100,7.5*chanlocs$LearY + 6, lwd=2)
+lines(150*chanlocs$RearX-100,7.5*chanlocs$RearY + 6, lwd=2)
+points(150*chanlocs$X_position[1:64]-100,7.5*chanlocs$Y_position[1:64] + 6, pch=16,col='lightgrey')
+points(150*chanlocs$X_position[chanindex[targetelectrodes]]-100,7.5*chanlocs$Y_position[chanindex[targetelectrodes]] + 6, pch=16,col='black')
+
+allbfs <- ERP_BF[3,]
+
+linestartstop <- times[allbfs>=3 & allbfs<10]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], -c(8.5,8.5,7.5,7.5), col=bfcols[1],border=NA)}}
+
+linestartstop <- times[allbfs>=10 & allbfs<30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], -c(8.5,8.5,7.5,7.5), col=bfcols[2],border=NA)}}
+
+linestartstop <- times[allbfs>=30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], -c(8.5,8.5,7.5,7.5), col=bfcols[3],border=NA)}}
+
+legend(700,12,c('Human','Android'),lty=1,lwd=3,col=collist[c(3,2)],cex=1.8,box.lwd=2)
+text(-190,11,'(b)',cex=3)
+
+legend(-200,-6,c('BF>3','BF>10','BF>30'),lwd=5,col=bfcols, box.lwd=2, cex=1.5)
+
+plotlims <- c(-200,1000,0,1) 
+ticklocsx <- seq(-200,1000,200)  
+ticklocsy <- seq(0,1,0.25)    
+ticklabelsx <- ticklocsx      
+ticklabelsy <- ticklocsy*100
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+
+mtext(text = ticklabelsx, side = 1, at=ticklocsx,line=0.5,cex=1.5)  
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1,cex=1.5) 
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.8)  #}    
+title(ylab="Classifier accuracy (%)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1.8)
+text(-190,0.95,'(c)',cex=3)
+
+lines(c(-200, 1000),c(0.5, 0.5), col='black', lty=2)
+lines(c(0,0),c(0,1), col='black')
+
+polygon(c(-200:1000,1000:-200), c(mlimits[3,],mlimits[4,1201:1]), col=addalpha(collist[2],0.3),border=NA)
+
+lines(-200:1000,meanMVPA[2,], col=collist[2], lwd=3, cex=0.5)
+
+allbfs <- mBF[2,]
+
+linestartstop <- times[allbfs>=3 & allbfs<10]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.24,0.24,0.26,0.26), col=bfcols[1],border=NA)}}
+
+linestartstop <- times[allbfs>=10 & allbfs<30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.24,0.24,0.26,0.26), col=bfcols[2],border=NA)}}
+
+linestartstop <- times[allbfs>=30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.24,0.24,0.26,0.26), col=bfcols[3],border=NA)}}
+
+legend(-200,0.25,c('BF>3','BF>10','BF>30'),lwd=5,col=bfcols, box.lwd=2, cex=1.5)
+
+plotlims <- c(-200,1000,0,1) 
+ticklocsx <- seq(-200,1000,200)  
+ticklocsy <- seq(0,1,0.25)    
+ticklabelsx <- ticklocsx      
+ticklabelsy <- ticklocsy*100
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+
+mtext(text = ticklabelsx, side = 1, at=ticklocsx,line=0.5,cex=1.5)  
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1,cex=1.5) 
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.8)  #}    
+title(ylab="Classifier accuracy (%)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1.8)
+text(-190,0.95,'(d)',cex=3)
+
+lines(c(-200, 1000),c(0.5, 0.5), col='black', lty=2)
+lines(c(0,0),c(0,1), col='black')
+
+polygon(c(-200:1000,1000:-200), c(mlimits[5,],mlimits[6,1201:1]), col=addalpha(collist[3],0.3),border=NA)
+
+lines(-200:1000,meanMVPA[3,], col=collist[3], lwd=3, cex=0.5)
+
+allbfs <- mBF[3,]
+
+linestartstop <- times[allbfs>=3 & allbfs<10]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.24,0.24,0.26,0.26), col=bfcols[1],border=NA)}}
+
+linestartstop <- times[allbfs>=10 & allbfs<30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.24,0.24,0.26,0.26), col=bfcols[2],border=NA)}}
+
+linestartstop <- times[allbfs>=30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.24,0.24,0.26,0.26), col=bfcols[3],border=NA)}}
+
+legend(-200,0.25,c('BF>3','BF>10','BF>30'),lwd=5,col=bfcols, box.lwd=2, cex=1.5)
+
+dev.off()
 
@@
 
+conddprimes <- colMeans(allRobotdprime)
+condRTs <- 10^(colMeans(meanRobotRTs)/20)
+
 ```
+
+We first explored the behavioural results for identification of human versus non-human stimuli.
+We calculated d-prime scores to compare sensitivity across conditions.
+Sensitivity was highest for identifying robots (d' = `r round(conddprimes[1],digits=2)`), but still well above chance for both the human (d' = `r round(conddprimes[3],digits=2)`) and android (d' = `r round(conddprimes[2],digits=2)`) conditions.
+The Bayes factor score for a one-way ANOVA comparing these three conditions indicated very substantial evidence ($log_{10}BF_{10} =$ `r round(log10(bfdprime),digits=2)`) for a difference between conditions, as illustrated in Figure \ref{fig:RobotsData}a.
+Pairwise Bayesian t-tests between conditions indicate very convincing differences in sensitivity between robots and androids ($log_{10}BF_{10} =$ `r round(log10(bfcontrasts[1]),digits=2)`) and robots and humans ($log_{10}BF_{10} =$ `r round(log10(bfcontrasts[2]),digits=2)`).
+The difference between androids and humans ($log_{10}BF_{10} =$ `r round(log10(bfcontrasts[3]),digits=2)`) was also very substantial.
+
+Reaction times also differed between conditions, though the effects were rather smaller.
+Reactions were fastest for identifying robots (RT = `r round(condRTs[1],digits=0)`ms), compared with humans (RT = `r round(condRTs[3],digits=0)`ms) and androids (RT = `r round(condRTs[2],digits=0)`ms).
+The Bayes factor score for a one-way ANOVA comparing these three conditions indicated strong evidence ($log_{10}BF_{10} =$ `r round(log10(bfRT),digits=2)`) for a difference between conditions, as illustrated in Figure \ref{fig:RobotsData}b.
+Pairwise Bayesian t-tests between conditions indicate very convincing differences in sensitivity between robots and androids ($log_{10}BF_{10} =$ `r round(log10(bfcontrastsRT[1]),digits=2)`) and robots and humans ($log_{10}BF_{10} =$ `r round(log10(bfcontrastsRT[2]),digits=2)`), whereas the reaction time was equivalent between androids and humans ($log_{10}BF_{10} =$ `r round(log10(bfcontrastsRT[3]),digits=2)`).
+
+```{r RobotsData, fig.cap="Summary of response data and grand mean ERP for Experiment 1.
+Panel (a) shows d-prime scores for identifying images of human (blue), android (green) and robot (red) faces.
+Small points show individual participants, and the larger symbols with error bars indicate the group mean and bootstrapped 95 percent confidence intervals.
+Panel (b) plots reaction times in the same format (note the logarithmic x-axis).
+Panel (c) shows the grant mean ERP across all participants and conditions, pooled across electrodes P6, P8, PO6 and PO8 (see inset).
+The shaded region around the curve illustrates the 95 percent confidence interval, and the grey rectangle at the foot indicates the stimulus duration.", fig.align="center", echo=FALSE, fig.width=12, fig.height=12}
+
+knitr::include_graphics('Figures/RobotsData.pdf')
+
+```
+
+EEG activity showed a clear visually evoked potential over posterior electrode sites (see Figure \ref{fig:RobotsData}c), with typical components found in response to visual stimuli (the P100, N170 and P200 are indicated in the figure).
+Pairwise comparisons of conditions are shown in Figure \ref{fig:RobotsMVPA}a,b.
+In general there is a tendency for the ERP response to human faces to diverge slightly from the other two conditions, however the evidence for a convincing difference was not compelling.
+Bayes factors exceeded 3 for only a small number of time points around 300-400ms in the comparison between human and robot images (see yellow bars at y = -8 in Figure \ref{fig:RobotsMVPA}a), but these differences were small considering the variance in the data.
+
+```{r RobotsMVPA, fig.cap="Univariate and multivariate comparisons across image type.
+Panel (a) shows the ERPs comparing human (blue) and robot (red) face images, and panel (b) compares human (blue) and android (green) faces.
+Panels (c) and (d) show multivariate pattern classification accuracy for the same comparisons.
+Points at y = -8 and y = 25 indicate Bayes factor scores for comparisons between ERPs (a,b) and comparing classification accuracy to chance (50 percent correct; c,d).", fig.align="center", echo=FALSE, fig.width=12, fig.height=12}
+
+knitr::include_graphics('Figures/RobotsMVPA.pdf')
+
+```
+
+We also conducted multivariate pattern analysis independently at each time-point for the same two comparisons.
+The evoked responses for human and robot images caused sufficiently distinct patterns of voltages across the scalp that the pattern classifier could distinguish them from around 100 ms following stimulus onset, with accuracy up to `r round(100*max(meanMVPA[2,]),digits=0)`\% correct (see Figure \ref{fig:RobotsMVPA}c).
+Bayes factors exceeded 30 for much of the time window between 100 and 800 ms, indicating that the decoding was meaningfully above chance performance (50\% correct).
+It was also possible to classify between human and android images (see Figure \ref{fig:RobotsMVPA}d), however performance was much poorer, with a maximum of `r round(100*max(meanMVPA[3,]),digits=0)`\% correct.
+Classification accuracy had an initial peak around 100ms that provided compelling evidence for above chance classification (BF>30), and a later region of above-chance classification between 500 and 700ms.
+In the Discussion we speculate that these two time periods might correspond to distinct types of signal associated with the uncanny valley.
+However we first sought to generalise our results to a different stimulus set, and next report the results of Experiment 2 which used hyper-realistic silicone masks.
 
@@
 
-# (download and) analyse individual participant data for experiment 2
+# statistical analysis for experiment 2
+processeddir <- 'local/masksmvpa/'
+excludelist <- c(3,16,24,26,29)
 
-if (processdata > 2){
+if (processdata > 1){
 
-  # 100: asian, 200: western
-  # 11: halloween, 12: silicone, 23: real
-  legaltriggers <- c(111,112,123,211,212,223)
-  sublist <- dir(paste0(rawdir,'Masks'),full.names=FALSE)
-  subdirs <- dir(paste0(rawdir,'Masks'),full.names=TRUE)
+datafiles <- dir(processeddir,pattern='*decoding.mat',full.names=TRUE)    
+allmvpa <- array(0,dim=c(length(datafiles),3,1201))  
+for (s in 1:length(datafiles)){
+  data <- readMat(datafiles[s])
+  allmvpa[s,,] <- data$Value/100
+}    
+times <- data$Time
 
-  for (s in 1:length(sublist)){
-
-    if (!file.exists(paste0(processeddir,'MasksP/M',s,'_processed.RData'))){
-    datafiles <- dir(subdirs[s],pattern='*.csv.gz',full.names=TRUE)
-
-    trialcounter <- matrix(0,nrow=3,ncol=6)
-    alltrials <- array(0,dim=c(3,6,76,64,1200))
-    for (block in 1:3){
-
-      EEGdata <- read.csv(datafiles[block])
-      electrodes <- colnames(EEGdata)[3:68]
-
-      # bandpass filter data
-      filt <- butter(10,1/16.666,type='low')
-      for (ch in 1:66){
-        temp <- EEGdata[,ch+2]
-        ftemp <- signal::filter(filt,temp)
-        EEGdata[,ch+2] <- ftemp
+datafiles1 <- dir(processeddir,pattern='*_101.mat',full.names=TRUE)    
+datafiles2 <- dir(processeddir,pattern='*_102.mat',full.names=TRUE)    
+datafiles3 <- dir(processeddir,pattern='*_103.mat',full.names=TRUE)    
+allmeans <- array(0,dim=c(length(datafiles1),3,66,1201))
+for (s in 1:length(datafiles1)){
+  data <- readMat(datafiles1[s])
+  allmeans[s,1,,] <- data$F*10^6
+  data <- readMat(datafiles2[s])
+  allmeans[s,2,,] <- data$F*10^6
+  data <- readMat(datafiles3[s])
+  allmeans[s,3,,] <- data$F*10^6
 }
 
-    triggertimes <- NULL
-    counter <- 0
-    lasttrigger <- -10000
-    for (n in 1:nrow(EEGdata)){
-      if (EEGdata$Trigger[n] %in% legaltriggers){
-        if (n>(lasttrigger+100)){
-        counter <- counter + 1
-        triggertimes[counter] <- n
-        lasttrigger <- n
-      }}
-    }
+allmvpa <- allmvpa[-excludelist,,]
+allmeans <- allmeans[-excludelist,,,]
 
-    for (trial in 1:counter){
-      thiscond <- which(legaltriggers==EEGdata$Trigger[triggertimes[trial]])
-      trialcounter[block,thiscond] <- trialcounter[block,thiscond] + 1
+  allMaskRTs <- array(0,dim=c(30,3,444))
+  allMaskaccuracy <- array(0,dim=c(30,3,444))
+  allMaskdprime <- matrix(0,nrow=30,ncol=3)
+  allMasktrialcounts <- matrix(0,nrow=30,ncol=3)
 
-      for (ch in 1:64){
-       temp <- EEGdata[triggertimes[trial]+(-200:999),ch+2]
-       temp <- temp - mean(temp[1:200])
-       alltrials[block,thiscond,trialcounter[block,thiscond],ch,] <- temp
+  for (s in 1:30){
+    data <- readMat(paste0('local/RawData/Experiment 2/',s+350,'/trialorderMasks.mat'))
+
+    trialorder <- data$R[7][[1]]
+    responses <- data$R[9][[1]]
+    RTs <- data$R[10][[1]]
+    condlist <- data$R[6][[1]]
+    condcounter <- c(0,0,0)
+    sortedRT <- matrix(0,nrow=3,ncol=444)
+    sortedresp <- matrix(0,nrow=3,ncol=444)
+
+    for (block in 1:3){
+      for (trial in 1:296){
+        cond <- condlist[trialorder[block,trial]]
+        condcounter[cond] <- condcounter[cond] + 1
+        sortedRT[cond,condcounter[cond]] <- 20*log10(RTs[block,trial] * 1000)
+        sortedresp[cond,condcounter[cond]] <- responses[block,trial] - 1
       }
@@
 
+      hits <- NULL
+  misses <- NULL
+  for (cond in 1:3){
+
+  if (cond<3){
+  hits[cond] <- condcounter[cond]-sum(sortedresp[cond,1:condcounter[cond]])
+  misses[cond] <- sum(sortedresp[cond,1:condcounter[cond]])
+  }
+  if (cond==3){
+  hits[cond] <- sum(sortedresp[cond,1:condcounter[cond]])
+  misses[cond] <- condcounter[cond]-sum(sortedresp[cond,1:condcounter[cond]])
   }
 
-    save(file=paste0(processeddir,'MasksP/M',s,'_processed.RData'),list=c('trialcounter','alltrials'))
   }
+    hitrate <- hits/(hits + misses)
+  for (cond in 1:3){
+    if (cond<3){falsealarms <- misses[3]/ (misses[3] + hits[3])}
+    if (cond==3){falsealarms <- sum(misses[1:2]) / (sum(misses[1:2]) + sum(hits[1:2]))}
+  allMaskdprime[s,cond] <- qnorm(hitrate[cond]) - qnorm(falsealarms)
+  }
+
+    allMaskRTs[s,,] <- sortedRT
+    allMaskaccuracy[s,,] <- sortedresp
+    allMasktrialcounts[s,] <- condcounter
+  }
+
+allMaskdprime[which(is.infinite(allMaskdprime))] <- 5
+
+meanMaskRTs <- matrix(0,nrow=30,ncol=3)
+for (s in 1:30){
+  for (cond in 1:3){
+    meanMaskRTs[s,cond] <- mean(allMaskRTs[s,cond,1:allMasktrialcounts[s,cond]])
   }
@@
 
-```
+dataforANOVA <- melt(allMaskdprime)
+colnames(dataforANOVA) <- c('Participant','Condition','dprime')
+dataforANOVA$Participant <- as.factor(dataforANOVA$Participant)
+dataforANOVA$Condition <- as.factor(dataforANOVA$Condition)
+bfdprime <- extractBF(anovaBF(dprime ~ Condition,dataforANOVA,whichRandom='Participant'))$bf
 
-```{r include=FALSE, results='hide'}
+bfcontrasts <- NULL
+for (comp in 1:3){
+bfcontrasts[comp] <- extractBF(ttestBF(allMaskdprime[,comparisons[comp,1]],allMaskdprime[,comparisons[comp,2]],paired=TRUE))$bf}
 
-# do MVPA for experiment 2
+dataforANOVA <- melt(meanMaskRTs)
+colnames(dataforANOVA) <- c('Participant','Condition','RT')
+dataforANOVA$Participant <- as.factor(dataforANOVA$Participant)
+dataforANOVA$Condition <- as.factor(dataforANOVA$Condition)
+bfRT <- extractBF(anovaBF(RT ~ Condition,dataforANOVA,whichRandom='Participant'))$bf
 
-if (processdata > 1){
+bfcontrastsRT <- NULL
+for (comp in 1:3){
+bfcontrastsRT[comp] <- extractBF(ttestBF(meanMaskRTs[,comparisons[comp,1]],meanMaskRTs[,comparisons[comp,2]],paired=TRUE))$bf}
 
+subjmeanERP <- apply(allmeans,c(1,3,4),mean)
+meanERP <- apply(allmeans,2:4,mean)
+meanMVPA <- apply(allmvpa,2:3,mean)
+grandmeanERP <- apply(subjmeanERP[,targetelectrodes,],3,mean)
+subjERPs <- apply(subjmeanERP[,targetelectrodes,],c(1,3),mean)
+condERPs <- apply(allmeans[,,targetelectrodes,],c(1,2,4),mean)
+
+mlimits <- matrix(0,nrow=6,ncol=1201)
+mBF <- matrix(0,nrow=3,ncol=1201)
+bspop <- 1:nbootstraps
+for (n in 1:1201){
+
+  for (cond in 1:3){
+  for (b in 1:nbootstraps){
+    bspop[b] <- mean(sample(allmvpa[,cond,n],replace=TRUE))
+  }
+mlimits[(1:2)+((cond-1)*2),n] <- quantile(bspop,probs=c(0.025,0.975)) 
+mBF[cond,n] <- extractBF(ttestBF(allmvpa[,cond,n],mu=0.5))$bf
+  }
+}
+
+comparisons <- matrix(c(1,2,1,3,2,3),nrow=3,ncol=2,byrow=TRUE)
+limits <- matrix(0,nrow=8,ncol=1201)
+ERP_BF <- matrix(0,nrow=3,ncol=1201)
+bspop <- 1:nbootstraps
+for (n in 1:1201){
+
+  for (b in 1:nbootstraps){
+    bspop[b] <- mean(sample(subjERPs[,n],replace=TRUE))
+  }
+  limits[1:2,n] <- quantile(bspop,probs=c(0.025,0.975))
+
+  for (cond in 1:3){
+  for (b in 1:nbootstraps){
+    bspop[b] <- mean(sample(condERPs[,cond,n],replace=TRUE))
+  }
+  limits[(1:2)+(cond*2),n] <- quantile(bspop,probs=c(0.025,0.975)) 
+  ERP_BF[cond,n] <- extractBF(ttestBF(condERPs[,comparisons[cond,1],n],condERPs[,comparisons[cond,2],n],paired=TRUE))$bf
+  }
+}
+
+chlist <- readMat('local/channel.mat')
+chanlabels <- unlist(chlist$HeadPoints[[2]])
+chanlocs <- read.csv('local/channeldata.csv')
+
+save(file='local/GroupDataMasks.RData',list=c('allmeans','allmvpa','mlimits','subjmeanERP','limits','grandmeanERP','subjERPs','condERPs','meanMVPA','meanERP','mBF','ERP_BF','allMaskdprime','meanMaskRTs','bfdprime','bfRT','bfcontrasts','bfcontrastsRT','chanlocs','chanlabels'))
 }
@@
 
+if (file.exists('local/GroupDataMasks.RData')){load('local/GroupDataMasks.RData')}  
 if (processdata > 0){
+
+pdf(paste0('Figures/MasksData.pdf'), bg="transparent", height = 12, width = 12)
+
+par(mfrow=c(2,2))
+
+  plotlims <- c(0,5,0.5,3.5)  
+  ticklocsy <- c(0.5,1,2,3,3.5)    
+  ticklocsx <- 0:5    # locations of tick marks on y axis
+  ticklabelsy <- c("","Halloween","Silicone","Human","")       
+  ticklabelsx <- ticklocsx    # set labels for y ticks
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  mtext(text = ticklabelsx, side = 1, at=ticklocsx,line=0.5,cex=1.5)     
+  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=3,cex=1.5) 
+  title(xlab="d prime", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.8)
+
+  text(0.15,3.3,'(a)',cex=3)
+
+  a <- density(allMaskdprime[,1],cut=6)
+  a$y <- 0.35*a$y/max(a$y)
+  polygon(a$x,1.1+a$y,border=NA,col=addalpha(collist[1],0.5))
+
+    a <- density(allMaskdprime[,2])
+  a$y <- 0.35*a$y/max(a$y)
+  polygon(a$x,2.1+a$y,border=NA,col=addalpha(collist[2],0.5))
+
+    a <- density(allMaskdprime[,3])
+  a$y <- 0.35*a$y/max(a$y)
+  polygon(a$x,3.1+a$y,border=NA,col=addalpha(collist[3],0.5))
+
+  xvals <- seq(-0.1,0.1,length=nrow(allMaskdprime))
+  points(allMaskdprime[,1],1+xvals-0.2,pch=16,col=collist[1])
+  points(allMaskdprime[,2],2+xvals-0.2,pch=15,col=collist[2])
+  points(allMaskdprime[,3],3+xvals-0.2,pch=18,col=collist[3])
+
+  for (cond in 1:3){
+  bs <- NULL
+  for (n in 1:nbootstraps){bs[n] <- mean(sample(allMaskdprime[,cond],replace=TRUE))}
+  ci <- quantile(bs,c(0.025,0.975))
+  arrows(mean(allMaskdprime[,cond]),cond,ci[1],cond,angle=90,length=0.1,lwd=3)
+  arrows(mean(allMaskdprime[,cond]),cond,ci[2],cond,angle=90,length=0.1,lwd=3)
+  }
+
+  points(mean(allMaskdprime[,1]),1,pch=21,cex=2,lwd=2,bg=collist[1])
+  points(mean(allMaskdprime[,2]),2,pch=22,cex=2,lwd=2,bg=collist[2])
+  points(mean(allMaskdprime[,3]),3,pch=23,cex=2,lwd=2,bg=collist[3])
+
+  plotlims <- c(49,61,0.5,3.5)  
+  ticklocsy <- c(0.5,1,2,3,3.5)    
+  ticklocsx <- seq(49,61,3)
+  ticklabelsy <- c("","Halloween","Silicone","Human","")       
+  ticklabelsx <- c('','400','','800','')    # set labels for y ticks
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.5, cex=1.5)     
+  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=3,cex=1.5) 
+  title(xlab="Reaction time (ms)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.8)
+
+    text(20*log10(300),3.3,'(b)',cex=3)
+
+  a <- density(meanMaskRTs[,1],cut=6)
+  a$y <- 0.35*a$y/max(a$y)
+  polygon(a$x,1.1+a$y,border=NA,col=addalpha(collist[1],0.5))
+
+    a <- density(meanMaskRTs[,2])
+  a$y <- 0.35*a$y/max(a$y)
+  polygon(a$x,2.1+a$y,border=NA,col=addalpha(collist[2],0.5))
+
+    a <- density(meanMaskRTs[,3])
+  a$y <- 0.35*a$y/max(a$y)
+  polygon(a$x,3.1+a$y,border=NA,col=addalpha(collist[3],0.5))
+
+  xvals <- seq(-0.1,0.1,length=nrow(meanMaskRTs))
+  points(meanMaskRTs[,1],1+xvals-0.2,pch=16,col=collist[1])
+  points(meanMaskRTs[,2],2+xvals-0.2,pch=15,col=collist[2])
+  points(meanMaskRTs[,3],3+xvals-0.2,pch=18,col=collist[3])
+
+  for (cond in 1:3){
+  bs <- NULL
+  for (n in 1:nbootstraps){bs[n] <- mean(sample(meanMaskRTs[,cond],replace=TRUE))}
+  ci <- quantile(bs,c(0.025,0.975))
+  arrows(mean(meanMaskRTs[,cond]),cond,ci[1],cond,angle=90,length=0.1,lwd=3)
+  arrows(mean(meanMaskRTs[,cond]),cond,ci[2],cond,angle=90,length=0.1,lwd=3)
+  }
+  points(mean(meanMaskRTs[,1]),1,pch=21,cex=2,lwd=2,bg=collist[1])
+  points(mean(meanMaskRTs[,2]),2,pch=22,cex=2,lwd=2,bg=collist[2])
+  points(mean(meanMaskRTs[,3]),3,pch=23,cex=2,lwd=2,bg=collist[3])
+
+par(mfrow=c(2,1),mfg=c(2,1))
+
+plotlims <- c(-200,1000,-12,12)  
+ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
+ticklocsy <- seq(-12,12,4)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.5, cex=1.5)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1.5)  
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.8)   
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1.8)
+
+  text(-200,10,'(c)',cex=3)
+
+lines(c(-200,1000),c(0,0),lty=1)
+lines(c(0,0),c(-20,20),lty=1)
+polygon(c(0,250,250,0),c(-13,-13,-11,-11),col=rgb(0,0,0,0.3),border=NA)
+
+polygon(c(-200:1000,1000:-200), c(limits[1,],limits[2,1201:1]), col=rgb(0,0,0,0.1),border=NA)
+
+lines(-200:1000, grandmeanERP, lwd=3)
+
+  text(105,10,'P100',cex=2)
+  text(155,-4,'N170',cex=2)
+  text(250,4.5,'P200',cex=2)
+
+chanindex <- match(toupper(chanlabels),toupper(chanlocs$Electrode))
+chanxy <- chanlocs[chanindex,2:3]
+lines(150*chanlocs$OutlineX-100,7.5*chanlocs$OutlineY + 6, lwd=2)
+lines(150*chanlocs$NoseX-100,7.5*chanlocs$NoseY + 6, lwd=2)
+lines(150*chanlocs$LearX-100,7.5*chanlocs$LearY + 6, lwd=2)
+lines(150*chanlocs$RearX-100,7.5*chanlocs$RearY + 6, lwd=2)
+points(150*chanlocs$X_position[1:64]-100,7.5*chanlocs$Y_position[1:64] + 6, pch=16,col='lightgrey')
+points(150*chanlocs$X_position[chanindex[targetelectrodes]]-100,7.5*chanlocs$Y_position[chanindex[targetelectrodes]] + 6, pch=16,col='black')
+
+dev.off()
+
+pdf(paste0('Figures/MasksMVPA.pdf'), bg="transparent", height = 12, width = 24)
+
+par(mfrow=c(2,2))
+
+times <- -199:1200
+
+plotlims <- c(-200,1000,-12,12)  
+ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
+ticklocsy <- seq(-12,12,4)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)    
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.5, cex=1.5)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1.5)  
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.8)   
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1.8)
+
+lines(c(-200,1000),c(0,0),lty=1)
+lines(c(0,0),c(-20,20),lty=1)
+polygon(c(0,250,250,0),c(-13,-13,-11,-11),col=rgb(0,0,0,0.3),border=NA)
+
+polygon(c(-200:1000,1000:-200), c(limits[3,],limits[4,1201:1]), col=addalpha(collist[1],0.3),border=NA)
+polygon(c(-200:1000,1000:-200), c(limits[7,],limits[8,1201:1]), col=addalpha(collist[3],0.3),border=NA)
+
+lines(-200:1000, colMeans(meanERP[1,targetelectrodes,]), lwd=3, col=collist[1])     
+lines(-200:1000, colMeans(meanERP[3,targetelectrodes,]), lwd=3, col=collist[3])
+
+chanindex <- match(toupper(chanlabels),toupper(chanlocs$Electrode))
+chanxy <- chanlocs[chanindex,2:3]
+lines(150*chanlocs$OutlineX-100,7.5*chanlocs$OutlineY + 6, lwd=2)
+lines(150*chanlocs$NoseX-100,7.5*chanlocs$NoseY + 6, lwd=2)
+lines(150*chanlocs$LearX-100,7.5*chanlocs$LearY + 6, lwd=2)
+lines(150*chanlocs$RearX-100,7.5*chanlocs$RearY + 6, lwd=2)
+points(150*chanlocs$X_position[1:64]-100,7.5*chanlocs$Y_position[1:64] + 6, pch=16,col='lightgrey')
+points(150*chanlocs$X_position[chanindex[targetelectrodes]]-100,7.5*chanlocs$Y_position[chanindex[targetelectrodes]] + 6, pch=16,col='black')
+
+allbfs <- ERP_BF[2,]
+
+linestartstop <- times[allbfs>=3 & allbfs<10]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], -c(8.5,8.5,7.5,7.5), col=bfcols[1],border=NA)}}
+
+linestartstop <- times[allbfs>=10 & allbfs<30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], -c(8.5,8.5,7.5,7.5), col=bfcols[2],border=NA)}}
+
+linestartstop <- times[allbfs>=30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], -c(8.5,8.5,7.5,7.5), col=bfcols[3],border=NA)}}
+
+legend(700,12,c('Human','Halloween'),lty=1,lwd=3,col=collist[c(3,1)],cex=1.8,box.lwd=2)
+text(-190,11,'(a)',cex=3)
+
+legend(-200,-6,c('BF>3','BF>10','BF>30'),lwd=5,col=bfcols, box.lwd=2, cex=1.5)
+
+plotlims <- c(-200,1000,-12,12)  
+ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
+ticklocsy <- seq(-12,12,4)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.5, cex=1.5)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1.5)  
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.8)   
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1.8)
+
+lines(c(-200,1000),c(0,0),lty=1)
+lines(c(0,0),c(-20,20),lty=1)
+polygon(c(0,250,250,0),c(-13,-13,-11,-11),col=rgb(0,0,0,0.3),border=NA)
+
+polygon(c(-200:1000,1000:-200), c(limits[5,],limits[6,1201:1]), col=addalpha(collist[2],0.3),border=NA)
+polygon(c(-200:1000,1000:-200), c(limits[7,],limits[8,1201:1]), col=addalpha(collist[3],0.3),border=NA)
+
+lines(-200:1000, colMeans(meanERP[2,targetelectrodes,]), lwd=3, col=collist[2])     
+lines(-200:1000, colMeans(meanERP[3,targetelectrodes,]), lwd=3, col=collist[3])
+
+chanindex <- match(toupper(chanlabels),toupper(chanlocs$Electrode))
+chanxy <- chanlocs[chanindex,2:3]
+lines(150*chanlocs$OutlineX-100,7.5*chanlocs$OutlineY + 6, lwd=2)
+lines(150*chanlocs$NoseX-100,7.5*chanlocs$NoseY + 6, lwd=2)
+lines(150*chanlocs$LearX-100,7.5*chanlocs$LearY + 6, lwd=2)
+lines(150*chanlocs$RearX-100,7.5*chanlocs$RearY + 6, lwd=2)
+points(150*chanlocs$X_position[1:64]-100,7.5*chanlocs$Y_position[1:64] + 6, pch=16,col='lightgrey')
+points(150*chanlocs$X_position[chanindex[targetelectrodes]]-100,7.5*chanlocs$Y_position[chanindex[targetelectrodes]] + 6, pch=16,col='black')
+
+allbfs <- ERP_BF[3,]
+
+linestartstop <- times[allbfs>=3 & allbfs<10]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], -c(8.5,8.5,7.5,7.5), col=bfcols[1],border=NA)}}
+
+linestartstop <- times[allbfs>=10 & allbfs<30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], -c(8.5,8.5,7.5,7.5), col=bfcols[2],border=NA)}}
+
+linestartstop <- times[allbfs>=30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], -c(8.5,8.5,7.5,7.5), col=bfcols[3],border=NA)}}
+
+legend(700,12,c('Human','Silicone'),lty=1,lwd=3,col=collist[c(3,2)],cex=1.8,box.lwd=2)
+text(-190,11,'(b)',cex=3)
+
+legend(-200,-6,c('BF>3','BF>10','BF>30'),lwd=5,col=bfcols, box.lwd=2, cex=1.5)
+
+plotlims <- c(-200,1000,0,1) 
+ticklocsx <- seq(-200,1000,200)  
+ticklocsy <- seq(0,1,0.25)    
+ticklabelsx <- ticklocsx      
+ticklabelsy <- ticklocsy*100
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+
+mtext(text = ticklabelsx, side = 1, at=ticklocsx,line=0.5,cex=1.5)  
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1,cex=1.5) 
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.8)  #}    
+title(ylab="Classifier accuracy (%)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1.8)
+text(-190,0.95,'(c)',cex=3)
+
+lines(c(-200, 1000),c(0.5, 0.5), col='black', lty=2)
+lines(c(0,0),c(0,1), col='black')
+
+polygon(c(-200:1000,1000:-200), c(mlimits[3,],mlimits[4,1201:1]), col=addalpha(collist[2],0.3),border=NA)
+
+lines(-200:1000,meanMVPA[2,], col=collist[2], lwd=3, cex=0.5)
+
+allbfs <- mBF[2,]
+
+linestartstop <- times[allbfs>=3 & allbfs<10]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.24,0.24,0.26,0.26), col=bfcols[1],border=NA)}}
+
+linestartstop <- times[allbfs>=10 & allbfs<30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.24,0.24,0.26,0.26), col=bfcols[2],border=NA)}}
+
+linestartstop <- times[allbfs>=30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.24,0.24,0.26,0.26), col=bfcols[3],border=NA)}}
+
+legend(-200,0.25,c('BF>3','BF>10','BF>30'),lwd=5,col=bfcols, box.lwd=2, cex=1.5)
+
+plotlims <- c(-200,1000,0,1) 
+ticklocsx <- seq(-200,1000,200)  
+ticklocsy <- seq(0,1,0.25)    
+ticklabelsx <- ticklocsx      
+ticklabelsy <- ticklocsy*100
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+
+mtext(text = ticklabelsx, side = 1, at=ticklocsx,line=0.5,cex=1.5)  
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1,cex=1.5) 
+title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.8)  #}    
+title(ylab="Classifier accuracy (%)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1.8)
+text(-190,0.95,'(d)',cex=3)
+
+lines(c(-200, 1000),c(0.5, 0.5), col='black', lty=2)
+lines(c(0,0),c(0,1), col='black')
+
+polygon(c(-200:1000,1000:-200), c(mlimits[5,],mlimits[6,1201:1]), col=addalpha(collist[3],0.3),border=NA)
+
+lines(-200:1000,meanMVPA[3,], col=collist[3], lwd=3, cex=0.5)
+
+allbfs <- mBF[3,]
+
+linestartstop <- times[allbfs>=3 & allbfs<10]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.24,0.24,0.26,0.26), col=bfcols[1],border=NA)}}
+
+linestartstop <- times[allbfs>=10 & allbfs<30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.24,0.24,0.26,0.26), col=bfcols[2],border=NA)}}
+
+linestartstop <- times[allbfs>=30]
+if (length(linestartstop)>1){xpairs <- getstartstop(linestartstop)
+for (n in 1:((length(xpairs)/2)-1)){polygon(xpairs[n,c(1,2,2,1)], c(0.24,0.24,0.26,0.26), col=bfcols[3],border=NA)}}
+
+legend(-200,0.25,c('BF>3','BF>10','BF>30'),lwd=5,col=bfcols, box.lwd=2, cex=1.5)
+
+dev.off()
 
@@
 
+conddprimes <- colMeans(allMaskdprime)
+condRTs <- 10^(colMeans(meanMaskRTs)/20)
+
 ```
 
-```{r pupildata, fig.cap="Caption.", fig.align="center", echo=FALSE}
+The results of Experiment 2 were similar to those of Experiment 1, despite using a quite different stimulus set involving images of humans wearing masks, rather than robots.
+Sensitivity was highest for identifying Halloween masks (d' = `r round(conddprimes[1],digits=2)`), but still well above chance for both the human (d' = `r round(conddprimes[3],digits=2)`) and silicone mask (d' = `r round(conddprimes[2],digits=2)`) conditions.
+The Bayes factor score for a one-way ANOVA comparing these three conditions indicated very substantial evidence ($log_{10}BF_{10} =$ `r round(log10(bfdprime),digits=2)`) for a difference between conditions, as illustrated in Figure \ref{fig:MasksData}a.
+Pairwise Bayesian t-tests between conditions indicate very convincing differences in sensitivity between Halloween and silicone masks ($log_{10}BF_{10} =$ `r round(log10(bfcontrasts[1]),digits=2)`) between Halloween masks and humans ($log_{10}BF_{10} =$ `r round(log10(bfcontrasts[2]),digits=2)`), and between silicone masks and humans ($log_{10}BF_{10} =$ `r round(log10(bfcontrasts[3]),digits=2)`).
+Unlike in Experiment 1, there were no convincing reaction time differences between conditions ($log_{10}BF_{10} =$ `r round(log10(bfRT),digits=2)`), as illustrated in Figure \ref{fig:MasksData}b.
 
-# knitr::include_graphics(paste0('Figures/pupildata.pdf'))
+```{r MasksData, fig.cap="Summary of response data and grand mean ERP for Experiment 2.
+Panel (a) shows d-prime scores for identifying images of human faces (blue), silicone masks (green) and Halloween masks (red).
+Small points show individual participants, and the larger symbols with error bars indicate the group mean and bootstrapped 95 percent confidence intervals.
+Panel (b) plots reaction times in the same format (note the logarithmic x-axis).
+Panel (c) shows the grant mean ERP across all participants and conditions, pooled across electrodes P6, P8, PO6 and PO8 (see inset).
+The shaded region around the curve illustrates the 95 percent confidence interval, and the grey rectangle at the foot indicates the stimulus duration.", fig.align="center", echo=FALSE, fig.width=12, fig.height=12}
+
+knitr::include_graphics('Figures/MaskSData.pdf')
 
 ```
+
+The grand average ERP waveform for Experiment 2 (see Figure \ref{fig:MasksData}c) had similar initial components as for Experiment 1.
+The latter portion of the waveforms differed somewhat, most likely owing to the difference in presentation duration across experiments (250ms versus 500ms).
+There was a substantial univariate difference in ERP response between human and Halloween mask conditions extending from around 170 to 230ms following stimulus onset (see Figure \ref{fig:MasksMVPA}a), with Bayes factors exceeding 30.
+Univariate differences between the human and silicone mask conditions were not compelling (see Figure \ref{fig:MasksMVPA}b).
+
+```{r MasksMVPA, fig.cap="Univariate and multivariate comparisons across image type for Experiment 2.
+Panel (a) shows the ERPs comparing human faces (blue) and Halloween masks (red), and panel (b) compares human faces (blue) and silicone masks (green).
+Panels (c) and (d) show multivariate pattern classification accuracy for the same comparisons.
+Points at y = -8 and y = 25 indicate Bayes factor scores for comparisons between ERPs (a,b) and comparing classification accuracy to chance (50 percent correct; c,d).", fig.align="center", echo=FALSE, fig.width=12, fig.height=12}
+
+knitr::include_graphics('Figures/MaskSMVPA.pdf')
+
+```
+
+Multivariate pattern analysis revealed extremely high classification accuracy (up to `r round(100*max(meanMVPA[2,]),digits=0)`\% correct) comparing human faces with Halloween masks.
+This was convincingly above chance, with a Bayes factor score exceeding 30 from around 100ms following stimulus onset, and extending across the full time window (see Figure \ref{fig:MasksMVPA}c).
+Classification was also convincingly above chance when comparing human faces with silicone masks (Figure \ref{fig:MasksMVPA}d).
+This timecourse had an initial peak of high accuracy (up to `r round(100*max(meanMVPA[3,]),digits=0)`\% correct) between 100 and 200ms after stimulus onset, followed by a second peak around 600ms.
+This replicates the finding from Experiment 1 that uncanny valley responses might involve two distinct components at different moments in time.
+
 # Discussion
@@
 
+SF was funded by a YorRobots Venables internship. Also supported by BBSRC grant BB/V007580/1 awarded to DHB. ANY OTHER GRANTS TO ACKNOWLEDGE HERE?
+
 # References

### 2023-02-17 eeglabpreprocess.m

@@ -1,0 +1,377 @@
+% script preprocessing in EEGlab and brainstorm
+
+clear
+close all;
+
+eeglabdir = '/Users/db900/Documents/MATLAB/eeglab2022.1';
+brainstormdir = '/Users/db900/Documents/MATLAB/brainstorm3';
+
+rawdatadir = '/Users/db900/Documents/git/uncannyvalley/local/RawData/Experiment 1';
+eeglabdata = '/Users/db900/Documents/git/uncannyvalley/local/preprocessed';
+dbpath = '/Users/db900/Documents/git/uncannyvalley/local/brainstormdb';
+procpath = '/Users/db900/Documents/git/uncannyvalley/local/robotsmvpa';
+protocolpath = '/Users/db900/Documents/git/uncannyvalley/local/brainstormdb/Experiment1/data/';
+
+if ~exist(dbpath,'dir')
+    mkdir(dbpath);
+end
+if ~exist(procpath,'dir')
+    mkdir(procpath);
+end
+
+rmpath(brainstormdir);
+% addpath(eeglabdir);
+% 
+% [ALLEEG EEG CURRENTSET ALLCOM] = eeglab('nogui');
+% % plugin_askinstall('ANTeepimport');
+% 
+% robotstoclean = [302 304 305 309 313];
+% for s = 301:329
+%     s
+% 
+%     if ~exist(strcat(eeglabdata,'/',num2str(s),'.set'),'file')
+%         tic
+% 
+%         EEGpath = strcat(rawdatadir,'/',num2str(s));
+%         d = dir(strcat(EEGpath,'/*.cnt'))       % index the directory containing the EEG files
+%         counter = length(d);
+% 
+%         c = 1;
+%         fname = d(c).name;
+%         EEG = pop_loadeep_v4(strcat(EEGpath,'/',fname));    % load the EEG data
+% 
+%         if counter>1
+%             for c = 2:counter                       % loop through all cnt files
+%                 fname = d(c).name;
+%                 EEG2 = pop_loadeep_v4(strcat(EEGpath,'/',fname));    % load the EEG data
+%                 EEG = pop_mergeset(EEG, EEG2);
+%             end
+%         end
+% 
+%         EEG = eeg_checkset( EEG );
+%         EEG=pop_chanedit(EEG, 'lookup',strcat(eeglabdir,'/plugins/dipfit/standard_BEM/elec/standard_1005.elc'));
+% 
[…]

### 2023-02-17 masks1.m

@@ -1,117 +1,0 @@
-% Script generated by Brainstorm (12-Dec-2022)
-rawpath = '/Volumes/USB128/UncannyValley/MasksRaw/';
-procpath = '/Volumes/USB128/UncannyValley/MasksProcessed/';
-dbpath = '/Volumes/USB128/brainstormdb/Masks/data/';
-
-for s = 351:380
-    s
-    tic
-% Input files
-sFiles = [];
-SubjectNames = {num2str(s)};
-RawFiles = {strcat(rawpath,num2str(s),'.set')};
-
-% Process: Create link to raw file
-sFiles = bst_process('CallProcess', 'process_import_data_raw', sFiles, [], ...
-    'subjectname',    SubjectNames{1}, ...
-    'datafile',       {RawFiles{1}, 'EEG-EEGLAB'}, ...
-    'channelreplace', 1, ...
-    'channelalign',   1, ...
-    'evtmode',        'value');
-
-% Process: Band-pass:0.5Hz-48Hz
-sFiles = bst_process('CallProcess', 'process_bandpass', sFiles, [], ...
-    'sensortypes', 'MEG, EEG', ...
-    'highpass',    0.5, ...
-    'lowpass',     30, ...
-    'tranband',    0, ...
-    'attenuation', 'relax', ...  % 40dB
-    'ver',         '2019', ...  % 2019
-    'mirror',      0, ...
-    'read_all',    0);
-
-% merge across asian and western image sets by renaming event triggers
-sFiles = bst_process('CallProcess', 'process_evt_rename', sFiles, [], ...
-    'src',   '111, 211, 112, 212, 123, 223', ...
-    'dest',  '101, 101, 102, 102, 103, 103');
-
-% Process: Import MEG/EEG: Events
-sFiles = bst_process('CallProcess', 'process_import_data_event', sFiles, [], ...
-    'subjectname',   SubjectNames{1}, ...
-    'condition',     '', ...
-    'eventname',     '101, 102, 103', ...
-    'timewindow',    [], ...
-    'epochtime',     [-0.2, 1], ...
-    'split',         0, ...
-    'createcond',    1, ...
-    'ignoreshort',   1, ...
-    'usectfcomp',    1, ...
-    'usessp',        1, ...
-    'freq',          [], ...
[…]

### 2023-02-17 robots1.m

@@ -1,112 +1,0 @@
-% Script generated by Brainstorm (12-Dec-2022)
-rawpath = '/Volumes/USB128/UncannyValley/RobotsClean/';
-procpath = '/Volumes/USB128/UncannyValley/RobotsProcessed/';
-dbpath = '/Volumes/USB128/brainstormdb/Robots/data/';
-
-slist = [302 304 305 309 313];
-for sno = 1:length(slist)
-    s = slist(sno)
-    tic
-% Input files
-sFiles = [];
-SubjectNames = {num2str(s)};
-RawFiles = {strcat(rawpath,num2str(s),'.set')};
-
-% Process: Create link to raw file
-sFiles = bst_process('CallProcess', 'process_import_data_raw', sFiles, [], ...
-    'subjectname',    SubjectNames{1}, ...
-    'datafile',       {RawFiles{1}, 'EEG-EEGLAB'}, ...
-    'channelreplace', 1, ...
-    'channelalign',   1, ...
-    'evtmode',        'value');
-
-% Process: Band-pass:0.5Hz-48Hz
-sFiles = bst_process('CallProcess', 'process_bandpass', sFiles, [], ...
-    'sensortypes', 'MEG, EEG', ...
-    'highpass',    0.5, ...
-    'lowpass',     30, ...
-    'tranband',    0, ...
-    'attenuation', 'relax', ...  % 40dB
-    'ver',         '2019', ...  % 2019
-    'mirror',      0, ...
-    'read_all',    0);
-
-% Process: Import MEG/EEG: Events
-sFiles = bst_process('CallProcess', 'process_import_data_event', sFiles, [], ...
-    'subjectname',   SubjectNames{1}, ...
-    'condition',     '', ...
-    'eventname',     '101, 102, 103', ...
-    'timewindow',    [], ...
-    'epochtime',     [-0.2, 1], ...
-    'split',         0, ...
-    'createcond',    1, ...
-    'ignoreshort',   1, ...
-    'usectfcomp',    1, ...
-    'usessp',        1, ...
-    'freq',          [], ...
-    'baseline',      [-0.2, -0.001], ...
-    'blsensortypes', 'MEG, EEG');
-
-d = dir(strcat(dbpath,num2str(s),'/101/data_101_trial*'));
-sFiles1 = {};
-for n = 1:length(d)
[…]

### 2024-04-21 manuscript.Rmd
Added autobuild files

@@
   | for robots and hyper-realistic masks 
-  | (for submission to Computers in Human Behavior)
 author: |
@@
 output:
-  pdf_document:
-    toc: no
   bookdown::pdf_document2:
@@
   word_document: default
+  pdf_document:
+    toc: no
   html_document: default
@@
 
-processdata <- 0  # this flag determines the amount of processing, with 4 levels:
+processdata <- 0  # this flag determines the amount of processing, with 3 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
 # 2 - do statistics and bootstrapping using processed data
-# 3 - download all raw data and do preprocessing (requires ~60GB of storage)
 
@@
 
-rawdir <- 'local/raw/'
-rawdir <- '/Volumes/USB128/UncannyValley/'
-processeddir <- 'local/output/'
-# processeddir <- '/Volumes/USB128/UncannyValley/'
-
 if (!dir.exists('local/')){dir.create('local/')}
-# if (!dir.exists('local/robotsmvpa/')){dir.create('local/robotsmvpa/')}
-# if (!dir.exists('local/masksmvpa/')){dir.create('local/masksmvpa/')}
+if (!dir.exists('local/robotsmvpa/')){dir.create('local/robotsmvpa/')}
+if (!dir.exists('local/masksmvpa/')){dir.create('local/masksmvpa/')}
 
@@
 
+  if (!file.exists('local/channel.mat')){
+  osfproject <- osf_retrieve_node('uzbns')
+  osffiles <- osf_ls_files(osfproject)
+  fid <- which(osffiles$name=='channel.mat')
+  osf_download(osffiles[fid,], path='local/',progress=TRUE)}
+
+  if (!file.exists('local/channeldata.csv')){
+  osfproject <- osf_retrieve_node('uzbns')
+  osffiles <- osf_ls_files(osfproject)
+  fid <- which(osffiles$name=='channeldata.csv')
+  osf_download(osffiles[fid,], path='local/',progress=TRUE)}
+
 ```
@@
 Images were taken from a variety of sources that permit reuse in academic contexts and in most cases were not part of the stimulus set from the experiments.
-The silicone mask image was taken by the authors, and was used in Experiment 2.", fig.align="center", echo=FALSE, fig.width=8, fig.height=8}
+The silicone mask image was taken by the authors, and was used in Experiment 2.", fig.align="center", out.width='80%', echo=FALSE}
 
@@
 
-We analysed response data by calculating d-prime scores for each condition, derived from the hit rate and false alarm rate [@Macmillan2005].
+We analysed response data by calculating d-prime ($d'$) scores for each condition, derived from the hit rate and false alarm rate [@Macmillan2005].
 For the human conditions, the hit rate was the proportion of human images correctly identified as human, and the false alarm rate was the proportion of robot or mask images that were incorrectly judged as being human.
@@
 
-if (file.exists('local/GroupDataRobots.RData')){load('local/GroupDataRobots.RData')}  
+  if (!file.exists('local/GroupDataRobots.RData')){
+  osfproject <- osf_retrieve_node('uzbns')
+  osffiles <- osf_ls_files(osfproject)
+  fid <- which(osffiles$name=='GroupDataRobots.RData')
+  osf_download(osffiles[fid,], path='local/',progress=TRUE)}
+
+load('local/GroupDataRobots.RData')
 if (processdata > 0){
@@
 We calculated d-prime scores to compare sensitivity across conditions.
-Sensitivity was highest for identifying robots (d' = `r round(conddprimes[1],digits=2)`), but still well above chance for both the human (d' = `r round(conddprimes[3],digits=2)`) and android (d' = `r round(conddprimes[2],digits=2)`) conditions.
+Sensitivity was highest for identifying robots ($d' =$ `r round(conddprimes[1],digits=2)`), but still well above chance for both the human ($d' =$ `r round(conddprimes[3],digits=2)`) and android ($d' =$ `r round(conddprimes[2],digits=2)`) conditions.
 The Bayes factor score for a one-way ANOVA comparing these three conditions indicated very substantial evidence ($log_{10}BF_{10} =$ `r round(log10(bfdprime),digits=2)`) for a difference between conditions, as illustrated in Figure \ref{fig:RobotsData}a.
@@
 Panel (b) plots reaction times in the same format (note the logarithmic x-axis).
-Panel (c) shows the grant mean ERP across all participants and conditions, pooled across electrodes P6, P8, PO6 and PO8 (see inset).
-The shaded region around the curve illustrates the 95 percent confidence interval, and the grey rectangle at the foot indicates the stimulus duration.", fig.align="center", echo=FALSE, fig.width=12, fig.height=12}
+Panel (c) shows the grand mean ERP across all participants and conditions, pooled across electrodes P6, P8, PO6 and PO8 (see inset).
+The shaded region around the curve illustrates the 95 percent confidence interval, and the grey rectangle at the foot indicates the stimulus duration.", fig.align="center", echo=FALSE}
 
@@
 Panels (c) and (d) show multivariate pattern classification accuracy for the same comparisons.
-Points at y = -8 and y = 25 indicate Bayes factor scores for comparisons between ERPs (a,b) and comparing classification accuracy to chance (50 percent correct; c,d).", fig.align="center", echo=FALSE, fig.width=12, fig.height=12}
+Points at y = -8 and y = 25 indicate Bayes factor scores for comparisons between ERPs (a,b) and comparing classification accuracy to chance (50 percent correct; c,d).", fig.align="center", echo=FALSE}
 
@@
 
-if (file.exists('local/GroupDataMasks.RData')){load('local/GroupDataMasks.RData')}  
+  if (!file.exists('local/GroupDataMasks.RData')){
+  osfproject <- osf_retrieve_node('uzbns')
+  osffiles <- osf_ls_files(osfproject)
+  fid <- which(osffiles$name=='GroupDataMasks.RData')
+  osf_download(osffiles[fid,], path='local/',progress=TRUE)}
+
+load('local/GroupDataMasks.RData')
+
 if (processdata > 0){
@@
 The results of Experiment 2 were similar to those of Experiment 1, despite using a quite different stimulus set involving images of humans wearing masks, rather than robots.
-Sensitivity was highest for identifying Halloween masks (d' = `r round(conddprimes[1],digits=2)`), but still well above chance for both the human (d' = `r round(conddprimes[3],digits=2)`) and silicone mask (d' = `r round(conddprimes[2],digits=2)`) conditions.
+Sensitivity was highest for identifying Halloween masks ($d' =$ `r round(conddprimes[1],digits=2)`), but still well above chance for both the human ($d' =$ `r round(conddprimes[3],digits=2)`) and silicone mask ($d' =$ `r round(conddprimes[2],digits=2)`) conditions.
 The Bayes factor score for a one-way ANOVA comparing these three conditions indicated very substantial evidence ($log_{10}BF_{10} =$ `r round(log10(bfdprime),digits=2)`) for a difference between conditions, as illustrated in Figure \ref{fig:MasksData}a.

### 2024-04-21 manuscript.tex
Added autobuild files

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 \author{Shona Fitzpatrick, Ailish K. Byrne, Alex Headley, Jet G. Sanders,\\
-Helen Petrie, Rob Jenkins \& Daniel H. Baker}
-\date{2023-01-02}
+Helen Petrie, Rob Jenkins \& Daniel H. Baker (\href{mailto:daniel.baker@york.ac.uk}{\nolinkurl{daniel.baker@york.ac.uk}})}
+\date{University of York}
 
@@
 
-Many people report an aversion to entities that are human-like, but on closer inspection are actually artificial.
-Examples include humanoid robots (androids), puppets, realistic computer-generated images, and hyper-realistic masks.
+Many people report an aversion to entities that are superficially human-like, but on closer inspection are actually artificial.
+Examples include humanoid robots (androids), puppets, hyper-realistic masks, and computer-generated images or movies.
 The term `uncanny valley' (Mori, 1970; English translation in Mori et al., 2012) describes the idea that entities that are clearly human or clearly artificial do not evoke unease, whereas artificial entities that are human-like are disconcerting.
@@
 We achieve this through two EEG experiments, in which we measure neural responses to static images.
-In the first experiment, the stimuli were humans, machine-like robots, and human-like robots.
-In the second experiment we aimed to generalise the finding by using images of people wearing no masks, wearing obvious masks (e.g.~carnival or halloween masks), and wearing hyper-realistic silicone masks (Sanders et al., 2017).
-Rather than focus on specific ERP components, we use a non-parametric cluster correction procedure to compare conditions.
-We also apply a pattern classification approach to identify time windows in which information in the EEG signal can be used to distinguish between pairs of conditions.
+In the first experiment, the stimuli were humans, machine-like robots, and human-like robots (see Figure \ref{fig:stimexamples}a).
+In the second experiment we aimed to generalise the finding by using images of people wearing no masks, wearing obvious masks (e.g.~carnival or Halloween masks), and wearing hyper-realistic silicone masks (Sanders et al., 2017) (see Figure \ref{fig:stimexamples}b).
+Rather than focus on specific ERP components, we use a multivariate pattern classification approach to identify time windows in which information in the EEG signal can be used to distinguish between pairs of conditions.
+Our rationale is that timepoints where signals evoked by human faces can be distinguished from those evoked by human-like robots, or hyper-realistic masks, are candidates for a neural signature of the uncanny valley effect.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Figures/stimfigure}
+
+}
+
+\caption{Illustrative stimuli from the same categories as used in Experiments 1 and 2.
+Row (a) shows a human face, an android and a robot, all against white backgrounds.
+Row (b) shows a human face, a hyper-realistic silicone mask, and a carnival mask, all against natural backgrounds.
+Images were taken from a variety of sources that permit reuse in academic contexts and in most cases were not part of the stimulus set from the experiments.
+The silicone mask image was taken by the authors, and was used in Experiment 2.}\label{fig:stimexamples}
+\end{figure}
 
@@
 Images all showed the head and shoulders of the subject, had white backgrounds, and were sourced from the internet.
-In Experiment 2, the stimulus set consisted of a total of 296 images, comprising real faces (148 images), people wearing silicone masks (74 images), and people wearing Halloween masks (74 images).
+In Experiment 2, the stimulus set consisted of a total of 296 images, comprising real faces (148 images), people wearing silicone masks (74 images), and people wearing obvious masks of the sort typically worn for carnivals and Halloween celebrations (74 images).
 The backgrounds of these images were more heterogeneous, and showed the natural surroundings of the subject.
@@
 In the third block, stimuli doubled in size again, and subtended \(22\times30\) degrees.
+The rationale for the size manipulation was to investigate whether increasing levels of detail made the silicone masks more identifiable (Sanders et al., 2017), however as that is not the main focus of the current paper we collapse results across size conditions.
 Stimuli were presented for 250ms, and participants indicated whether they thought each image contained a real face or a mask, using a two-button trackball.
@@
 
+We analysed response data by calculating d-prime (\(d'\)) scores for each condition, derived from the hit rate and false alarm rate (Macmillan and Creelman, 2005).
+For the human conditions, the hit rate was the proportion of human images correctly identified as human, and the false alarm rate was the proportion of robot or mask images that were incorrectly judged as being human.
+For the robot and mask conditions, the hit rate was the proportion of robot/mask images correctly identified as not being human, and the false alarm rate was the proportion of human images that were incorrectly judged as being non-human (note that this means the false alarm rate was the same for the robot and android conditions, and for the silicone and Halloween mask conditions).
+We capped infinite d-prime values (which occur e.g.~when the hit rate is 1) at an arbitrary ceiling of 5.
+We log transformed the reaction times (which typically have positive skew) and performed all averaging and statistical analysis on the logarithmic values.
+
 EEG signals were recorded during each block, and saved to disc for subsequent offline analysis.
-We used a component of the EEGlab toolbox (Delorme and Makeig, 2004) to convert the continuous data from a proprietary file format to a compressed csv text file.
-All subsequent analyses were conducted in R using these files.
-
-For each block, data at each electrode were low-pass filtered at 30Hz with a \(10^{th}\) order Butterworth filter, and then epoched using the stimulus onset triggers.
-A pre-stimulus baseline (average voltage of the 200ms before stimulus onset) was subtracted from each waveform.
-We rejected ERPs that showed evidence of excessive noise or movement artefacts on a per-electrode basis by excluding trials where the standard deviation across the time window from 200ms before to 1000ms after stimulus onset exceeded \(40\mu V\).
-ERPs were averaged across trials for each participant, and then across participants to calculate group averages.
+We used components of the EEGlab toolbox (Delorme and Makeig, 2004) to import the data into Matlab and collate data across blocks.
+We then used Brainstorm (Tadel et al., 2011) to filter the data using a bandpass filter (0.5 to 30Hz), epoch by condition, and subtract a pre-trial baseline (the mean voltage for the 200ms before stimulus onset).
+Five participants were excluded from the EEG analysis of each experiment due to excessive noise.
+Our attempts to clean up the data from these participants using independent components analysis was unsuccessful.
+Their behavioural data were still included in the analysis.
+In Experiment 2 we combined data across all three image sizes, as this was not the main focus of our analysis.
 
@@
 The resulting Bayes factor score is a summary of the evidence in favour of either the null hypothesis (that the waveforms are equal) or the alternative hypothesis (that they differ).
-We use the heuristics proposed by Jeffreys (1961) that Bayes factors \textgreater3 constitute some evidence supporting the alternative hypothesis, factors \textgreater10 constitute strong evidence, and factors \textgreater30 constitute very strong evidence.
+We use the heuristics proposed by Jeffreys (1961) that Bayes factors \textgreater3 (\(log_{10}BF_{10}\) \textgreater{} 0.5) constitute some evidence supporting the alternative hypothesis, factors \textgreater10 (\(log_{10}BF_{10}\) \textgreater{} 1) constitute strong evidence, and factors \textgreater30 (\(log_{10}BF_{10}\) \textgreater{} 1.5) constitute very strong evidence.
 
-Multivariate pattern analysis was conducted by training a linear support vector machine algorithm to discriminate between patterns of activity across electrodes at a specific time point.
-The patterns came from the real face condition and one of the mask conditions at a single stimulus size, and for a single participant.
-Examples of each pattern were calculated by averaging over random subsets of 36 trials from a given condition, and using these to train the classifier.
+Multivariate pattern analysis was conducted by training a linear support vector machine algorithm (LibSVM; Chang and Lin (2011)) to discriminate between patterns of activity across electrodes at a specific time point.
+The patterns came from the human face condition and one of the other conditions, for a single participant.
+Four examples of each pattern were calculated by averaging over random subsets of 20\% of the available trials from a given condition, and using these to train the classifier.
 The accuracy of the classifier was tested on the averaged remaining trials (that were not used in training) for each condition.
@@
 The analysis was carried out at all time points, and also for all participants.
-We then averaged classifier accuracy across participants, and calculated one sample Bayesian t-tests at each time point as described above.
+We then averaged classifier accuracy across participants, and calculated one sample Bayesian t-tests comparing to chance performance at each time point as described above.
 
@@
 
+We first explored the behavioural results for identification of human versus non-human stimuli.
+We calculated d-prime scores to compare sensitivity across conditions.
+Sensitivity was highest for identifying robots (\(d' =\) 4), but still well above chance for both the human (\(d' =\) 2.72) and android (\(d' =\) 2.27) conditions.
+The Bayes factor score for a one-way ANOVA comparing these three conditions indicated very substantial evidence (\(log_{10}BF_{10} =\) 6.67) for a difference between conditions, as illustrated in Figure \ref{fig:RobotsData}a.
+Pairwise Bayesian t-tests between conditions indicate very convincing differences in sensitivity between robots and androids (\(log_{10}BF_{10} =\) 7.15) and robots and humans (\(log_{10}BF_{10} =\) 6.27).
+The difference between androids and humans (\(log_{10}BF_{10} =\) 5.58) was also very substantial.
+
+Reaction times also differed between conditions, though the effects were rather smaller.
+Reactions were fastest for identifying robots (RT = 688ms), compared with humans (RT = 803ms) and androids (RT = 809ms).
+The Bayes factor score for a one-way ANOVA comparing these three conditions indicated strong evidence (\(log_{10}BF_{10} =\) 1.44) for a difference between conditions, as illustrated in Figure \ref{fig:RobotsData}b.
+Pairwise Bayesian t-tests between conditions indicate very convincing differences in sensitivity between robots and androids (\(log_{10}BF_{10} =\) 5.01) and robots and humans (\(log_{10}BF_{10} =\) 4.61), whereas the reaction time was equivalent between androids and humans (\(log_{10}BF_{10} =\) -0.68).
+
 \begin{figure}
@@
 
-\caption{I.}\label{fig:RobotsData}
+\caption{Summary of response data and grand mean ERP for Experiment 1.
+Panel (a) shows d-prime scores for identifying images of human (blue), android (green) and robot (red) faces.
+Small points show individual participants, and the larger symbols with error bars indicate the group mean and bootstrapped 95 percent confidence intervals.
+Panel (b) plots reaction times in the same format (note the logarithmic x-axis).
+Panel (c) shows the grand mean ERP across all participants and conditions, pooled across electrodes P6, P8, PO6 and PO8 (see inset).
+The shaded region around the curve illustrates the 95 percent confidence interval, and the grey rectangle at the foot indicates the stimulus duration.}\label{fig:RobotsData}
 \end{figure}
+
+EEG activity showed a clear visually evoked potential over posterior electrode sites (see Figure \ref{fig:RobotsData}c), with typical components found in response to visual stimuli (the P100, N170 and P200 are indicated in the figure).
+Pairwise comparisons of conditions are shown in Figure \ref{fig:RobotsMVPA}a,b.
+In general there is a tendency for the ERP response to human faces to diverge slightly from the other two conditions, however the evidence for a convincing difference was not compelling.
+Bayes factors exceeded 3 for only a small number of time points around 300-400ms in the comparison between human and robot images (see yellow bars at y = -8 in Figure \ref{fig:RobotsMVPA}a), but these differences were small considering the variance in the data.
 
@@
 
-\caption{I.}\label{fig:RobotsMVPA}
+\caption{Univariate and multivariate comparisons across image type.
+Panel (a) shows the ERPs comparing human (blue) and robot (red) face images, and panel (b) compares human (blue) and android (green) faces.
+Panels (c) and (d) show multivariate pattern classification accuracy for the same comparisons.
+Points at y = -8 and y = 25 indicate Bayes factor scores for comparisons between ERPs (a,b) and comparing classification accuracy to chance (50 percent correct; c,d).}\label{fig:RobotsMVPA}
 \end{figure}
+
+We also conducted multivariate pattern analysis independently at each time-point for the same two comparisons.
+The evoked responses for human and robot images caused sufficiently distinct patterns of voltages across the scalp that the pattern classifier could distinguish them from around 100 ms following stimulus onset, with accuracy up to 72\% correct (see Figure \ref{fig:RobotsMVPA}c).
+Bayes factors exceeded 30 for much of the time window between 100 and 800 ms, indicating that the decoding was meaningfully above chance performance (50\% correct).
+It was also possible to classify between human and android images (see Figure \ref{fig:RobotsMVPA}d), however performance was much poorer, with a maximum of 62\% correct.
+Classification accuracy had an initial peak around 100ms that provided compelling evidence for above chance classification (BF\textgreater30), and a later region of above-chance classification between 500 and 700ms.
+In the Discussion we speculate that these two time periods might correspond to distinct types of signal associated with the uncanny valley.
+However we first sought to generalise our results to a different stimulus set, and next report the results of Experiment 2 which used hyper-realistic silicone masks.
 
@@
 
+The results of Experiment 2 were similar to those of Experiment 1, despite using a quite different stimulus set involving images of humans wearing masks, rather than robots.
+Sensitivity was highest for identifying Halloween masks (\(d' =\) 4.01), but still well above chance for both the human (\(d' =\) 2.52) and silicone mask (\(d' =\) 1.29) conditions.
+The Bayes factor score for a one-way ANOVA comparing these three conditions indicated very substantial evidence (\(log_{10}BF_{10} =\) 13.34) for a difference between conditions, as illustrated in Figure \ref{fig:MasksData}a.
+Pairwise Bayesian t-tests between conditions indicate very convincing differences in sensitivity between Halloween and silicone masks (\(log_{10}BF_{10} =\) 9.71) between Halloween masks and humans (\(log_{10}BF_{10} =\) 11.59), and between silicone masks and humans (\(log_{10}BF_{10} =\) 5.19).
+Unlike in Experiment 1, there were no convincing reaction time differences between conditions (\(log_{10}BF_{10} =\) -0.8), as illustrated in Figure \ref{fig:MasksData}b.
+
 \begin{figure}
 
-{\centering \includegraphics{Figures/MaskData}
+{\centering \includegraphics{Figures/MaskSData}
 
@@
 
-\caption{I.}\label{fig:MasksData}
+\caption{Summary of response data and grand mean ERP for Experiment 2.
+Panel (a) shows d-prime scores for identifying images of human faces (blue), silicone masks (green) and Halloween masks (red).
+Small points show individual participants, and the larger symbols with error bars indicate the group mean and bootstrapped 95 percent confidence intervals.
+Panel (b) plots reaction times in the same format (note the logarithmic x-axis).
+Panel (c) shows the grand mean ERP across all participants and conditions, pooled across electrodes P6, P8, PO6 and PO8 (see inset).
+The shaded region around the curve illustrates the 95 percent confidence interval, and the grey rectangle at the foot indicates the stimulus duration.}\label{fig:MasksData}
 \end{figure}
+
+The grand average ERP waveform for Experiment 2 (see Figure \ref{fig:MasksData}c) had similar initial components as for Experiment 1.
+The latter portion of the waveforms differed somewhat, most likely owing to the difference in presentation duration across experiments (250ms versus 500ms).
+There was a substantial univariate difference in ERP response between human and Halloween mask conditions extending from around 170 to 230ms following stimulus onset (see Figure \ref{fig:MasksMVPA}a), with Bayes factors exceeding 30.
+Univariate differences between the human and silicone mask conditions were not compelling (see Figure \ref{fig:MasksMVPA}b).
 
@@
 
-{\centering \includegraphics{Figures/MaskMVPA}
+{\centering \includegraphics{Figures/MaskSMVPA}
 
@@
 
-\caption{I.}\label{fig:MasksMVPA}
+\caption{Univariate and multivariate comparisons across image type for Experiment 2.
+Panel (a) shows the ERPs comparing human faces (blue) and Halloween masks (red), and panel (b) compares human faces (blue) and silicone masks (green).
+Panels (c) and (d) show multivariate pattern classification accuracy for the same comparisons.
+Points at y = -8 and y = 25 indicate Bayes factor scores for comparisons between ERPs (a,b) and comparing classification accuracy to chance (50 percent correct; c,d).}\label{fig:MasksMVPA}
 \end{figure}
+
+Multivariate pattern analysis revealed extremely high classification accuracy (up to 97\% correct) comparing human faces with Halloween masks.
+This was convincingly above chance, with a Bayes factor score exceeding 30 from around 100ms following stimulus onset, and extending across the full time window (see Figure \ref{fig:MasksMVPA}c).
+Classification was also convincingly above chance when comparing human faces with silicone masks (Figure \ref{fig:MasksMVPA}d).
+This timecourse had an initial peak of high accuracy (up to 76\% correct) between 100 and 200ms after stimulus onset, followed by a second peak around 600ms.
+This replicates the finding from Experiment 1 that uncanny valley responses might involve two distinct components at different moments in time.
 
@@
 
+SF was funded by a YorRobots Venables internship. Also supported by BBSRC grant BB/V007580/1 awarded to DHB. ANY OTHER GRANTS TO ACKNOWLEDGE HERE?
+
 \hypertarget{references}{%
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-Chang2011}{}}%
+Chang C-C, Lin C-J. 2011. {LIBSVM} : A library for support vector machines. \emph{ACM Transactions on Intelligent Systems and Technology} \textbf{2(27)}:1--27.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Delorme2004}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Macmillan2005}{}}%
+Macmillan NA, Creelman CD. 2005. Detection theory: A user's guide. Psychology Press.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Mori1970}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Tadel2011}{}}%
+Tadel F, Baillet S, Mosher JC, Pantazis D, Leahy RM.
+2011.
+Brainstorm: A user-friendly application for MEG/EEG analysis.
+\emph{Comput Intell Neurosci} \textbf{2011}:879716.
+doi:\href{https://doi.org/10.1155/2011/879716}{10.1155/2011/879716}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Thierry2007}{}}%

### 2024-04-21 manuscript.Rmd
Fixed typo in figure names
Test figure generation

@@
 
-processdata <- 0  # this flag determines the amount of processing, with 3 levels:
+processdata <- 1  # this flag determines the amount of processing, with 3 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
 The term 'uncanny valley' [@Mori1970; English translation in @Mori2012] describes the idea that entities that are clearly human or clearly artificial do not evoke unease, whereas artificial entities that are human-like are disconcerting.
-Understanding these experiences is increasingly important as artificial entities become more integrated into our everyday lives, however at present relatively little is known about the neural underpinnings of the uncanny valley effect.
+Understanding these experiences is increasingly important as artificial entities become more integrated into our everyday lives, however at present relatively little is known about the neural underpinnings of the uncanny valley effect [for a recent review, see @Vaitonyte2023].
 
@@
 
-One previous study has measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
-@Saygin2012 found repetition suppression effects in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
+A previous study by @Saygin2012 measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
+They found repetition suppression effects in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
 These effects were stronger than for movies of humans or mechanical robots performing the same actions.
@@
 
-```{r include=FALSE, results='hide'}
+```{r exp1stats, include=FALSE, results='hide'}
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r exp1fig, include=FALSE, results='hide'}
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r exp2stats, include=FALSE, results='hide'}
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r exp2fig, include=FALSE, results='hide'}
 
@@
 
-knitr::include_graphics('Figures/MaskSData.pdf')
+knitr::include_graphics('Figures/MasksData.pdf')
 
@@
 
-knitr::include_graphics('Figures/MaskSMVPA.pdf')
+knitr::include_graphics('Figures/MasksMVPA.pdf')
 
@@
 
+Across two experiments using diverse stimuli, we identified a potential neurophysiological signature of the 'uncanny valley' effect.
+EEG responses to androids or silicone masks could be distinguished from responses to human faces at around 100ms after stimulus onset, and also in a later time window around 500-800ms after stimulus onset.
+There were no clear differences in the unimodal ERP response at posterior electrodes, but performance of a multivariate pattern classifier was above chance in these time windows.
+This is a different pattern from that observed for more obviously non-human stimuli (robots and Halloween masks), where there were both univariate and multivariate differences, and the multivariate discrimination accuracy was above chance for an extended time window.
+Perceptual judgements indicated that identification performance for uncanny valley stimuli was relatively poor, indicating confusion with real human images.
+The similarity in results across our two experiments is striking, and constitutes an internal conceptual replication of our main findings.
+
+Big theory
+
+Another increasingly common situation that triggers the 'uncanny valley' experience is in the domain of computer-generated images and movies.
+Artificial intelligence algorithms are now able to generate images and movies based on text prompts (for example "a picture of a girl flying a kite in a field") that often include human subjects.
+However, at time of writing, images of humans often contain errors, such as the presence of too many limbs, digits, teeth etc.
+Synthetic movies often contain continuity errors, and issues reproducing biological motion.
+Many of these errors are subtle and take time to spot, but it is also the case that human observers can report that images look 'wrong' without explicitly knowing why.
+The neural uncanny valley effect that we report here might prove a useful index of these instinctive reactions, and could even potentially be used to improve artificial intelligence algorithms.
+For example, images could be penalised for producing neural responses that differed from those for natural images.
+
 # Conclusions

### 2024-04-21 manuscript.tex
Test figure generation

@@
 \title{Neural correlates of the uncanny valley effect\\
-for robots and hyper-realistic masks\\
-(for submission to Computers in Human Behavior)}
+for robots and hyper-realistic masks}
 \author{Shona Fitzpatrick, Ailish K. Byrne, Alex Headley, Jet G. Sanders,\\
@@
 The term `uncanny valley' (Mori, 1970; English translation in Mori et al., 2012) describes the idea that entities that are clearly human or clearly artificial do not evoke unease, whereas artificial entities that are human-like are disconcerting.
-Understanding these experiences is increasingly important as artificial entities become more integrated into our everyday lives, however at present relatively little is known about the neural underpinnings of the uncanny valley effect.
+Understanding these experiences is increasingly important as artificial entities become more integrated into our everyday lives, however at present relatively little is known about the neural underpinnings of the uncanny valley effect (for a recent review, see Vaitonytė et al., 2023).
 
@@
 
-One previous study has measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
-Saygin et al.
-(2012) found repetition suppression effects in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
+A previous study by Saygin et al.
+(2012) measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
+They found repetition suppression effects in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
 These effects were stronger than for movies of humans or mechanical robots performing the same actions.
@@
 
-{\centering \includegraphics{Figures/MaskSData}
+{\centering \includegraphics{Figures/MasksData}
 
@@
 
-{\centering \includegraphics{Figures/MaskSMVPA}
+{\centering \includegraphics{Figures/MasksMVPA}
 
@@
 \section{Discussion}\label{discussion}}
+
+Across two experiments using diverse stimuli, we identified a potential neurophysiological signature of the `uncanny valley' effect.
+EEG responses to androids or silicone masks could be distinguished from responses to human faces at around 100ms after stimulus onset, and also in a later time window around 500-800ms after stimulus onset.
+There were no clear differences in the unimodal ERP response at posterior electrodes, but performance of a multivariate pattern classifier was above chance in these time windows.
+This is a different pattern from that observed for more obviously non-human stimuli (robots and Halloween masks), where there were both univariate and multivariate differences, and the multivariate discrimination accuracy was above chance for an extended time window.
+Perceptual judgements indicated that identification performance for uncanny valley stimuli was relatively poor, indicating confusion with real human images.
+The similarity in results across our two experiments is striking, and constitutes an internal conceptual replication of our main findings.
+
+Big theory
+
+Another increasingly common situation that triggers the `uncanny valley' experience is in the domain of computer-generated images and movies.
+Artificial intelligence algorithms are now able to generate images and movies based on text prompts (for example ``a picture of a girl flying a kite in a field'') that often include human subjects.
+However, at time of writing, images of humans often contain errors, such as the presence of too many limbs, digits, teeth etc.
+Synthetic movies often contain continuity errors, and issues reproducing biological motion.
+Many of these errors are subtle and take time to spot, but it is also the case that human observers can report that images look `wrong' without explicitly knowing why.
+The neural uncanny valley effect that we report here might prove a useful index of these instinctive reactions, and could even potentially be used to improve artificial intelligence algorithms.
+For example, images could be penalised for producing neural responses that differed from those for natural images.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Vaitonyte2023}{}}%
+Vaitonytė J, Alimardani M, Louwerse MM.
+2023.
+Scoping review of the neural evidence on the uncanny valley.
+\emph{Computers in Human Behavior Reports} \textbf{9}:100263.
+doi:\url{https://doi.org/10.1016/j.chbr.2022.100263}
+
 \end{CSLReferences}

### 2024-04-22 manuscript.Rmd
Testing full build with bootstrapping

@@
 
-processdata <- 1  # this flag determines the amount of processing, with 3 levels:
+processdata <- 2  # this flag determines the amount of processing, with 3 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
 
+  if (!file.exists('local/robotsmvpa/301_101.mat')){
+  osfproject <- osf_retrieve_node('uzbns')
+  osffiles <- osf_ls_files(osfproject)
+  fid <- which(osffiles$name=='robotsmvpa.zip')
+  osf_download(osffiles[fid,], path='local/',progress=TRUE)
+  unzip('local/robotsmvpa.zip',exdir='local/',overwrite=TRUE)
+  }
+  if (!file.exists('local/responsedata/301trialorderRobots.mat')){
+  osfproject <- osf_retrieve_node('uzbns')
+  osffiles <- osf_ls_files(osfproject)
+  fid <- which(osffiles$name=='responsedata.zip')
+  osf_download(osffiles[fid,], path='local/',progress=TRUE)
+  unzip('local/responsedata.zip',exdir='local/',overwrite=TRUE)
+  }
   comparisons <- matrix(c(1,2,1,3,2,3),nrow=3,ncol=2,byrow=TRUE)
@@
   for (s in 1:29){
-    data <- readMat(paste0('local/RawData/Experiment 1/',s+300,'/',s+300,'trialorderRobots.mat'))
+    data <- readMat(paste0('local/responsedata/',s+300,'trialorderRobots.mat'))
 
@@
 if (processdata > 1){
+
+  if (!file.exists('local/masksmvpa/351_101.mat')){
+  osfproject <- osf_retrieve_node('uzbns')
+  osffiles <- osf_ls_files(osfproject)
+  fid <- which(osffiles$name=='masksmvpa.zip')
+  osf_download(osffiles[fid,], path='local/',progress=TRUE)
+  unzip('local/masksmvpa.zip',exdir='local/',overwrite=TRUE)
+  }
+  if (!file.exists('local/responsedata/351trialorderMasks.mat')){
+  osfproject <- osf_retrieve_node('uzbns')
+  osffiles <- osf_ls_files(osfproject)
+  fid <- which(osffiles$name=='responsedata.zip')
+  osf_download(osffiles[fid,], path='local/',progress=TRUE)
+  unzip('local/responsedata.zip',exdir='local/',overwrite=TRUE)
+  }
 
@@
   for (s in 1:30){
-    data <- readMat(paste0('local/RawData/Experiment 2/',s+350,'/trialorderMasks.mat'))
+    data <- readMat(paste0('local/responsedata/',s+350,'trialorderMasks.mat'))
 

### 2024-04-22 manuscript.Rmd
Fixed osf download bug

--- 2024-04-21 manuscript.Rmd
@@
 
+  if (!file.exists('local/robotsmvpa/301_101.mat')){
+  osfproject <- osf_retrieve_node('uzbns')
+  osffiles <- osf_ls_files(osfproject)
+  fid <- which(osffiles$name=='robotsmvpa.zip')
+  osf_download(osffiles[fid,], path='local/',progress=TRUE)
+  unzip('local/robotsmvpa.zip',exdir='local/',overwrite=TRUE)
+  }
+  if (!file.exists('local/responsedata/301trialorderRobots.mat')){
+  osffiles <- osf_retrieve_file('fvsq8')
+  osf_download(osffiles, path='local/',progress=TRUE,conflicts='overwrite')
+  unzip('local/responsedata.zip',exdir='local/',overwrite=TRUE)
+  }
   comparisons <- matrix(c(1,2,1,3,2,3),nrow=3,ncol=2,byrow=TRUE)
@@
 if (processdata > 1){
+
+  if (!file.exists('local/masksmvpa/351_101.mat')){
+  osfproject <- osf_retrieve_node('uzbns')
+  osffiles <- osf_ls_files(osfproject)
+  fid <- which(osffiles$name=='masksmvpa.zip')
+  osf_download(osffiles[fid,], path='local/',progress=TRUE)
+  unzip('local/masksmvpa.zip',exdir='local/',overwrite=TRUE)
+  }
+    if (!file.exists('local/responsedata/351trialorderMasks.mat')){
+  osffiles <- osf_retrieve_file('fvsq8')
+  osf_download(osffiles, path='local/',progress=TRUE,conflicts='overwrite')
+  unzip('local/responsedata.zip',exdir='local/',overwrite=TRUE)
+    }
 

### 2024-05-23 manuscript.Rmd
Added discussion and abstract

--- 2024-04-21 manuscript.Rmd
@@
 author: |
-  | Shona Fitzpatrick, Ailish K. Byrne, Alex Headley, Jet G. Sanders,
-  | Helen Petrie, Rob Jenkins & Daniel H. Baker (daniel.baker@york.ac.uk)
-date: "University of York"
+  | Shona Fitzpatrick$^1$, Ailish K. Byrne$^2$, Alex Headley$^1$, Jet G. Sanders$^3$,
+  | Helen Petrie$^4$, Rob Jenkins$^1$ & Daniel H. Baker$^{1,5}$
 output:
@@
 
+1. Department of Psychology, University of York, York, UK
+2. School of Medicine, Keele University, Newcastle-under-Lyme, Staffordshire, UK
+3. Department of Psychological and Behavioural Science, London School of Economics, London, UK
+4. Department of Computer Science, University of York, York, UK
+5. Corresponding author, email: daniel.baker\@york.ac.uk
+
 ```{r setup, include=FALSE}
 
-processdata <- 1  # this flag determines the amount of processing, with 3 levels:
+processdata <- 2  # this flag determines the amount of processing, with 3 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
 
+Viewing artificial objects and images that are designed to appear human can elicit a sense of unease, referred to as the 'uncanny valley' effect.
+Here we investigate neural correlates of the uncanny valley, using still images of androids (robots designed to look human), and hyper-realistic silicone masks, in two independent experiments.
+In both cases, human-like stimuli were harder to distinguish from real human faces than examples that were clearly not designed to mimic humans (mechanical robots, and Halloween masks).
+Stimulus evoked potentials did not show convincing differences between faces and either androids or realistic masks when using traditional univariate statistical tests.
+However, a more sensitive multivariate analysis identified two regions of above-chance decoding, indicating neural differences in the response between human faces and androids/realistic masks.
+The first time window was around 100-200ms post stimulus onset, and most likely corresponds to low-level image differences between conditions.
+The second time window was around 600ms post stimulus onset, and may reflect top-down processing, and perhaps correspond to the subjective sense of unease characteristic of the uncanny valley effect.
+Objective neural components might be used in future to rapidly train generative artificial intelligence systems to produce more realistic images that are perceived as natural by human observers.
+
 # Introduction
@@
 
-A previous study by @Saygin2012 measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
+One previous study by @Saygin2012 measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
 They found repetition suppression effects in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
@@
 Stimuli subtended $11\times11$ degrees at the viewing distance of 57cm, and were shown against a mid-grey background, with a black central fixation cross displayed throughout.
-The presentation duration was 500ms, and participants were asked to press a mouse button to indicate if they believed each image was of a human or of a robot.
+The presentation duration was 500ms, and participants were asked to press a mouse button to indicate if they believed each image was of a human or of a robot/android.
 After each response there was a random duration blank period with a mean duration of 1000ms and a standard deviation of 200ms.
@@
 Five participants were excluded from the EEG analysis of each experiment due to excessive noise.
-Our attempts to clean up the data from these participants using independent components analysis was unsuccessful.
+Our attempts to clean up the data from these participants using independent components analysis were unsuccessful.
 Their behavioural data were still included in the analysis.
@@
 
-We performed univariate analyses by conducting Bayesian t-tests [@Rouder2009] between ERPs from pairs of conditions at each time point using a JZS prior.
+We performed univariate analyses by conducting Bayesian t-tests [@Rouder2009] between ERPs from pairs of conditions at each time point using a JZS prior, using signals pooled across electrodes P6, P8, PO6 and PO8.
 The resulting Bayes factor score is a summary of the evidence in favour of either the null hypothesis (that the waveforms are equal) or the alternative hypothesis (that they differ).
@@
 
-Raw data, processed data, and analysis scripts are freely available through the project repository at: https://osf.io/5nz2h/
+Raw data, processed data, and analysis scripts are freely available through the project repository at: https://doi.org/10.17605/OSF.IO/5NZ2H
 
@@
 
+  if (!file.exists('local/robotsmvpa/301_101.mat')){
+  osffiles <- osf_retrieve_file('pzcd9')
+  osf_download(osffiles, path='local/',progress=TRUE,conflicts='overwrite')
+  unzip('local/robotsmvpa.zip',exdir='local/',overwrite=TRUE)
+  }
+  if (!file.exists('local/responsedata/301trialorderRobots.mat')){
+  osffiles <- osf_retrieve_file('fvsq8')
+  osf_download(osffiles, path='local/',progress=TRUE,conflicts='overwrite')
+  unzip('local/responsedata.zip',exdir='local/',overwrite=TRUE)
+  }
   comparisons <- matrix(c(1,2,1,3,2,3),nrow=3,ncol=2,byrow=TRUE)
@@
 if (processdata > 1){
+
+  if (!file.exists('local/masksmvpa/351_101.mat')){
+  osffiles <- osf_retrieve_file('8wmxv')
+  osf_download(osffiles, path='local/',progress=TRUE,conflicts='overwrite')
+  unzip('local/masksmvpa.zip',exdir='local/',overwrite=TRUE)
+  }
+    if (!file.exists('local/responsedata/351trialorderMasks.mat')){
+  osffiles <- osf_retrieve_file('fvsq8')
+  osf_download(osffiles, path='local/',progress=TRUE,conflicts='overwrite')
+  unzip('local/responsedata.zip',exdir='local/',overwrite=TRUE)
+    }
 
@@
 
-Big theory
+Our early time window when pattern classification is above chance corresponds approximately to the P100 and N170 components of the ERP.
+Similar early components have also been investigated in other ERP studies on the uncanny valley effect [@Schindler2017; @Mustafa2016].
+This time window is unlikely to be modulated substantially by top-down influences, so we attribute the early component to image-based differences between stimulus categories [@Coggan2016].
+ERP components in later time windows have also been studied in previous work [@Urgen2018; @Mustafa2017; @Cheetham2015].
+Differences between stimulus categories at these times are more amenable to top-down influences, and most likely involve higher brain areas outside of occipital cortex.
+We therefore predict that ERP components at later time points should correspond with perceptual judgements and reports of uncanniness - this is a worthwhile hypothesis for future work to investigate.
+
+Our use of hyper-realistic silicone masks is novel in the context of the study of uncanny valley effects.
+Previous studies using these masks have demonstrated that they are difficult to distinguish from real faces [@Sanders2017], including in applied settings such as simulated passport control [@Robertson2020], and showing large individual differences [@Sanders2018].
+Image analysis indicates that good identification performance of silicone masks is typically based on attention to the region below the eyes [@Sanders2018], however it is plausible that many observers are not explicitly aware of the cues they use to perform this judgement.
+This might contribute to both the early and late components identified in this study, and presumably also to the subjective sensation of 'uncanniness' that is characteristic of the phenomenon.
 
@@
 However, at time of writing, images of humans often contain errors, such as the presence of too many limbs, digits, teeth etc.
-Synthetic movies often contain continuity errors, and issues reproducing biological motion.
+Synthetic movies often contain continuity errors, and have issues reproducing biological motion.
 Many of these errors are subtle and take time to spot, but it is also the case that human observers can report that images look 'wrong' without explicitly knowing why.
@@
 
+We have identified neural correlates of the uncanny valley effect that are consistent across two experiments, using androids and hyper-realistic silicone masks.
+In both cases, perceptual discrimination from real human faces was possible, but more challenging than discriminating from mechanical robots or Halloween masks.
+Univariate differences in the ERP signal were unconvincing, but a more sensitive multivariate classification analysis identified differences at both early (100-200ms) and later (around 600ms) time points.
+These findings suggest the importance of both bottom up and top down influences on the subjective experience of the uncanny valley.
+
 # Acknowledgements

### 2024-05-23 manuscript.tex
Added discussion and abstract

@@
 for robots and hyper-realistic masks}
-\author{Shona Fitzpatrick, Ailish K. Byrne, Alex Headley, Jet G. Sanders,\\
-Helen Petrie, Rob Jenkins \& Daniel H. Baker (\href{mailto:daniel.baker@york.ac.uk}{\nolinkurl{daniel.baker@york.ac.uk}})}
-\date{University of York}
+\author{Shona Fitzpatrick\(^1\), Ailish K. Byrne\(^2\), Alex Headley\(^1\), Jet G. Sanders\(^3\),\\
+Helen Petrie\(^4\), Rob Jenkins\(^1\) \& Daniel H. Baker\(^{1,5}\)}
+\date{}
 
@@
 
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Department of Psychology, University of York, York, UK
+\item
+  School of Medicine, Keele University, Newcastle-under-Lyme, Staffordshire, UK
+\item
+  Department of Psychological and Behavioural Science, London School of Economics, London, UK
+\item
+  Department of Computer Science, University of York, York, UK
+\item
+  Corresponding author, email: daniel.baker@york.ac.uk
+\end{enumerate}
+
 \hypertarget{abstract}{%
 \section{Abstract}\label{abstract}}
+
+Viewing artificial objects and images that are designed to appear human can elicit a sense of unease, referred to as the `uncanny valley' effect.
+Here we investigate neural correlates of the uncanny valley, using still images of androids (robots designed to look human), and hyper-realistic silicone masks, in two independent experiments.
+In both cases, human-like stimuli were harder to distinguish from real human faces than examples that were clearly not designed to mimic humans (mechanical robots, and Halloween masks).
+Stimulus evoked potentials did not show convincing differences between faces and either androids or realistic masks when using traditional univariate statistical tests.
+However, a more sensitive multivariate analysis identified two regions of above-chance decoding, indicating neural differences in the response between human faces and androids/realistic masks.
+The first time window was around 100-200ms post stimulus onset, and most likely corresponds to low-level image differences between conditions.
+The second time window was around 600ms post stimulus onset, and may reflect top-down processing, and perhaps correspond to the subjective sense of unease characteristic of the uncanny valley effect.
+Objective neural components might be used in future to rapidly train generative artificial intelligence systems to produce more realistic images that are perceived as natural by human observers.
 
@@
 
-A previous study by Saygin et al.
+One previous study by Saygin et al.
 (2012) measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
@@
 Stimuli subtended \(11\times11\) degrees at the viewing distance of 57cm, and were shown against a mid-grey background, with a black central fixation cross displayed throughout.
-The presentation duration was 500ms, and participants were asked to press a mouse button to indicate if they believed each image was of a human or of a robot.
+The presentation duration was 500ms, and participants were asked to press a mouse button to indicate if they believed each image was of a human or of a robot/android.
 After each response there was a random duration blank period with a mean duration of 1000ms and a standard deviation of 200ms.
@@
 
-We performed univariate analyses by conducting Bayesian t-tests (Rouder et al., 2009) between ERPs from pairs of conditions at each time point using a JZS prior.
+We performed univariate analyses by conducting Bayesian t-tests (Rouder et al., 2009) between ERPs from pairs of conditions at each time point using a JZS prior, using signals pooled across electrodes P6, P8, PO6 and PO8.
 The resulting Bayes factor score is a summary of the evidence in favour of either the null hypothesis (that the waveforms are equal) or the alternative hypothesis (that they differ).
@@
 
-Raw data, processed data, and analysis scripts are freely available through the project repository at: \url{https://osf.io/5nz2h/}
+Raw data, processed data, and analysis scripts are freely available through the project repository at: \url{https://doi.org/10.17605/OSF.IO/5NZ2H}
 
@@
 
-Big theory
+Our early time window when pattern classification is above chance corresponds approximately to the P100 and N170 components of the ERP.
+Similar early components have also been investigated in other ERP studies on the uncanny valley effect (Mustafa and Magnor, 2016; Schindler et al., 2017).
+This time window is unlikely to be modulated substantially by top-down influences, so we attribute the early component to image-based differences between stimulus categories (Coggan et al., 2016).
+ERP components in later time windows have also been studied in previous work (Cheetham et al., 2015; Mustafa et al., 2017; Urgen et al., 2018).
+Differences between stimulus categories at these times are more amenable to top-down influences, and most likely involve higher brain areas outside of occipital cortex.
+We therefore predict that ERP components at later time points should correspond with perceptual judgements and reports of uncanniness - this is a worthwhile hypothesis for future work to investigate.
+
+Our use of hyper-realistic silicone masks is novel in the context of the study of uncanny valley effects.
+Previous studies using these masks have demonstrated that they are difficult to distinguish from real faces (Sanders et al., 2017), including in applied settings such as simulated passport control (Robertson et al., 2020), and showing large individual differences (Sanders and Jenkins, 2018).
+Image analysis indicates that good identification performance of silicone masks is typically based on attention to the region below the eyes (Sanders and Jenkins, 2018), however it is plausible that many observers are not explicitly aware of the cues they use to perform this judgement.
+This might contribute to both the early and late components identified in this study, and presumably also to the subjective sensation of `uncanniness' that is characteristic of the phenomenon.
 
@@
 However, at time of writing, images of humans often contain errors, such as the presence of too many limbs, digits, teeth etc.
-Synthetic movies often contain continuity errors, and issues reproducing biological motion.
+Synthetic movies often contain continuity errors, and have issues reproducing biological motion.
 Many of these errors are subtle and take time to spot, but it is also the case that human observers can report that images look `wrong' without explicitly knowing why.
@@
 \section{Conclusions}\label{conclusions}}
+
+We have identified neural correlates of the uncanny valley effect that are consistent across two experiments, using androids and hyper-realistic silicone masks.
+In both cases, perceptual discrimination from real human faces was possible, but more challenging than discriminating from mechanical robots or Halloween masks.
+Univariate differences in the ERP signal were unconvincing, but a more sensitive multivariate classification analysis identified differences at both early (100-200ms) and later (around 600ms) time points.
+These findings suggest the importance of both bottom up and top down influences on the subjective experience of the uncanny valley.
 
@@
 Chang C-C, Lin C-J. 2011. {LIBSVM} : A library for support vector machines. \emph{ACM Transactions on Intelligent Systems and Technology} \textbf{2(27)}:1--27.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Cheetham2015}{}}%
+Cheetham M, Wu L, Pauli P, Jancke L.
+2015.
+Arousal, valence, and the uncanny valley: Psychophysiological and self-report findings.
+\emph{Front Psychol} \textbf{6}:981.
+doi:\href{https://doi.org/10.3389/fpsyg.2015.00981}{10.3389/fpsyg.2015.00981}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Coggan2016}{}}%
+Coggan DD, Baker DH, Andrews TJ.
+2016.
+The role of visual and semantic properties in the emergence of category-specific patterns of neural response in the human brain.
+\emph{eNeuro} \textbf{3}.
+doi:\href{https://doi.org/10.1523/ENEURO.0158-16.2016}{10.1523/ENEURO.0158-16.2016}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Mustafa2017}{}}%
+Mustafa M, Guthe S, Tauscher J-P, Goesele M, Magnor M.
+2017.
+How human am i?: EEG-based evaluation of virtual charactersProceedings of the 2017 CHI Conference on Human Factors in Computing Systems, CHI 17.
+ACM.
+doi:\href{https://doi.org/10.1145/3025453.3026043}{10.1145/3025453.3026043}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Mustafa2016}{}}%
+Mustafa M, Magnor M.
+2016.
+EEG based analysis of the perception of computer-generated faces.Proceedings of the 13th European Conference on Visual Media Production (CVMP 2016), CVMP 2016.
+ACM.
+doi:\href{https://doi.org/10.1145/2998559.2998563}{10.1145/2998559.2998563}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Robertson2020}{}}%
+Robertson DJ, Sanders JG, Towler A, Kramer RSS, Spowage J, Byrne A, Burton AM, Jenkins R.
+2020.
+Hyper-realistic face masks in a live passport-checking task.
+\emph{Perception} \textbf{49}:298--309.
+doi:\href{https://doi.org/10.1177/0301006620904614}{10.1177/0301006620904614}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Rouder2009}{}}%
@@
 doi:\href{https://doi.org/10.3758/PBR.16.2.225}{10.3758/PBR.16.2.225}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sanders2018}{}}%
+Sanders JG, Jenkins R.
+2018.
+Individual differences in hyper-realistic mask detection.
+\emph{Cogn Res Princ Implic} \textbf{3}:24.
+doi:\href{https://doi.org/10.1186/s41235-018-0118-3}{10.1186/s41235-018-0118-3}
 
@@
 doi:\href{https://doi.org/10.1093/scan/nsr025}{10.1093/scan/nsr025}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schindler2017}{}}%
+Schindler S, Zell E, Botsch M, Kissler J.
+2017.
+Differential effects of face-realism and emotion on event-related brain potentials and their implications for the uncanny valley theory.
+\emph{Sci Rep} \textbf{7}:45003.
+doi:\href{https://doi.org/10.1038/srep45003}{10.1038/srep45003}
 

### 2024-05-23 plotindividuals.R

@@ -2,11 +2,11 @@
 if (file.exists('local/GroupDataRobots.RData')){load('local/GroupDataRobots.RData')}  
 targetelectrodes <- c(28,54,58,64)
 
-pdf(paste0('Figures/allERProbot.pdf'), bg="transparent", height = 12, width = 10)
+pdf(paste0('Figures/allERProbot.pdf'), bg="transparent", height = 12, width = 12)
 
-par(mfrow=c(6,5))
+par(mfrow=c(5,5))
 
-for (s in 1:28){
+for (s in 1:24){
 plotlims <- c(-200,1000,-12,12)  
 ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
 ticklocsy <- seq(-12,12,4)    # locations of tick marks on y axis
@@ -45,7 +45,7 @@ title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=2.2, cex.lab=1)
 lines(c(-200,1000),c(0,0),lty=1)
 lines(c(0,0),c(-20,20),lty=1)
 
-includeds <- 1:28
+includeds <- 1:24
 lines(-200:1000, apply(subjmeanERP[includeds,targetelectrodes,],3,mean), lwd=3)     
 
 
@@ -56,9 +56,9 @@ dev.off()
 
 
 
-pdf(paste0('Figures/allMVPArobot.pdf'), bg="transparent", height = 12, width = 10)
+pdf(paste0('Figures/allMVPArobot.pdf'), bg="transparent", height = 12, width = 12)
 
-par(mfrow=c(6,5))
+par(mfrow=c(5,5))
 
 plotlims <- c(-200,1000,0,100)  
 ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
@@ -66,7 +66,7 @@ ticklocsy <- seq(0,100,25)    # locations of tick marks on y axis
 ticklabelsx <- ticklocsx        # set labels for x ticks
 ticklabelsy <- ticklocsy    # set labels for y ticks
 
-for (s in 1:28){
+for (s in 1:24){
 
   plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
   axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
[…]

### 2024-06-30 manuscript.Rmd
Incorporated co-author comments and questionnaire data. Anonymised for submission.

@@
   | for robots and hyper-realistic masks 
-author: |
-  | Shona Fitzpatrick$^1$, Ailish K. Byrne$^2$, Alex Headley$^1$, Jet G. Sanders$^3$,
-  | Helen Petrie$^4$, Rob Jenkins$^1$ & Daniel H. Baker$^{1,5}$
 output:
@@
 bibliography: references.bib
-csl: elife.csl
+csl: computers-in-human-behavior.csl
 ---
 
-1. Department of Psychology, University of York, York, UK
-2. School of Medicine, Keele University, Newcastle-under-Lyme, Staffordshire, UK
-3. Department of Psychological and Behavioural Science, London School of Economics, London, UK
-4. Department of Computer Science, University of York, York, UK
-5. Corresponding author, email: daniel.baker\@york.ac.uk
+[**Author information redacted for blind peer review**]
+
+<!-- author: | -->
+<!--   | Shona Fitzpatrick$^1$, Ailish K. Byrne$^2$, Alex Headley$^1$, Jet G. Sanders$^3$, -->
+<!--   | Helen Petrie$^4$, Rob Jenkins$^1$ & Daniel H. Baker$^{1,5}$ -->
+
+<!-- 1. Department of Psychology, University of York, York, UK -->
+<!-- 2. School of Medicine, Keele University, Newcastle-under-Lyme, Staffordshire, UK -->
+<!-- 3. Department of Psychological and Behavioural Science, London School of Economics, London, UK -->
+<!-- 4. Department of Computer Science, University of York, York, UK -->
+<!-- 5. Corresponding author, email: daniel.baker\@york.ac.uk -->
 
@@
 
-processdata <- 2  # this flag determines the amount of processing, with 3 levels:
+processdata <- 0  # this flag determines the amount of processing, with 3 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
 # check which packages are installed, install the missing ones, and activate
-packagelist <- c('knitr','e1071','signal','osfr','tictoc','BayesFactor','reshape2','powerplus','R.matlab') # list of CRAN packages
+packagelist <- c('knitr','e1071','signal','osfr','tictoc','BayesFactor','reshape2','R.matlab') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
@@
 
-  if (!file.exists('local/channel.mat')){
+filelist <- c('channel.mat','channeldata.csv','maskquestionnairelong.csv','robotquestionnairelong.csv')
+
+for (f in 1:length(filelist)){
+  if (!file.exists(paste0('local/',filelist[f]))){
   osfproject <- osf_retrieve_node('uzbns')
   osffiles <- osf_ls_files(osfproject)
-  fid <- which(osffiles$name=='channel.mat')
+  fid <- which(osffiles$name==filelist[f])
   osf_download(osffiles[fid,], path='local/',progress=TRUE)}
-
-  if (!file.exists('local/channeldata.csv')){
-  osfproject <- osf_retrieve_node('uzbns')
-  osffiles <- osf_ls_files(osfproject)
-  fid <- which(osffiles$name=='channeldata.csv')
-  osf_download(osffiles[fid,], path='local/',progress=TRUE)}
+}
 
@@
 Viewing artificial objects and images that are designed to appear human can elicit a sense of unease, referred to as the 'uncanny valley' effect.
-Here we investigate neural correlates of the uncanny valley, using still images of androids (robots designed to look human), and hyper-realistic silicone masks, in two independent experiments.
-In both cases, human-like stimuli were harder to distinguish from real human faces than examples that were clearly not designed to mimic humans (mechanical robots, and Halloween masks).
+Here we investigate neural correlates of the uncanny valley, using still images of androids (robots designed to look human), and humans wearing hyper-realistic silicone masks, as well as still images of real humans, in two experiments.
+In both experiments, human-like stimuli were harder to distinguish from real human faces than stimuli that were clearly not designed to mimic humans but contain facial features (mechanical robots and Halloween masks).
 Stimulus evoked potentials did not show convincing differences between faces and either androids or realistic masks when using traditional univariate statistical tests.
@@
 The first time window was around 100-200ms post stimulus onset, and most likely corresponds to low-level image differences between conditions.
-The second time window was around 600ms post stimulus onset, and may reflect top-down processing, and perhaps correspond to the subjective sense of unease characteristic of the uncanny valley effect.
+The second time window was around 600ms post stimulus onset, and may reflect top-down processing, and may correspond to the subjective sense of unease characteristic of the uncanny valley effect.
 Objective neural components might be used in future to rapidly train generative artificial intelligence systems to produce more realistic images that are perceived as natural by human observers.
@@
 
-Many people report an aversion to entities that are superficially human-like, but on closer inspection are actually artificial.
-Examples include humanoid robots (androids), puppets, hyper-realistic masks, and computer-generated images or movies.
-The term 'uncanny valley' [@Mori1970; English translation in @Mori2012] describes the idea that entities that are clearly human or clearly artificial do not evoke unease, whereas artificial entities that are human-like are disconcerting.
-Understanding these experiences is increasingly important as artificial entities become more integrated into our everyday lives, however at present relatively little is known about the neural underpinnings of the uncanny valley effect [for a recent review, see @Vaitonyte2023].
+Many people report an aversion to entities that are superficially human-like, but on closer inspection turn out to be artificial.
+Examples include humanoid robots (androids), puppets, hyper-realistic masks [@Sanders2021], and computer-generated images or movies.
+The term 'uncanny valley' [@Mori1970; English translation in @Mori2012] describes the idea that clearly human or clearly artificial entities do not evoke unease, whereas artificial entities that are human-like are disconcerting.
+Understanding these experiences is increasingly important as artificial entities become more integrated into our everyday lives.
+However at present relatively little is known about the neural underpinnings of the uncanny valley effect [for a recent review, see @Vaitonyte2023].
 
@@
 For example, areas of the occipital lobe [@Gauthier2000] and fusiform gyrus [@Kanwisher1997] respond more to faces than non-face stimuli, and sections of extrastriate cortex are responsive to bodies [@Downing2001].
-There are also event-related potential (ERP) signals associated with face and body stimuli, though their precise purpose is still debated [@Thierry2007].
-It seems highly likely that 'uncanny' images will activate these same processes, yet it is unclear whether the sense of unease they produce occurs at bottom-up sensory stages, or is modulated by more top-down cognitive factors.
+There are also event-related potential (ERP) signals associated with face and body stimuli, though their precise role is still debated [@Thierry2007; @Hong2022].
+It seems highly likely that 'uncanny' images will activate these same processes, yet it is unclear whether the sense of unease they produce occurs at bottom-up sensory stages or is modulated by more top-down cognitive factors.
 
 One previous study by @Saygin2012 measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
-They found repetition suppression effects in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
+They found repetition suppression effects^[Repetition suppression is a phenomenon in which the neural responses to repeated presentations of identical or similar stimuli is reduced relative to the response on the first presentation.] in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
 These effects were stronger than for movies of humans or mechanical robots performing the same actions.
-A more recent electroencephalography (EEG) study [@Urgen2018] identified a difference in the N400 component between dynamic and static conditions using the same stimuli.
-Although this difference was strongest over frontal electrodes, source reconstruction of the N400 itself suggested a left-lateralised source in temporo-parietal cortex, consistent with the fMRI results [@Saygin2012].
+A more recent electroencephalography (EEG) study [@Urgen2018] identified a difference in the N400 component^[The N400 is an electromagnetic brain potential obtained 400ms after stimulus onset, typically over centro-parietal electrodes.
+It has been proposed to reflect the extent to which the stimulus presented was surprising or unexpected.] between dynamic and static conditions using the same stimuli.
+Although this difference was strongest over frontal electrodes, source reconstruction of the N400 itself suggested a left-lateralised source in the temporo-parietal cortex, consistent with the fMRI results [@Saygin2012].
 The authors interpret both of these findings as being due to the discrepancy between the human-like appearance and the clearly non-biological motion of the robot.
 
-Our aim here was to further investigate neural correlates of the uncanny valley effect.
-We achieve this through two EEG experiments, in which we measure neural responses to static images.
-In the first experiment, the stimuli were humans, machine-like robots, and human-like robots (see Figure \ref{fig:stimexamples}a).
+Our aim was to further investigate neural correlates of the uncanny valley effect.
+We achieved this through two EEG experiments, in which we measured neural responses to static images.
+In the first experiment, the stimuli were still images of humans, machine-like robots, and human-like robots (see Figure \ref{fig:stimexamples}a).
 In the second experiment we aimed to generalise the finding by using images of people wearing no masks, wearing obvious masks (e.g.
-carnival or Halloween masks), and wearing hyper-realistic silicone masks [@Sanders2017] (see Figure \ref{fig:stimexamples}b).
+Halloween masks), and wearing hyper-realistic silicone masks [@Sanders2017] (see Figure \ref{fig:stimexamples}b).
 Rather than focus on specific ERP components, we use a multivariate pattern classification approach to identify time windows in which information in the EEG signal can be used to distinguish between pairs of conditions.
@@
 Row (a) shows a human face, an android and a robot, all against white backgrounds.
-Row (b) shows a human face, a hyper-realistic silicone mask, and a carnival mask, all against natural backgrounds.
+Row (b) shows a human face, a hyper-realistic silicone mask, and a Halloween mask, all against natural backgrounds.
 Images were taken from a variety of sources that permit reuse in academic contexts and in most cases were not part of the stimulus set from the experiments.
@@
 
-A total of 29 participants completed Experiment 1 (12 male, 17 female), and 30 participants completed Experiment 2 (7 male, 23 female).
+A total of 29 participants completed Experiment 1 (12 male, 17 female), and 30 different participants completed Experiment 2 (7 male, 23 female).
 None of the participants had previously taken part in a study using these stimuli, and all were naïve to the hypotheses and wore their normal optical correction if required.
-Written informed consent was collected before each experiment began, and all procedures were approved by the Ethics committee of the Department of Psychology at the University of York.
+Written informed consent was collected before each experiment began, and all procedures were approved by the Ethics committee of [**redacted for blind peer review**].
 
@@
 Images all showed the head and shoulders of the subject, had white backgrounds, and were sourced from the internet.
-In Experiment 2, the stimulus set consisted of a total of 296 images, comprising real faces (148 images), people wearing silicone masks (74 images), and people wearing obvious masks of the sort typically worn for carnivals and Halloween celebrations (74 images).
+In Experiment 2, the stimulus set (first described by @Sanders2019, but here including additional images) consisted of a total of 296 images, comprising real faces (148 images), people wearing silicone masks (74 images), and people wearing obvious masks of the sort typically worn for carnivals and Halloween celebrations (74 images).
 The backgrounds of these images were more heterogeneous, and showed the natural surroundings of the subject.
@@
 
-### Experiment 1: robots
+### Experiment 1: Robots
 
@@
 
-### Experiment 2: hyper-realistic masks
+After the EEG experiment, participants also completed a series of questionnaires using the Qualtrics platform.
+These involved rating their perception of a subset of the stimuli (8 from each category), using items from the Godspeed questionnaire [@Bartneck2009].
+Inspection time was unlimited.
+Participants also provided demographic information (age, gender) and completed the GAToRS [@Koverola2022] and AQ [@Baron-Cohen2001] questionnaires, however the results of these additional questionnaires are not presented here.
+
+### Experiment 2: Hyper-realistic masks
 
@@
 In the third block, stimuli doubled in size again, and subtended $22\times30$ degrees.
-The rationale for the size manipulation was to investigate whether increasing levels of detail made the silicone masks more identifiable [@Sanders2017], however as that is not the main focus of the current paper we collapse results across size conditions.
+The rationale for the size manipulation was to investigate whether increasing levels of detail made the silicone masks more identifiable [@Sanders2017; @Sanders2019].
+However as that is not the main focus of the current paper, and our preliminary analyses indicated no differences between size conditions, we collapse results across size conditions.
 Stimuli were presented for 250ms, and participants indicated whether they thought each image contained a real face or a mask, using a two-button trackball.
@@
 
+An independent group of 20 participants also completed an online questionnaire in which they rated the images along various dimensions.
+The participants repeated the real face vs mask judgement from the main experiment, and were additionally asked to rate emotional expressiveness, realism, and uncanniness for each image using a 7-point Likert scale.
+Inspection time was unlimited for these judgments.
+
 ## Data analysis
@@
 
-EEG signals were recorded during each block, and saved to disc for subsequent offline analysis.
+EEG signals were recorded during each block and saved to disc for subsequent offline analysis.
 We used components of the EEGlab toolbox [@Delorme2004] to import the data into Matlab and collate data across blocks.
@@
 Our attempts to clean up the data from these participants using independent components analysis were unsuccessful.
-Their behavioural data were still included in the analysis.
-In Experiment 2 we combined data across all three image sizes, as this was not the main focus of our analysis.
+Their behavioural data were unaffected, and therefore still included in the analysis.
 
@@
 
-Multivariate pattern analysis was conducted by training a linear support vector machine algorithm (LibSVM; @Chang2011) to discriminate between patterns of activity across electrodes at a specific time point.
+Multivariate pattern analysis was conducted by training a linear support vector machine algorithm [LibSVM, @Chang2011] to discriminate between patterns of activity across electrodes at a specific time point.
 The patterns came from the human face condition and one of the other conditions, for a single participant.
-Four examples of each pattern were calculated by averaging over random subsets of 20\% of the available trials from a given condition, and using these to train the classifier.
-The accuracy of the classifier was tested on the averaged remaining trials (that were not used in training) for each condition.
+Four examples of each pattern were calculated by averaging over random subsets of 20\% of the available trials from a given condition, and these were used to train the classifier.
+The accuracy of the classifier was tested on the remaining trials (that were not used in training) for each condition.
 This process was repeated 1000 times with different trial permutations to obtain an average accuracy, where chance performance is at 50\% correct.
-The analysis was carried out at all time points, and also for all participants.
+The analysis was carried out at all time points, and for each participant separately.
 We then averaged classifier accuracy across participants, and calculated one sample Bayesian t-tests comparing to chance performance at each time point as described above.
@@
 
-Raw data, processed data, and analysis scripts are freely available through the project repository at: https://doi.org/10.17605/OSF.IO/5NZ2H
+Raw data, processed data, and analysis scripts are freely available through the project repository at: [**redacted for blind peer review**] 
+<!-- https://doi.org/10.17605/OSF.IO/5NZ2H -->
 
@@
 
+```{r exp1questionnaires, include=FALSE, results='hide'}
+
+qlist <- c('Fake-Natural','Unconscious-Conscious','Apathetic-Responsive','Dislike-Like','Unfriendly-Friendly','Stagnant-Lively','Unintelligent-Intelligent','Irresponsible-Responsible','Anxious-Relaxed','Surprised-Quiescent')
+
+robotQdata <- read.csv('local/robotquestionnairelong.csv')
+
+filelist <- unique(robotQdata$File)
+plist <- unique(robotQdata$Participant)
+measurelist <- unique(robotQdata$Measure)
+
+sortedQdata <- array(0,dim=c(length(plist),length(filelist),length(measurelist)))
+for (file in 1:length(filelist)){
+  conddata <- subset(robotQdata,File==filelist[file],)
+  for (measure in 1:length(measurelist)){
+    measuredata <- subset(conddata,Measure==measurelist[measure])
+    for (p in 1:length(plist)){
+      pdata <- subset(measuredata,Participant==plist[p])
+
+      sortedQdata[p,file,measure] <- pdata$Response
+    }
+  }
+}
+
+conditionQdata <- array(0,dim=c(29,3,10))
+conditionQdata[,1,] <- apply(sortedQdata[,1:8,],c(1,3),mean)
+conditionQdata[,2,] <- apply(sortedQdata[,9:16,],c(1,3),mean)
+conditionQdata[,3,] <- apply(sortedQdata[,17:24,],c(1,3),mean)
+
+meanQdata <- apply(conditionQdata,c(2,3),mean)
+
+pdf(paste0('Figures/RobotRatings.pdf'), bg="transparent", height = 30, width = 12)
+
+par(mfrow=c(5,2))
+
+plotlims <- c(1,5,0.5,3.5)  
+ticklocsy <- c(0.5,1,2,3,3.5)    
+ticklocsx <- seq(1,5,1)    # locations of tick marks on y axis
+ticklabelsy <- c("","Robot","Android","Human","")       
+ticklabelsx <- ticklocsx    # set labels for y ticks
+
+for (cond in 1:10){
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx,line=1,cex=1.5)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=3,cex=1.5) 
+title(xlab=qlist[cond], col.lab=rgb(0,0,0), line=2.4, cex.lab=2)
+
+text(1.15,3.3,paste0('(',letters[cond],')'),cex=3)
+
+a <- density(conditionQdata[,1,cond],cut=6)
+a$y <- 0.35*a$y/max(a$y)
+polygon(a$x,1.1+a$y,border=NA,col=addalpha(collist[1],0.5))
+
+a <- density(conditionQdata[,2,cond])
+a$y <- 0.35*a$y/max(a$y)
+polygon(a$x,2.1+a$y,border=NA,col=addalpha(collist[2],0.5))
+
+a <- density(conditionQdata[,3,cond])
+a$y <- 0.35*a$y/max(a$y)
+polygon(a$x,3.1+a$y,border=NA,col=addalpha(collist[3],0.5))
+
+xvals <- seq(-0.1,0.1,length=nrow(conditionQdata))
+points(conditionQdata[,1,cond],1+xvals-0.2,pch=16,col=collist[1])
+points(conditionQdata[,2,cond],2+xvals-0.2,pch=15,col=collist[2])
+points(conditionQdata[,3,cond],3+xvals-0.2,pch=18,col=collist[3])
+
+for (cond2 in 1:3){
+  bs <- NULL
+  for (n in 1:nbootstraps){bs[n] <- mean(sample(conditionQdata[,cond2,cond],replace=TRUE))}
+  ci <- quantile(bs,c(0.025,0.975))
+  arrows(mean(conditionQdata[,cond2,cond]),cond2,ci[1],cond2,angle=90,length=0.1,lwd=3)
+  arrows(mean(conditionQdata[,cond2,cond]),cond2,ci[2],cond2,angle=90,length=0.1,lwd=3)
+}
+
+points(mean(conditionQdata[,1,cond]),1,pch=21,cex=2,lwd=2,bg=collist[1])
+points(mean(conditionQdata[,2,cond]),2,pch=22,cex=2,lwd=2,bg=collist[2])
+points(mean(conditionQdata[,3,cond]),3,pch=23,cex=2,lwd=2,bg=collist[3])
+
+}
+
+dev.off()
+
+```
+
 We first explored the behavioural results for identification of human versus non-human stimuli.
@@
 
-EEG activity showed a clear visually evoked potential over posterior electrode sites (see Figure \ref{fig:RobotsData}c), with typical components found in response to visual stimuli (the P100, N170 and P200 are indicated in the figure).
+EEG activity showed a clear visually evoked potential over posterior electrode sites (see Figure \ref{fig:RobotsData}c), with typical components found in response to visual stimuli pooled across all conditions (the P100, N170 and P200 are indicated in the figure).
 Pairwise comparisons of conditions are shown in Figure \ref{fig:RobotsMVPA}a,b.
-In general there is a tendency for the ERP response to human faces to diverge slightly from the other two conditions, however the evidence for a convincing difference was not compelling.
+In general there is a tendency for the ERP response to human faces to diverge slightly from the other two conditions [@Geiger2021], however the evidence for this divergence was not compelling.
 Bayes factors exceeded 3 for only a small number of time points around 300-400ms in the comparison between human and robot images (see yellow bars at y = -8 in Figure \ref{fig:RobotsMVPA}a), but these differences were small considering the variance in the data.
@@
 However we first sought to generalise our results to a different stimulus set, and next report the results of Experiment 2 which used hyper-realistic silicone masks.
+
+Finally, we analysed the rating data from a set of 10 questionnaire items for 8 stimuli from each category.
+The results are summarised in Figure \@ref(fig:robotratings), and in general show differences between stimulus categories along most dimensions.
+Of particular note, the U-shaped function predicted by the uncanny valley effect was apparent for ratings along the Dislike-Like (Figure \@ref(fig:robotratings)d), Unfriendly-Friendly (Figure \@ref(fig:robotratings)e), and Anxious-Relaxed (Figure \@ref(fig:robotratings)i) dimensions.
+These are all dimensions with emotional valence, indicating support for the 'uncanniness' of our android stimuli.
+However we note that the android and robot categories were typically rated as being more similar to each other than to the real human faces.
+
+```{r robotratings, fig.cap="Ratings of stimuli using items from the Godspeed questionnaire.
+Each rating was on a Likert scale from 1-5, and was the average of ratings from 8 stimulus examples.
+Dots show individual participant scores, with the larger symbols indicating the mean and 95\\% bootstrapped confidence intervals.", fig.align="center", out.width="50%", echo=FALSE}
+
+knitr::include_graphics('Figures/RobotRatings.pdf')
+
+```
 
@@
 
+```{r exp2questionnaires, include=FALSE, results='hide'}
+
+maskQdata <- read.csv('local/maskquestionnairelong.csv')
+comparisons <- matrix(c(1,2,1,3,2,3),nrow=3,ncol=2,byrow=TRUE)
+
+hits <- matrix(0,nrow=20,ncol=3)
+misses <- matrix(0,nrow=20,ncol=3)
+
+accdata <- subset(maskQdata,maskQdata$Measure=='Acc')
+for (s in 1:20){
+  thissubj <- subset(accdata,accdata$Participant==s)
+  condition <- NULL
+  for (i in 1:nrow(thissubj)){
+    if (grepl('hm',thissubj$File[i])){condition[i] <- 1}
+    if (grepl('sm',thissubj$File[i])){condition[i] <- 2}    
+    if (grepl('rf',thissubj$File[i])){condition[i] <- 3}
+  }
+  for (i in 1:nrow(thissubj)){
+    hits[s,condition[i]] <- hits[s,condition[i]] + thissubj$Response[i] 
+    misses[s,condition[i]] <- misses[s,condition[i]] + (1-thissubj$Response[i])
+  }}
+
+hitrate <- hits / (hits + misses)
+falsealarms <- 0*hitrate
+falsealarms[,1] <- misses[,3] / (misses[,3] + hits[,3])
+falsealarms[,2] <- misses[,3] / (misses[,3] + hits[,3])
+falsealarms[,3] <- rowMeans(misses[,1:2]) / (rowMeans(misses[,1:2]) + rowMeans(hits[,1:2]))
+
+subjdprime <- qnorm(hitrate) - qnorm(falsealarms)
+subjdprime[which(is.infinite(subjdprime))] <- 5
+meandprimes <- colMeans(subjdprime)
+
+condlist <- unique(maskQdata$Condition)
+plist <- unique(maskQdata$Participant)
+measurelist <- unique(maskQdata$Measure)
+
+averageQdata <- array(0,dim=c(length(plist),length(condlist),length(measurelist)))
+
+for (cond in 1:length(condlist)){
+  conddata <- subset(maskQdata,Condition==condlist[cond],)
+  for (measure in 1:length(measurelist)){
+    measuredata <- subset(conddata,Measure==measurelist[measure])
+    for (p in 1:length(plist)){
+      pdata <- subset(measuredata,Participant==plist[p])
+
+      averageQdata[p,cond,measure] <- mean(pdata$Response)
+    }
+  }
+}
+meanQscores <- apply(averageQdata,2:3,mean)
+
+dataforANOVA <- melt(subjdprime)
+colnames(dataforANOVA) <- c('Participant','Condition','dprime')
+dataforANOVA$Participant <- as.factor(dataforANOVA$Participant)
+dataforANOVA$Condition <- as.factor(dataforANOVA$Condition)
+bfdprime2 <- extractBF(anovaBF(dprime ~ Condition,dataforANOVA,whichRandom='Participant'))$bf
+
+bfcontrasts2 <- NULL
+for (comp in 1:3){
+bfcontrasts2[comp] <- extractBF(ttestBF(subjdprime[,comparisons[comp,1]],subjdprime[,comparisons[comp,2]],paired=TRUE))$bf}
+
+dataforANOVA <- melt(averageQdata[,,1])
+colnames(dataforANOVA) <- c('Participant','Condition','dprime')
+dataforANOVA$Participant <- as.factor(dataforANOVA$Participant)
+dataforANOVA$Condition <- as.factor(dataforANOVA$Condition)
+bfEmoE <- extractBF(anovaBF(dprime ~ Condition,dataforANOVA,whichRandom='Participant'))$bf
+
+bfcontrastsEmoE <- NULL
+for (comp in 1:3){
+bfcontrastsEmoE[comp] <- extractBF(ttestBF(averageQdata[,comparisons[comp,1],1],averageQdata[,comparisons[comp,2],1],paired=TRUE))$bf}
+
+dataforANOVA <- melt(averageQdata[,,2])
+colnames(dataforANOVA) <- c('Participant','Condition','dprime')
+dataforANOVA$Participant <- as.factor(dataforANOVA$Participant)
+dataforANOVA$Condition <- as.factor(dataforANOVA$Condition)
+bfReal <- extractBF(anovaBF(dprime ~ Condition,dataforANOVA,whichRandom='Participant'))$bf
+
+bfcontrastsReal <- NULL
+for (comp in 1:3){
+bfcontrastsReal[comp] <- extractBF(ttestBF(averageQdata[,comparisons[comp,1],2],averageQdata[,comparisons[comp,2],2],paired=TRUE))$bf}
+
+dataforANOVA <- melt(averageQdata[,,3])
+colnames(dataforANOVA) <- c('Participant','Condition','dprime')
+dataforANOVA$Participant <- as.factor(dataforANOVA$Participant)
+dataforANOVA$Condition <- as.factor(dataforANOVA$Condition)
+bfUncan <- extractBF(anovaBF(dprime ~ Condition,dataforANOVA,whichRandom='Participant'))$bf
+
+bfcontrastsUncan <- NULL
+for (comp in 1:3){
+bfcontrastsUncan[comp] <- extractBF(ttestBF(averageQdata[,comparisons[comp,1],3],averageQdata[,comparisons[comp,2],3],paired=TRUE))$bf}
+
+if (processdata > 0){
+
+pdf(paste0('Figures/MaskRatings.pdf'), bg="transparent", height = 12, width = 12)
+
+par(mfrow=c(2,2))
+
+plotlims <- c(1,7,0.5,3.5)  
+ticklocsy <- c(0.5,1,2,3,3.5)    
+ticklocsx <- seq(1,7,1)    # locations of tick marks on y axis
+ticklabelsy <- c("","Halloween","Silicone","Human","")       
+ticklabelsx <- ticklocsx    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx,line=0.5,cex=1.5)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=3,cex=1.5) 
+title(xlab="Emotional Expressiveness", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.8)
+
+text(1.15,3.3,'(a)',cex=3)
+
+a <- density(averageQdata[,1,1],cut=6)
+a$y <- 0.35*a$y/max(a$y)
+polygon(a$x,1.1+a$y,border=NA,col=addalpha(collist[1],0.5))
+
+a <- density(averageQdata[,2,1])
+a$y <- 0.35*a$y/max(a$y)
+polygon(a$x,2.1+a$y,border=NA,col=addalpha(collist[2],0.5))
+
+a <- density(averageQdata[,3,1])
+a$y <- 0.35*a$y/max(a$y)
+polygon(a$x,3.1+a$y,border=NA,col=addalpha(collist[3],0.5))
+
+xvals <- seq(-0.1,0.1,length=nrow(averageQdata))
+points(averageQdata[,1,1],1+xvals-0.2,pch=16,col=collist[1])
+points(averageQdata[,2,1],2+xvals-0.2,pch=15,col=collist[2])
+points(averageQdata[,3,1],3+xvals-0.2,pch=18,col=collist[3])
+
+for (cond in 1:3){
+  bs <- NULL
+  for (n in 1:nbootstraps){bs[n] <- mean(sample(averageQdata[,cond,1],replace=TRUE))}
+  ci <- quantile(bs,c(0.025,0.975))
+  arrows(mean(averageQdata[,cond,1]),cond,ci[1],cond,angle=90,length=0.1,lwd=3)
+  arrows(mean(averageQdata[,cond,1]),cond,ci[2],cond,angle=90,length=0.1,lwd=3)
+}
+
+points(mean(averageQdata[,1,1]),1,pch=21,cex=2,lwd=2,bg=collist[1])
+points(mean(averageQdata[,2,1]),2,pch=22,cex=2,lwd=2,bg=collist[2])
+points(mean(averageQdata[,3,1]),3,pch=23,cex=2,lwd=2,bg=collist[3])
+
+plotlims <- c(1,7,0.5,3.5)  
+ticklocsy <- c(0.5,1,2,3,3.5)    
+ticklocsx <- seq(1,7,1)    # locations of tick marks on y axis
+ticklabelsy <- c("","Halloween","Silicone","Human","")       
+ticklabelsx <- ticklocsx    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx,line=0.5,cex=1.5)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=3,cex=1.5) 
+title(xlab="Realism", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.8)
+
+text(1.15,3.3,'(b)',cex=3)
+
+a <- density(averageQdata[,1,2],cut=6)
+a$y <- 0.35*a$y/max(a$y)
+polygon(a$x,1.1+a$y,border=NA,col=addalpha(collist[1],0.5))
+
+a <- density(averageQdata[,2,2])
+a$y <- 0.35*a$y/max(a$y)
+polygon(a$x,2.1+a$y,border=NA,col=addalpha(collist[2],0.5))
+
+a <- density(averageQdata[,3,2])
+a$y <- 0.35*a$y/max(a$y)
+polygon(a$x,3.1+a$y,border=NA,col=addalpha(collist[3],0.5))
+
+xvals <- seq(-0.1,0.1,length=nrow(averageQdata))
+points(averageQdata[,1,2],1+xvals-0.2,pch=16,col=collist[1])
+points(averageQdata[,2,2],2+xvals-0.2,pch=15,col=collist[2])
+points(averageQdata[,3,2],3+xvals-0.2,pch=18,col=collist[3])
+
+for (cond in 1:3){
+  bs <- NULL
+  for (n in 1:nbootstraps){bs[n] <- mean(sample(averageQdata[,cond,2],replace=TRUE))}
+  ci <- quantile(bs,c(0.025,0.975))
+  arrows(mean(averageQdata[,cond,2]),cond,ci[1],cond,angle=90,length=0.1,lwd=3)
+  arrows(mean(averageQdata[,cond,2]),cond,ci[2],cond,angle=90,length=0.1,lwd=3)
+}
+
+points(mean(averageQdata[,1,2]),1,pch=21,cex=2,lwd=2,bg=collist[1])
+points(mean(averageQdata[,2,2]),2,pch=22,cex=2,lwd=2,bg=collist[2])
+points(mean(averageQdata[,3,2]),3,pch=23,cex=2,lwd=2,bg=collist[3])
+
+plotlims <- c(1,7,0.5,3.5)  
+ticklocsy <- c(0.5,1,2,3,3.5)    
+ticklocsx <- seq(1,7,1)    # locations of tick marks on y axis
+ticklabelsy <- c("","Halloween","Silicone","Human","")       
+ticklabelsx <- ticklocsx    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx,line=0.5,cex=1.5)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=3,cex=1.5) 
+title(xlab="Uncanniness", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.8)
+
+text(1.15,3.3,'(c)',cex=3)
+
+a <- density(averageQdata[,1,3],cut=6)
+a$y <- 0.35*a$y/max(a$y)
+polygon(a$x,1.1+a$y,border=NA,col=addalpha(collist[1],0.5))
+
+a <- density(averageQdata[,2,3])
+a$y <- 0.35*a$y/max(a$y)
+polygon(a$x,2.1+a$y,border=NA,col=addalpha(collist[2],0.5))
+
+a <- density(averageQdata[,3,3])
+a$y <- 0.35*a$y/max(a$y)
+polygon(a$x,3.1+a$y,border=NA,col=addalpha(collist[3],0.5))
+
+xvals <- seq(-0.1,0.1,length=nrow(averageQdata))
+points(averageQdata[,1,3],1+xvals-0.2,pch=16,col=collist[1])
+points(averageQdata[,2,3],2+xvals-0.2,pch=15,col=collist[2])
+points(averageQdata[,3,3],3+xvals-0.2,pch=18,col=collist[3])
+
+for (cond in 1:3){
+  bs <- NULL
+  for (n in 1:nbootstraps){bs[n] <- mean(sample(averageQdata[,cond,3],replace=TRUE))}
+  ci <- quantile(bs,c(0.025,0.975))
+  arrows(mean(averageQdata[,cond,3]),cond,ci[1],cond,angle=90,length=0.1,lwd=3)
+  arrows(mean(averageQdata[,cond,3]),cond,ci[2],cond,angle=90,length=0.1,lwd=3)
+}
+
+points(mean(averageQdata[,1,3]),1,pch=21,cex=2,lwd=2,bg=collist[1])
+points(mean(averageQdata[,2,3]),2,pch=22,cex=2,lwd=2,bg=collist[2])
+points(mean(averageQdata[,3,3]),3,pch=23,cex=2,lwd=2,bg=collist[3])
+
+plotlims <- c(0,5,0.5,3.5)  
+ticklocsy <- c(0.5,1,2,3,3.5)    
+ticklocsx <- seq(0,5,1)    # locations of tick marks on y axis
+ticklabelsy <- c("","Halloween","Silicone","Human","")       
+ticklabelsx <- ticklocsx    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx,line=0.5,cex=1.5)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=3,cex=1.5) 
+title(xlab="d prime", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.8)
+
+text(0.15,3.3,'(d)',cex=3)
+
+a <- density(subjdprime[,1],cut=6)
+a$y <- 0.35*a$y/max(a$y)
+polygon(a$x,1.1+a$y,border=NA,col=addalpha(collist[1],0.5))
+
+a <- density(subjdprime[,2])
+a$y <- 0.35*a$y/max(a$y)
+polygon(a$x,2.1+a$y,border=NA,col=addalpha(collist[2],0.5))
+
+a <- density(subjdprime[,3])
+a$y <- 0.35*a$y/max(a$y)
+polygon(a$x,3.1+a$y,border=NA,col=addalpha(collist[3],0.5))
+
+xvals <- seq(-0.1,0.1,length=nrow(subjdprime))
+points(subjdprime[,1],1+xvals-0.2,pch=16,col=collist[1])
+points(subjdprime[,2],2+xvals-0.2,pch=15,col=collist[2])
+points(subjdprime[,3],3+xvals-0.2,pch=18,col=collist[3])
+
+for (cond in 1:3){
+  bs <- NULL
+  for (n in 1:nbootstraps){bs[n] <- mean(sample(subjdprime[,cond],replace=TRUE))}
+  ci <- quantile(bs,c(0.025,0.975))
+  arrows(mean(subjdprime[,cond]),cond,ci[1],cond,angle=90,length=0.1,lwd=3)
+  arrows(mean(subjdprime[,cond]),cond,ci[2],cond,angle=90,length=0.1,lwd=3)
+}
+
+points(mean(subjdprime[,1]),1,pch=21,cex=2,lwd=2,bg=collist[1])
+points(mean(subjdprime[,2]),2,pch=22,cex=2,lwd=2,bg=collist[2])
+points(mean(subjdprime[,3]),3,pch=23,cex=2,lwd=2,bg=collist[3])
+
+dev.off()
+
+}
+
+```
+
 The results of Experiment 2 were similar to those of Experiment 1, despite using a quite different stimulus set involving images of humans wearing masks, rather than robots.
@@
 
+We subsequently obtained ratings from an independent sample of 20 participants using the same stimuli as in the main experiment.
+This time, we asked for explicit ratings of emotional expressiveness, realism, and uncanniness, as well as repeating the binary real face vs mask rating.
+Real faces were rated highest for emotional expressiveness (M=`r round(mean(averageQdata[,3,1]),digits=1)`) and realism (M=`r round(mean(averageQdata[,3,2]),digits=1)`), and lowest for uncanniness (M=`r round(mean(averageQdata[,3,3]),digits=1)`) (Figure \@ref(fig:maskratings)a-c).
+The realistic silicone masks were rated highest for uncanniness (M=`r round(mean(averageQdata[,2,3]),digits=1)`), however this was not dramatically higher than for the Halloween masks (M=`r round(mean(averageQdata[,1,3]),digits=1)`).
+Arguably making judgements of uncanniness is less appropriate for masks that are not intended to be realistic, though our data do qualitatively conform to the U-shaped function expected by the uncanny valley hypothesis.
+The pattern of d-prime scores (Figure \@ref(fig:maskratings)d) was similar to those obtained in the main experiment (Figure \@ref(fig:MasksData)b), with generally higher scores attributable to the unlimited inspection time permitted here.
+
+```{r maskratings, fig.cap="Additional ratings of mask images, completed by an independent sample (N=20) with unlimited inspection time.
+Images were rated on three dimensions using seven-point scales (panels a-c), and also judged as being either a real face or a mask, from which d-prime scores were calculated (panel d).", fig.align="center", out.width="70%", echo=FALSE}
+
+knitr::include_graphics('Figures/MaskRatings.pdf')
+
+```
+
 # Discussion
@@
 Perceptual judgements indicated that identification performance for uncanny valley stimuli was relatively poor, indicating confusion with real human images.
-The similarity in results across our two experiments is striking, and constitutes an internal conceptual replication of our main findings.
-
-Our early time window when pattern classification is above chance corresponds approximately to the P100 and N170 components of the ERP.
-Similar early components have also been investigated in other ERP studies on the uncanny valley effect [@Schindler2017; @Mustafa2016].
+The similarity in results across our two experiments is striking and constitutes an internal conceptual replication of our main findings.
+
+The early time window when pattern classification is above chance corresponds approximately to the P100 and N170 components of the ERP.
+Similar early components have also been investigated in other ERP studies on the uncanny valley effect [@Schindler2017; @Mustafa2016], and comparing human and robot faces [@Geiger2021].
 This time window is unlikely to be modulated substantially by top-down influences, so we attribute the early component to image-based differences between stimulus categories [@Coggan2016].
@@
 Our use of hyper-realistic silicone masks is novel in the context of the study of uncanny valley effects.
-Previous studies using these masks have demonstrated that they are difficult to distinguish from real faces [@Sanders2017], including in applied settings such as simulated passport control [@Robertson2020], and showing large individual differences [@Sanders2018].
+Previous studies using these masks have demonstrated that they are difficult to distinguish from real faces [@Sanders2017; @Sanders2019], including in applied settings such as simulated passport control [@Robertson2020; @Robertson2024], and show large individual differences [@Sanders2018].
 Image analysis indicates that good identification performance of silicone masks is typically based on attention to the region below the eyes [@Sanders2018], however it is plausible that many observers are not explicitly aware of the cues they use to perform this judgement.
@@
 
+More generally, the advantage of measuring neural responses to 'uncanny valley' stimuli is that, without requiring conscious awareness or behavioural responses, they can facilitate detection of near-human stimuli.
+These types of near-human stimuli are becoming increasingly common in impersonation and identity evasion cases [@Sanders2021].
+Simultaneously, we observe a growing market for reducing the uncanny valley effect for the benefit of android and robot integration.
+Exploring the potential of non-invasive brain recordings will benefit various applied fields as a result.
+
 # Conclusions
@@
 
-SF was funded by a YorRobots Venables internship. Also supported by BBSRC grant BB/V007580/1 awarded to DHB. ANY OTHER GRANTS TO ACKNOWLEDGE HERE?
+[**redacted for blind peer review**]
+<!-- SF was funded by a YorRobots Venables internship.
+JGS was funded by the Economic and Social Research Council (Studentship ES/J500215/1) and Prins Bernhard Cultuurfonds (grant E/30/30.13.0630/HVH/IE).
+Also supported by BBSRC grant BB/V007580/1 awarded to DHB.
+-->
 

### 2024-06-30 manuscript.tex
Incorporated co-author comments and questionnaire data. Anonymised for submission.

@@
 \setcounter{secnumdepth}{5}
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 for robots and hyper-realistic masks}
-\author{Shona Fitzpatrick\(^1\), Ailish K. Byrne\(^2\), Alex Headley\(^1\), Jet G. Sanders\(^3\),\\
-Helen Petrie\(^4\), Rob Jenkins\(^1\) \& Daniel H. Baker\(^{1,5}\)}
-\date{}
+\author{}
+\date{\vspace{-2.5em}}
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Department of Psychology, University of York, York, UK
-\item
-  School of Medicine, Keele University, Newcastle-under-Lyme, Staffordshire, UK
-\item
-  Department of Psychological and Behavioural Science, London School of Economics, London, UK
-\item
-  Department of Computer Science, University of York, York, UK
-\item
-  Corresponding author, email: daniel.baker@york.ac.uk
-\end{enumerate}
+{[}\textbf{Author information redacted for blind peer review}{]}
 
-\hypertarget{abstract}{%
-\section{Abstract}\label{abstract}}
+\section{Abstract}\label{abstract}
 
 Viewing artificial objects and images that are designed to appear human can elicit a sense of unease, referred to as the `uncanny valley' effect.
-Here we investigate neural correlates of the uncanny valley, using still images of androids (robots designed to look human), and hyper-realistic silicone masks, in two independent experiments.
-In both cases, human-like stimuli were harder to distinguish from real human faces than examples that were clearly not designed to mimic humans (mechanical robots, and Halloween masks).
+Here we investigate neural correlates of the uncanny valley, using still images of androids (robots designed to look human), and humans wearing hyper-realistic silicone masks, as well as still images of real humans, in two experiments.
+In both experiments, human-like stimuli were harder to distinguish from real human faces than stimuli that were clearly not designed to mimic humans but contain facial features (mechanical robots and Halloween masks).
 Stimulus evoked potentials did not show convincing differences between faces and either androids or realistic masks when using traditional univariate statistical tests.
@@
 The first time window was around 100-200ms post stimulus onset, and most likely corresponds to low-level image differences between conditions.
-The second time window was around 600ms post stimulus onset, and may reflect top-down processing, and perhaps correspond to the subjective sense of unease characteristic of the uncanny valley effect.
+The second time window was around 600ms post stimulus onset, and may reflect top-down processing, and may correspond to the subjective sense of unease characteristic of the uncanny valley effect.
 Objective neural components might be used in future to rapidly train generative artificial intelligence systems to produce more realistic images that are perceived as natural by human observers.
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\section{Introduction}\label{introduction}
 
-Many people report an aversion to entities that are superficially human-like, but on closer inspection are actually artificial.
-Examples include humanoid robots (androids), puppets, hyper-realistic masks, and computer-generated images or movies.
-The term `uncanny valley' (Mori, 1970; English translation in Mori et al., 2012) describes the idea that entities that are clearly human or clearly artificial do not evoke unease, whereas artificial entities that are human-like are disconcerting.
-Understanding these experiences is increasingly important as artificial entities become more integrated into our everyday lives, however at present relatively little is known about the neural underpinnings of the uncanny valley effect (for a recent review, see Vaitonytė et al., 2023).
+Many people report an aversion to entities that are superficially human-like, but on closer inspection turn out to be artificial.
+Examples include humanoid robots (androids), puppets, hyper-realistic masks (Sanders \& Jenkins, 2021), and computer-generated images or movies.
+The term `uncanny valley' (Mori, 1970; English translation in Mori et al., 2012) describes the idea that clearly human or clearly artificial entities do not evoke unease, whereas artificial entities that are human-like are disconcerting.
+Understanding these experiences is increasingly important as artificial entities become more integrated into our everyday lives.
+However at present relatively little is known about the neural underpinnings of the uncanny valley effect (for a recent review, see Vaitonytė et al., 2023).
 
@@
 For example, areas of the occipital lobe (Gauthier et al., 2000) and fusiform gyrus (Kanwisher et al., 1997) respond more to faces than non-face stimuli, and sections of extrastriate cortex are responsive to bodies (Downing et al., 2001).
-There are also event-related potential (ERP) signals associated with face and body stimuli, though their precise purpose is still debated (Thierry et al., 2007).
-It seems highly likely that `uncanny' images will activate these same processes, yet it is unclear whether the sense of unease they produce occurs at bottom-up sensory stages, or is modulated by more top-down cognitive factors.
+There are also event-related potential (ERP) signals associated with face and body stimuli, though their precise role is still debated (Hong et al., 2022; Thierry et al., 2007).
+It seems highly likely that `uncanny' images will activate these same processes, yet it is unclear whether the sense of unease they produce occurs at bottom-up sensory stages or is modulated by more top-down cognitive factors.
 
@@
 (2012) measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
-They found repetition suppression effects in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
+They found repetition suppression effects\footnote{Repetition suppression is a phenomenon in which the neural responses to repeated presentations of identical or similar stimuli is reduced relative to the response on the first presentation.} in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
 These effects were stronger than for movies of humans or mechanical robots performing the same actions.
-A more recent electroencephalography (EEG) study (Urgen et al., 2018) identified a difference in the N400 component between dynamic and static conditions using the same stimuli.
-Although this difference was strongest over frontal electrodes, source reconstruction of the N400 itself suggested a left-lateralised source in temporo-parietal cortex, consistent with the fMRI results (Saygin et al., 2012).
+A more recent electroencephalography (EEG) study (Urgen et al., 2018) identified a difference in the N400 component\footnote{The N400 is an electromagnetic brain potential obtained 400ms after stimulus onset, typically over centro-parietal electrodes.
+It has been proposed to reflect the extent to which the stimulus presented was surprising or unexpected.} between dynamic and static conditions using the same stimuli.
+Although this difference was strongest over frontal electrodes, source reconstruction of the N400 itself suggested a left-lateralised source in the temporo-parietal cortex, consistent with the fMRI results (Saygin et al., 2012).
 The authors interpret both of these findings as being due to the discrepancy between the human-like appearance and the clearly non-biological motion of the robot.
 
-Our aim here was to further investigate neural correlates of the uncanny valley effect.
-We achieve this through two EEG experiments, in which we measure neural responses to static images.
-In the first experiment, the stimuli were humans, machine-like robots, and human-like robots (see Figure \ref{fig:stimexamples}a).
-In the second experiment we aimed to generalise the finding by using images of people wearing no masks, wearing obvious masks (e.g.~carnival or Halloween masks), and wearing hyper-realistic silicone masks (Sanders et al., 2017) (see Figure \ref{fig:stimexamples}b).
+Our aim was to further investigate neural correlates of the uncanny valley effect.
+We achieved this through two EEG experiments, in which we measured neural responses to static images.
+In the first experiment, the stimuli were still images of humans, machine-like robots, and human-like robots (see Figure \ref{fig:stimexamples}a).
+In the second experiment we aimed to generalise the finding by using images of people wearing no masks, wearing obvious masks (e.g.~Halloween masks), and wearing hyper-realistic silicone masks (Sanders et al., 2017) (see Figure \ref{fig:stimexamples}b).
 Rather than focus on specific ERP components, we use a multivariate pattern classification approach to identify time windows in which information in the EEG signal can be used to distinguish between pairs of conditions.
@@
 
-\hypertarget{materials-methods}{%
-\section{Materials \& Methods}\label{materials-methods}}
+\section{Materials \& Methods}\label{materials-methods}
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\subsection{Participants}\label{participants}
 
-A total of 29 participants completed Experiment 1 (12 male, 17 female), and 30 participants completed Experiment 2 (7 male, 23 female).
+A total of 29 participants completed Experiment 1 (12 male, 17 female), and 30 different participants completed Experiment 2 (7 male, 23 female).
 None of the participants had previously taken part in a study using these stimuli, and all were naïve to the hypotheses and wore their normal optical correction if required.
-Written informed consent was collected before each experiment began, and all procedures were approved by the Ethics committee of the Department of Psychology at the University of York.
+Written informed consent was collected before each experiment began, and all procedures were approved by the Ethics committee of {[}\textbf{redacted for blind peer review}{]}.
 
-\hypertarget{apparatus-stimuli}{%
-\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}
+\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}
 
@@
 Images all showed the head and shoulders of the subject, had white backgrounds, and were sourced from the internet.
-In Experiment 2, the stimulus set consisted of a total of 296 images, comprising real faces (148 images), people wearing silicone masks (74 images), and people wearing obvious masks of the sort typically worn for carnivals and Halloween celebrations (74 images).
+In Experiment 2, the stimulus set (first described by Sanders et al.
+(2019), but here including additional images) consisted of a total of 296 images, comprising real faces (148 images), people wearing silicone masks (74 images), and people wearing obvious masks of the sort typically worn for carnivals and Halloween celebrations (74 images).
 The backgrounds of these images were more heterogeneous, and showed the natural surroundings of the subject.
@@
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+\subsection{Procedure}\label{procedure}
 
-\hypertarget{experiment-1-robots}{%
-\subsubsection{Experiment 1: robots}\label{experiment-1-robots}}
+\subsubsection{Experiment 1: Robots}\label{experiment-1-robots}
 
@@
 
-\hypertarget{experiment-2-hyper-realistic-masks}{%
-\subsubsection{Experiment 2: hyper-realistic masks}\label{experiment-2-hyper-realistic-masks}}
+After the EEG experiment, participants also completed a series of questionnaires using the Qualtrics platform.
+These involved rating their perception of a subset of the stimuli (8 from each category), using items from the Godspeed questionnaire (Bartneck et al., 2009).
+Inspection time was unlimited.
+Participants also provided demographic information (age, gender) and completed the GAToRS (Koverola et al., 2022) and AQ (Baron-Cohen et al., 2001) questionnaires, however the results of these additional questionnaires are not presented here.
+
+\subsubsection{Experiment 2: Hyper-realistic masks}\label{experiment-2-hyper-realistic-masks}
 
@@
 In the third block, stimuli doubled in size again, and subtended \(22\times30\) degrees.
-The rationale for the size manipulation was to investigate whether increasing levels of detail made the silicone masks more identifiable (Sanders et al., 2017), however as that is not the main focus of the current paper we collapse results across size conditions.
+The rationale for the size manipulation was to investigate whether increasing levels of detail made the silicone masks more identifiable (Sanders et al., 2017, 2019).
+However as that is not the main focus of the current paper, and our preliminary analyses indicated no differences between size conditions, we collapse results across size conditions.
 Stimuli were presented for 250ms, and participants indicated whether they thought each image contained a real face or a mask, using a two-button trackball.
@@
 
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
+An independent group of 20 participants also completed an online questionnaire in which they rated the images along various dimensions.
+The participants repeated the real face vs mask judgement from the main experiment, and were additionally asked to rate emotional expressiveness, realism, and uncanniness for each image using a 7-point Likert scale.
+Inspection time was unlimited for these judgments.
 
-We analysed response data by calculating d-prime (\(d'\)) scores for each condition, derived from the hit rate and false alarm rate (Macmillan and Creelman, 2005).
+\subsection{Data analysis}\label{data-analysis}
+
+We analysed response data by calculating d-prime (\(d'\)) scores for each condition, derived from the hit rate and false alarm rate (Macmillan \& Creelman, 2005).
 For the human conditions, the hit rate was the proportion of human images correctly identified as human, and the false alarm rate was the proportion of robot or mask images that were incorrectly judged as being human.
@@
 
-EEG signals were recorded during each block, and saved to disc for subsequent offline analysis.
-We used components of the EEGlab toolbox (Delorme and Makeig, 2004) to import the data into Matlab and collate data across blocks.
+EEG signals were recorded during each block and saved to disc for subsequent offline analysis.
+We used components of the EEGlab toolbox (Delorme \& Makeig, 2004) to import the data into Matlab and collate data across blocks.
 We then used Brainstorm (Tadel et al., 2011) to filter the data using a bandpass filter (0.5 to 30Hz), epoch by condition, and subtract a pre-trial baseline (the mean voltage for the 200ms before stimulus onset).
@@
 
-Multivariate pattern analysis was conducted by training a linear support vector machine algorithm (LibSVM; Chang and Lin (2011)) to discriminate between patterns of activity across electrodes at a specific time point.
+Multivariate pattern analysis was conducted by training a linear support vector machine algorithm (LibSVM, Chang \& Lin, 2011) to discriminate between patterns of activity across electrodes at a specific time point.
 The patterns came from the human face condition and one of the other conditions, for a single participant.
-Four examples of each pattern were calculated by averaging over random subsets of 20\% of the available trials from a given condition, and using these to train the classifier.
-The accuracy of the classifier was tested on the averaged remaining trials (that were not used in training) for each condition.
+Four examples of each pattern were calculated by averaging over random subsets of 20\% of the available trials from a given condition, and these were used to train the classifier.
+The accuracy of the classifier was tested on the remaining trials (that were not used in training) for each condition.
 This process was repeated 1000 times with different trial permutations to obtain an average accuracy, where chance performance is at 50\% correct.
-The analysis was carried out at all time points, and also for all participants.
+The analysis was carried out at all time points, and for each participant separately.
 We then averaged classifier accuracy across participants, and calculated one sample Bayesian t-tests comparing to chance performance at each time point as described above.
 
-\hypertarget{data-and-code-availability}{%
-\subsection{Data and code availability}\label{data-and-code-availability}}
+\subsection{Data and code availability}\label{data-and-code-availability}
 
-Raw data, processed data, and analysis scripts are freely available through the project repository at: \url{https://doi.org/10.17605/OSF.IO/5NZ2H}
+Raw data, processed data, and analysis scripts are freely available through the project repository at: {[}\textbf{redacted for blind peer review}{]}
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\section{Results}\label{results}
 
-\hypertarget{experiment-1}{%
-\subsection{Experiment 1}\label{experiment-1}}
+\subsection{Experiment 1}\label{experiment-1}
 
@@
 
-EEG activity showed a clear visually evoked potential over posterior electrode sites (see Figure \ref{fig:RobotsData}c), with typical components found in response to visual stimuli (the P100, N170 and P200 are indicated in the figure).
+EEG activity showed a clear visually evoked potential over posterior electrode sites (see Figure \ref{fig:RobotsData}c), with typical components found in response to visual stimuli pooled across all conditions (the P100, N170 and P200 are indicated in the figure).
 Pairwise comparisons of conditions are shown in Figure \ref{fig:RobotsMVPA}a,b.
-In general there is a tendency for the ERP response to human faces to diverge slightly from the other two conditions, however the evidence for a convincing difference was not compelling.
+In general there is a tendency for the ERP response to human faces to diverge slightly from the other two conditions (Geiger \& Balas, 2021), however the evidence for this divergence was not compelling.
 Bayes factors exceeded 3 for only a small number of time points around 300-400ms in the comparison between human and robot images (see yellow bars at y = -8 in Figure \ref{fig:RobotsMVPA}a), but these differences were small considering the variance in the data.
@@
 
-\hypertarget{experiment-2}{%
-\subsection{Experiment 2}\label{experiment-2}}
+Finally, we analysed the rating data from a set of 10 questionnaire items for 8 stimuli from each category.
+The results are summarised in Figure \ref{fig:robotratings}, and in general show differences between stimulus categories along most dimensions.
+Of particular note, the U-shaped function predicted by the uncanny valley effect was apparent for ratings along the Dislike-Like (Figure \ref{fig:robotratings}d), Unfriendly-Friendly (Figure \ref{fig:robotratings}e), and Anxious-Relaxed (Figure \ref{fig:robotratings}i) dimensions.
+These are all dimensions with emotional valence, indicating support for the `uncanniness' of our android stimuli.
+However we note that the android and robot categories were typically rated as being more similar to each other than to the real human faces.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{Figures/RobotRatings}
+
+}
+
+\caption{Ratings of stimuli using items from the Godspeed questionnaire.
+Each rating was on a Likert scale from 1-5, and was the average of ratings from 8 stimulus examples.
+Dots show individual participant scores, with the larger symbols indicating the mean and 95\% bootstrapped confidence intervals.}\label{fig:robotratings}
+\end{figure}
+
+\subsection{Experiment 2}\label{experiment-2}
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+We subsequently obtained ratings from an independent sample of 20 participants using the same stimuli as in the main experiment.
+This time, we asked for explicit ratings of emotional expressiveness, realism, and uncanniness, as well as repeating the binary real face vs mask rating.
+Real faces were rated highest for emotional expressiveness (M=3.9) and realism (M=5.9), and lowest for uncanniness (M=2.7) (Figure \ref{fig:maskratings}a-c).
+The realistic silicone masks were rated highest for uncanniness (M=4.5), however this was not dramatically higher than for the Halloween masks (M=4.3).
+Arguably making judgements of uncanniness is less appropriate for masks that are not intended to be realistic, though our data do qualitatively conform to the U-shaped function expected by the uncanny valley hypothesis.
+The pattern of d-prime scores (Figure \ref{fig:maskratings}d) was similar to those obtained in the main experiment (Figure \ref{fig:MasksData}b), with generally higher scores attributable to the unlimited inspection time permitted here.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.7\linewidth]{Figures/MaskRatings}
+
+}
+
+\caption{Additional ratings of mask images, completed by an independent sample (N=20) with unlimited inspection time.
+Images were rated on three dimensions using seven-point scales (panels a-c), and also judged as being either a real face or a mask, from which d-prime scores were calculated (panel d).}\label{fig:maskratings}
+\end{figure}
+
+\section{Discussion}\label{discussion}
 
@@
 Perceptual judgements indicated that identification performance for uncanny valley stimuli was relatively poor, indicating confusion with real human images.
-The similarity in results across our two experiments is striking, and constitutes an internal conceptual replication of our main findings.
+The similarity in results across our two experiments is striking and constitutes an internal conceptual replication of our main findings.
 
-Our early time window when pattern classification is above chance corresponds approximately to the P100 and N170 components of the ERP.
-Similar early components have also been investigated in other ERP studies on the uncanny valley effect (Mustafa and Magnor, 2016; Schindler et al., 2017).
+The early time window when pattern classification is above chance corresponds approximately to the P100 and N170 components of the ERP.
+Similar early components have also been investigated in other ERP studies on the uncanny valley effect (Mustafa \& Magnor, 2016; Schindler et al., 2017), and comparing human and robot faces (Geiger \& Balas, 2021).
 This time window is unlikely to be modulated substantially by top-down influences, so we attribute the early component to image-based differences between stimulus categories (Coggan et al., 2016).
@@
 Our use of hyper-realistic silicone masks is novel in the context of the study of uncanny valley effects.
-Previous studies using these masks have demonstrated that they are difficult to distinguish from real faces (Sanders et al., 2017), including in applied settings such as simulated passport control (Robertson et al., 2020), and showing large individual differences (Sanders and Jenkins, 2018).
-Image analysis indicates that good identification performance of silicone masks is typically based on attention to the region below the eyes (Sanders and Jenkins, 2018), however it is plausible that many observers are not explicitly aware of the cues they use to perform this judgement.
+Previous studies using these masks have demonstrated that they are difficult to distinguish from real faces (Sanders et al., 2017, 2019), including in applied settings such as simulated passport control (Robertson et al., 2020, 2024), and show large individual differences (Sanders \& Jenkins, 2018).
+Image analysis indicates that good identification performance of silicone masks is typically based on attention to the region below the eyes (Sanders \& Jenkins, 2018), however it is plausible that many observers are not explicitly aware of the cues they use to perform this judgement.
 This might contribute to both the early and late components identified in this study, and presumably also to the subjective sensation of `uncanniness' that is characteristic of the phenomenon.
@@
 
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
+More generally, the advantage of measuring neural responses to `uncanny valley' stimuli is that, without requiring conscious awareness or behavioural responses, they can facilitate detection of near-human stimuli.
+These types of near-human stimuli are becoming increasingly common in impersonation and identity evasion cases (Sanders \& Jenkins, 2021).
+Simultaneously, we observe a growing market for reducing the uncanny valley effect for the benefit of android and robot integration.
+Exploring the potential of non-invasive brain recordings will benefit various applied fields as a result.
+
+\section{Conclusions}\label{conclusions}
 
@@
 
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
+\section{Acknowledgements}\label{acknowledgements}
 
-SF was funded by a YorRobots Venables internship. Also supported by BBSRC grant BB/V007580/1 awarded to DHB. ANY OTHER GRANTS TO ACKNOWLEDGE HERE?
+{[}\textbf{redacted for blind peer review}{]}
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
+\section*{References}\label{references}
 \addcontentsline{toc}{section}{References}
 
-\hypertarget{refs}{}
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Chang2011}{}}%
-Chang C-C, Lin C-J. 2011. {LIBSVM} : A library for support vector machines. \emph{ACM Transactions on Intelligent Systems and Technology} \textbf{2(27)}:1--27.
+\bibitem[\citeproctext]{ref-Baron-Cohen2001}
+Baron-Cohen, S., Wheelwright, S., Skinner, R., Martin, J., \& Clubley, E.
+(2001).
+The autism-spectrum quotient (AQ): Evidence from asperger syndrome/high-functioning autism, males and females, scientists and mathematicians.
+\emph{J Autism Dev Disord}, \emph{31}(1), 5--17.
+\url{https://doi.org/10.1023/a:1005653411471}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Cheetham2015}{}}%
-Cheetham M, Wu L, Pauli P, Jancke L.
-2015.
+\bibitem[\citeproctext]{ref-Bartneck2009}
+Bartneck, C., Kulić, D., Croft, E., \& Zoghbi, S.
+(2009).
+Measurement instruments for the anthropomorphism, animacy, likeability, perceived intelligence, and perceived safety of robots.
+\emph{International Journal of Social Robotics}, \emph{1}(1), 71--81.
+\url{https://doi.org/10.1007/s12369-008-0001-3}
+
+\bibitem[\citeproctext]{ref-Chang2011}
+Chang, C.-C., \& Lin, C.-J. (2011). {LIBSVM} : A library for support vector machines. \emph{ACM Transactions on Intelligent Systems and Technology}, \emph{2(27)}, 1--27.
+
+\bibitem[\citeproctext]{ref-Cheetham2015}
+Cheetham, M., Wu, L., Pauli, P., \& Jancke, L.
+(2015).
 Arousal, valence, and the uncanny valley: Psychophysiological and self-report findings.
-\emph{Front Psychol} \textbf{6}:981.
-doi:\href{https://doi.org/10.3389/fpsyg.2015.00981}{10.3389/fpsyg.2015.00981}
+\emph{Front Psychol}, \emph{6}, 981.
+\url{https://doi.org/10.3389/fpsyg.2015.00981}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Coggan2016}{}}%
-Coggan DD, Baker DH, Andrews TJ.
-2016.
+\bibitem[\citeproctext]{ref-Coggan2016}
+Coggan, D.
+D., Baker, D.
+H., \& Andrews, T.
+J.
+(2016).
 The role of visual and semantic properties in the emergence of category-specific patterns of neural response in the human brain.
-\emph{eNeuro} \textbf{3}.
-doi:\href{https://doi.org/10.1523/ENEURO.0158-16.2016}{10.1523/ENEURO.0158-16.2016}
+\emph{eNeuro}, \emph{3}(4).
+\url{https://doi.org/10.1523/ENEURO.0158-16.2016}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Delorme2004}{}}%
-Delorme A, Makeig S.
-2004.
+\bibitem[\citeproctext]{ref-Delorme2004}
+Delorme, A., \& Makeig, S.
+(2004).
 {EEGLAB}: An open source toolbox for analysis of single-trial {EEG} dynamics including independent component analysis.
-\emph{J Neurosci Methods} \textbf{134}:9--21.
-doi:\href{https://doi.org/10.1016/j.jneumeth.2003.10.009}{10.1016/j.jneumeth.2003.10.009}
+\emph{J Neurosci Methods}, \emph{134}(1), 9--21.
+\url{https://doi.org/10.1016/j.jneumeth.2003.10.009}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Downing2001}{}}%
-Downing PE, Jiang Y, Shuman M, Kanwisher N.
-2001.
+\bibitem[\citeproctext]{ref-Downing2001}
+Downing, P.
+E., Jiang, Y., Shuman, M., \& Kanwisher, N.
+(2001).
 A cortical area selective for visual processing of the human body.
-\emph{Science} \textbf{293}:2470--3.
-doi:\href{https://doi.org/10.1126/science.1063414}{10.1126/science.1063414}
+\emph{Science}, \emph{293}(5539), 2470--2473.
+\url{https://doi.org/10.1126/science.1063414}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gauthier2000}{}}%
-Gauthier I, Tarr MJ, Moylan J, Skudlarski P, Gore JC, Anderson AW.
-2000.
+\bibitem[\citeproctext]{ref-Gauthier2000}
+Gauthier, I., Tarr, M.
+J., Moylan, J., Skudlarski, P., Gore, J.
+C., \& Anderson, A.
+W.
+(2000).
 The fusiform "face area" is part of a network that processes faces at the individual level.
-\emph{J Cogn Neurosci} \textbf{12}:495--504.
-doi:\href{https://doi.org/10.1162/089892900562165}{10.1162/089892900562165}
+\emph{J Cogn Neurosci}, \emph{12}(3), 495--504.
+\url{https://doi.org/10.1162/089892900562165}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Hu2020}{}}%
-Hu Y, Baragchizadeh A, O'Toole AJ.
-2020.
+\bibitem[\citeproctext]{ref-Geiger2021}
+Geiger, A.
+R., \& Balas, B.
+(2021).
+Robot faces elicit responses intermediate to human faces and objects at face-sensitive ERP components.
+\emph{Sci Rep}, \emph{11}(1), 17890.
+\url{https://doi.org/10.1038/s41598-021-97527-6}
+
+\bibitem[\citeproctext]{ref-Hong2022}
+Hong, Y., Mayes, M.
+S., Munasinghe, A.
+P., \& Ratner, K.
+G.
+(2022).
+Scrutinizing whether mere group membership influences the N170 response to faces: Results from two preregistered event-related potential studies.
+\emph{J Cogn Neurosci}, \emph{34}(11), 1999--2015.
+\url{https://doi.org/10.1162/jocn_a_01887}
+
+\bibitem[\citeproctext]{ref-Hu2020}
+Hu, Y., Baragchizadeh, A., \& O'Toole, A.
+J.
+(2020).
 Integrating faces and bodies: Psychological and neural perspectives on whole person perception.
-\emph{Neurosci Biobehav Rev} \textbf{112}:472--486.
-doi:\href{https://doi.org/10.1016/j.neubiorev.2020.02.021}{10.1016/j.neubiorev.2020.02.021}
+\emph{Neurosci Biobehav Rev}, \emph{112}, 472--486.
+\url{https://doi.org/10.1016/j.neubiorev.2020.02.021}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Jeffreys1961}{}}%
-Jeffreys H. 1961. Theory of probability, 3rd ed. Oxford University Press, Clarendon Press.
+\bibitem[\citeproctext]{ref-Jeffreys1961}
+Jeffreys, H. (1961). \emph{Theory of probability} (3rd ed.). Oxford University Press, Clarendon Press.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kanwisher1997}{}}%
-Kanwisher N, McDermott J, Chun MM.
-1997.
+\bibitem[\citeproctext]{ref-Kanwisher1997}
+Kanwisher, N., McDermott, J., \& Chun, M.
+M.
+(1997).
 The fusiform face area: A module in human extrastriate cortex specialized for face perception.
-\emph{J Neurosci} \textbf{17}:4302--11.
-doi:\href{https://doi.org/10.1523/JNEUROSCI.17-11-04302.1997}{10.1523/JNEUROSCI.17-11-04302.1997}
+\emph{J Neurosci}, \emph{17}(11), 4302--4311.
+\url{https://doi.org/10.1523/JNEUROSCI.17-11-04302.1997}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Macmillan2005}{}}%
-Macmillan NA, Creelman CD. 2005. Detection theory: A user's guide. Psychology Press.
+\bibitem[\citeproctext]{ref-Koverola2022}
+Koverola, M., Kunnari, A., Sundvall, J., \& Laakasuo, M.
+(2022).
+General attitudes towards robots scale (GAToRS): A new instrument for social surveys.
+\emph{International Journal of Social Robotics}, \emph{14}(7), 1559--1581.
+\url{https://doi.org/10.1007/s12369-022-00880-3}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Mori1970}{}}%
-Mori M. 1970. The uncanny valley. \emph{Energy} \textbf{7}:33--35.
+\bibitem[\citeproctext]{ref-Macmillan2005}
+Macmillan, N. A., \& Creelman, C. D. (2005). \emph{Detection theory: A user's guide}. Psychology Press.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Mori2012}{}}%
-Mori M, MacDorman KF, Kageki N.
-2012.
+\bibitem[\citeproctext]{ref-Mori1970}
+Mori, M. (1970). The uncanny valley. \emph{Energy}, \emph{7}, 33--35.
+
+\bibitem[\citeproctext]{ref-Mori2012}
+Mori, M., MacDorman, K.
+F., \& Kageki, N.
+(2012).
 The uncanny valley {[}from the field{]}.
-\emph{IEEE Robotics \& Automation Magazine} \textbf{19}:98--100.
-doi:\href{https://doi.org/10.1109/MRA.2012.2192811}{10.1109/MRA.2012.2192811}
+\emph{IEEE Robotics \& Automation Magazine}, \emph{19}(2), 98--100.
+\url{https://doi.org/10.1109/MRA.2012.2192811}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Mustafa2017}{}}%
-Mustafa M, Guthe S, Tauscher J-P, Goesele M, Magnor M.
-2017.
-How human am i?: EEG-based evaluation of virtual charactersProceedings of the 2017 CHI Conference on Human Factors in Computing Systems, CHI 17.
-ACM.
-doi:\href{https://doi.org/10.1145/3025453.3026043}{10.1145/3025453.3026043}
+\bibitem[\citeproctext]{ref-Mustafa2017}
+Mustafa, M., Guthe, S., Tauscher, J.-P., Goesele, M., \& Magnor, M.
+(2017, May).
+How human am i?: EEG-based evaluation of virtual characters.
+\emph{Proceedings of the 2017 CHI Conference on Human Factors in Computing Systems}.
+\url{https://doi.org/10.1145/3025453.3026043}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Mustafa2016}{}}%
-Mustafa M, Magnor M.
-2016.
-EEG based analysis of the perception of computer-generated faces.Proceedings of the 13th European Conference on Visual Media Production (CVMP 2016), CVMP 2016.
-ACM.
-doi:\href{https://doi.org/10.1145/2998559.2998563}{10.1145/2998559.2998563}
+\bibitem[\citeproctext]{ref-Mustafa2016}
+Mustafa, M., \& Magnor, M.
+(2016, December).
+EEG based analysis of the perception of computer-generated faces.
+\emph{Proceedings of the 13th European Conference on Visual Media Production (CVMP 2016)}.
+\url{https://doi.org/10.1145/2998559.2998563}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Robertson2020}{}}%
-Robertson DJ, Sanders JG, Towler A, Kramer RSS, Spowage J, Byrne A, Burton AM, Jenkins R.
-2020.
+\bibitem[\citeproctext]{ref-Robertson2024}
+Robertson, D.
+J., Davis, J.
+P., Sanders, J.
+G., \& Towler, A.
+(2024).
+The super-recogniser advantage extends to the detection of hyper-realistic face masks.
+\emph{In Press}.
+\url{https://doi.org/10.31234/osf.io/u2kja}
+
+\bibitem[\citeproctext]{ref-Robertson2020}
+Robertson, D.
+J., Sanders, J.
+G., Towler, A., Kramer, R.
+S.
+S., Spowage, J., Byrne, A., Burton, A.
+M., \& Jenkins, R.
+(2020).
 Hyper-realistic face masks in a live passport-checking task.
-\emph{Perception} \textbf{49}:298--309.
-doi:\href{https://doi.org/10.1177/0301006620904614}{10.1177/0301006620904614}
+\emph{Perception}, \emph{49}(3), 298--309.
+\url{https://doi.org/10.1177/0301006620904614}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Rouder2009}{}}%
-Rouder JN, Speckman PL, Sun D, Morey RD, Iverson G.
-2009.
+\bibitem[\citeproctext]{ref-Rouder2009}
+Rouder, J.
+N., Speckman, P.
+L., Sun, D., Morey, R.
+D., \& Iverson, G.
+(2009).
 Bayesian t tests for accepting and rejecting the null hypothesis.
-\emph{Psychon Bull Rev} \textbf{16}:225--37.
-doi:\href{https://doi.org/10.3758/PBR.16.2.225}{10.3758/PBR.16.2.225}
+\emph{Psychon Bull Rev}, \emph{16}(2), 225--237.
+\url{https://doi.org/10.3758/PBR.16.2.225}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Sanders2018}{}}%
-Sanders JG, Jenkins R.
-2018.
-Individual differences in hyper-realistic mask detection.
-\emph{Cogn Res Princ Implic} \textbf{3}:24.
-doi:\href{https://doi.org/10.1186/s41235-018-0118-3}{10.1186/s41235-018-0118-3}
+\bibitem[\citeproctext]{ref-Sanders2018}
+Sanders, J. G., \& Jenkins, R. (2018). Individual differences in hyper-realistic mask detection. \emph{Cogn Res Princ Implic}, \emph{3}, 24. \url{https://doi.org/10.1186/s41235-018-0118-3}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Sanders2017}{}}%
-Sanders JG, Ueda Y, Minemoto K, Noyes E, Yoshikawa S, Jenkins R.
-2017.
+\bibitem[\citeproctext]{ref-Sanders2021}
+Sanders, J.
+G., \& Jenkins, R.
+(2021).
+Realistic masks in the real world.
+In M.
+Bindemann (Ed.), \emph{{Forensic Face Matching: Research and Practice}}.
+Oxford University Press.
+\url{https://doi.org/10.1093/oso/9780198837749.003.0010}
+
+\bibitem[\citeproctext]{ref-Sanders2017}
+Sanders, J.
+G., Ueda, Y., Minemoto, K., Noyes, E., Yoshikawa, S., \& Jenkins, R.
+(2017).
 Hyper-realistic face masks: A new challenge in person identification.
-\emph{Cognitive Research: Principles and Implications} \textbf{2}.
-doi:\href{https://doi.org/10.1186/s41235-017-0079-y}{10.1186/s41235-017-0079-y}
+\emph{Cognitive Research: Principles and Implications}, \emph{2}(1).
+\url{https://doi.org/10.1186/s41235-017-0079-y}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Saygin2012}{}}%
-Saygin AP, Chaminade T, Ishiguro H, Driver J, Frith C.
-2012.
+\bibitem[\citeproctext]{ref-Sanders2019}
+Sanders, J.
+G., Ueda, Y., Yoshikawa, S., \& Jenkins, R.
+(2019).
+More human than human: A turing test for photographed faces.
+\emph{Cogn Res Princ Implic}, \emph{4}(1), 43.
+\url{https://doi.org/10.1186/s41235-019-0197-9}
+
+\bibitem[\citeproctext]{ref-Saygin2012}
+Saygin, A.
+P., Chaminade, T., Ishiguro, H., Driver, J., \& Frith, C.
+(2012).
 The thing that should not be: Predictive coding and the uncanny valley in perceiving human and humanoid robot actions.
-\emph{Soc Cogn Affect Neurosci} \textbf{7}:413--22.
-doi:\href{https://doi.org/10.1093/scan/nsr025}{10.1093/scan/nsr025}
+\emph{Soc Cogn Affect Neurosci}, \emph{7}(4), 413--422.
+\url{https://doi.org/10.1093/scan/nsr025}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Schindler2017}{}}%
-Schindler S, Zell E, Botsch M, Kissler J.
-2017.
+\bibitem[\citeproctext]{ref-Schindler2017}
+Schindler, S., Zell, E., Botsch, M., \& Kissler, J.
+(2017).
 Differential effects of face-realism and emotion on event-related brain potentials and their implications for the uncanny valley theory.
-\emph{Sci Rep} \textbf{7}:45003.
-doi:\href{https://doi.org/10.1038/srep45003}{10.1038/srep45003}
+\emph{Sci Rep}, \emph{7}, 45003.
+\url{https://doi.org/10.1038/srep45003}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Tadel2011}{}}%
-Tadel F, Baillet S, Mosher JC, Pantazis D, Leahy RM.
-2011.
+\bibitem[\citeproctext]{ref-Tadel2011}
+Tadel, F., Baillet, S., Mosher, J.
+C., Pantazis, D., \& Leahy, R.
+M.
+(2011).
 Brainstorm: A user-friendly application for MEG/EEG analysis.
-\emph{Comput Intell Neurosci} \textbf{2011}:879716.
-doi:\href{https://doi.org/10.1155/2011/879716}{10.1155/2011/879716}
+\emph{Comput Intell Neurosci}, \emph{2011}, 879716.
+\url{https://doi.org/10.1155/2011/879716}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Thierry2007}{}}%
-Thierry G, Martin CD, Downing P, Pegna AJ.
-2007.
+\bibitem[\citeproctext]{ref-Thierry2007}
+Thierry, G., Martin, C.
+D., Downing, P., \& Pegna, A.
+J.
+(2007).
 Controlling for interstimulus perceptual variance abolishes N170 face selectivity.
-\emph{Nat Neurosci} \textbf{10}:505--11.
-doi:\href{https://doi.org/10.1038/nn1864}{10.1038/nn1864}
+\emph{Nat Neurosci}, \emph{10}(4), 505--511.
+\url{https://doi.org/10.1038/nn1864}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Urgen2018}{}}%
-Urgen BA, Kutas M, Saygin AP.
-2018.
+\bibitem[\citeproctext]{ref-Urgen2018}
+Urgen, B.
+A., Kutas, M., \& Saygin, A.
+P.
+(2018).
 Uncanny valley as a window into predictive processing in the social brain.
-\emph{Neuropsychologia} \textbf{114}:181--185.
-doi:\href{https://doi.org/10.1016/j.neuropsychologia.2018.04.027}{10.1016/j.neuropsychologia.2018.04.027}
+\emph{Neuropsychologia}, \emph{114}, 181--185.
+\url{https://doi.org/10.1016/j.neuropsychologia.2018.04.027}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Vaitonyte2023}{}}%
-Vaitonytė J, Alimardani M, Louwerse MM.
-2023.
+\bibitem[\citeproctext]{ref-Vaitonyte2023}
+Vaitonytė, J., Alimardani, M., \& Louwerse, M.
+M.
+(2023).
 Scoping review of the neural evidence on the uncanny valley.
-\emph{Computers in Human Behavior Reports} \textbf{9}:100263.
-doi:\url{https://doi.org/10.1016/j.chbr.2022.100263}
+\emph{Computers in Human Behavior Reports}, \emph{9}, 100263.
+https://doi.org/\url{https://doi.org/10.1016/j.chbr.2022.100263}
 

### 2024-07-01 manuscript.Rmd
Finished implementing co-author comments

@@
 One previous study by @Saygin2012 measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
-They found repetition suppression effects^[Repetition suppression is a phenomenon in which the neural responses to repeated presentations of identical or similar stimuli is reduced relative to the response on the first presentation.] in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
+They found repetition suppression effects^[Repetition suppression is a phenomenon in which the neural response to repeated presentations of identical or similar stimuli is reduced relative to the response on the first presentation.] in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
 These effects were stronger than for movies of humans or mechanical robots performing the same actions.
@@
 EEG data were collected using a 64-channel Waveguard cap and an ANT Neuroscan system, sampling at 1kHz.
+The ground electrode was located at position $AFz$, and all signals were referenced to the whole head average.
 Low latency digital triggers were sent between the display and the EEG amplifier using an 8-bit parallel cable.
@@
 Panel (a) shows d-prime scores for identifying images of human (blue), android (green) and robot (red) faces.
-Small points show individual participants, and the larger symbols with error bars indicate the group mean and bootstrapped 95 percent confidence intervals.
+Small points show individual participants, and the larger symbols with error bars indicate the group mean and bootstrapped 95\\% confidence intervals.
 Panel (b) plots reaction times in the same format (note the logarithmic x-axis).
 Panel (c) shows the grand mean ERP across all participants and conditions, pooled across electrodes P6, P8, PO6 and PO8 (see inset).
-The shaded region around the curve illustrates the 95 percent confidence interval, and the grey rectangle at the foot indicates the stimulus duration.", fig.align="center", echo=FALSE}
+The shaded region around the curve illustrates the 95\\% confidence interval, and the grey rectangle at the foot indicates the stimulus duration.", fig.align="center", echo=FALSE}
 
@@
 Panels (c) and (d) show multivariate pattern classification accuracy for the same comparisons.
-Points at y = -8 and y = 25 indicate Bayes factor scores for comparisons between ERPs (a,b) and comparing classification accuracy to chance (50 percent correct; c,d).", fig.align="center", echo=FALSE}
+Points at y = -8 and y = 25 indicate Bayes factor scores for comparisons between ERPs (a,b) and comparing classification accuracy to chance (50\\% correct; c,d).", fig.align="center", echo=FALSE}
 
@@
 In the Discussion we speculate that these two time periods might correspond to distinct types of signal associated with the uncanny valley.
-However we first sought to generalise our results to a different stimulus set, and next report the results of Experiment 2 which used hyper-realistic silicone masks.
 
@@
 However we note that the android and robot categories were typically rated as being more similar to each other than to the real human faces.
+Following Experiment 1, we sought to generalise our results to a different stimulus set, and next report the results of Experiment 2 which used hyper-realistic silicone masks.
 
@@
 Panel (a) shows d-prime scores for identifying images of human faces (blue), silicone masks (green) and Halloween masks (red).
-Small points show individual participants, and the larger symbols with error bars indicate the group mean and bootstrapped 95 percent confidence intervals.
+Small points show individual participants, and the larger symbols with error bars indicate the group mean and bootstrapped 95\\% confidence intervals.
 Panel (b) plots reaction times in the same format (note the logarithmic x-axis).
 Panel (c) shows the grand mean ERP across all participants and conditions, pooled across electrodes P6, P8, PO6 and PO8 (see inset).
-The shaded region around the curve illustrates the 95 percent confidence interval, and the grey rectangle at the foot indicates the stimulus duration.", fig.align="center", echo=FALSE}
+The shaded region around the curve illustrates the 95\\% confidence interval, and the grey rectangle at the foot indicates the stimulus duration.", fig.align="center", echo=FALSE}
 
@@
 
-We subsequently obtained ratings from an independent sample of 20 participants using the same stimuli as in the main experiment.
+We subsequently obtained ratings from an independent sample of 20 participants using the same stimuli as in the EEG experiment.
 This time, we asked for explicit ratings of emotional expressiveness, realism, and uncanniness, as well as repeating the binary real face vs mask rating.
@@
 Arguably making judgements of uncanniness is less appropriate for masks that are not intended to be realistic, though our data do qualitatively conform to the U-shaped function expected by the uncanny valley hypothesis.
-The pattern of d-prime scores (Figure \@ref(fig:maskratings)d) was similar to those obtained in the main experiment (Figure \@ref(fig:MasksData)b), with generally higher scores attributable to the unlimited inspection time permitted here.
+The pattern of d-prime scores (Figure \@ref(fig:maskratings)d) was similar to those obtained in the main experiment (Figure \@ref(fig:MasksData)b), with generally higher scores attributable to the unlimited inspection time permitted in this online follow-up experiment
 
@@
 Perceptual judgements indicated that identification performance for uncanny valley stimuli was relatively poor, indicating confusion with real human images.
+We also confirmed that android images were perceived more negatively than either human or robot images, and that silicone masks were perceived as more uncanny than human faces.
 The similarity in results across our two experiments is striking and constitutes an internal conceptual replication of our main findings.
@@
 Previous studies using these masks have demonstrated that they are difficult to distinguish from real faces [@Sanders2017; @Sanders2019], including in applied settings such as simulated passport control [@Robertson2020; @Robertson2024], and show large individual differences [@Sanders2018].
-Image analysis indicates that good identification performance of silicone masks is typically based on attention to the region below the eyes [@Sanders2018], however it is plausible that many observers are not explicitly aware of the cues they use to perform this judgement.
+Image analysis indicates that good identification performance for silicone masks is typically based on attention to the region below the eyes [@Sanders2018], however it is plausible that many observers are not explicitly aware of the cues they use to perform this judgement.
 This might contribute to both the early and late components identified in this study, and presumably also to the subjective sensation of 'uncanniness' that is characteristic of the phenomenon.

### 2024-07-01 manuscript.tex
Finished implementing co-author comments

@@
 (2012) measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
-They found repetition suppression effects\footnote{Repetition suppression is a phenomenon in which the neural responses to repeated presentations of identical or similar stimuli is reduced relative to the response on the first presentation.} in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
+They found repetition suppression effects\footnote{Repetition suppression is a phenomenon in which the neural response to repeated presentations of identical or similar stimuli is reduced relative to the response on the first presentation.} in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
 These effects were stronger than for movies of humans or mechanical robots performing the same actions.
@@
 EEG data were collected using a 64-channel Waveguard cap and an ANT Neuroscan system, sampling at 1kHz.
+The ground electrode was located at position \(AFz\), and all signals were referenced to the whole head average.
 Low latency digital triggers were sent between the display and the EEG amplifier using an 8-bit parallel cable.
@@
 Panel (a) shows d-prime scores for identifying images of human (blue), android (green) and robot (red) faces.
-Small points show individual participants, and the larger symbols with error bars indicate the group mean and bootstrapped 95 percent confidence intervals.
+Small points show individual participants, and the larger symbols with error bars indicate the group mean and bootstrapped 95\% confidence intervals.
 Panel (b) plots reaction times in the same format (note the logarithmic x-axis).
 Panel (c) shows the grand mean ERP across all participants and conditions, pooled across electrodes P6, P8, PO6 and PO8 (see inset).
-The shaded region around the curve illustrates the 95 percent confidence interval, and the grey rectangle at the foot indicates the stimulus duration.}\label{fig:RobotsData}
+The shaded region around the curve illustrates the 95\% confidence interval, and the grey rectangle at the foot indicates the stimulus duration.}\label{fig:RobotsData}
 \end{figure}
@@
 Panels (c) and (d) show multivariate pattern classification accuracy for the same comparisons.
-Points at y = -8 and y = 25 indicate Bayes factor scores for comparisons between ERPs (a,b) and comparing classification accuracy to chance (50 percent correct; c,d).}\label{fig:RobotsMVPA}
+Points at y = -8 and y = 25 indicate Bayes factor scores for comparisons between ERPs (a,b) and comparing classification accuracy to chance (50\% correct; c,d).}\label{fig:RobotsMVPA}
 \end{figure}
@@
 Panel (a) shows d-prime scores for identifying images of human faces (blue), silicone masks (green) and Halloween masks (red).
-Small points show individual participants, and the larger symbols with error bars indicate the group mean and bootstrapped 95 percent confidence intervals.
+Small points show individual participants, and the larger symbols with error bars indicate the group mean and bootstrapped 95\% confidence intervals.
 Panel (b) plots reaction times in the same format (note the logarithmic x-axis).
 Panel (c) shows the grand mean ERP across all participants and conditions, pooled across electrodes P6, P8, PO6 and PO8 (see inset).
-The shaded region around the curve illustrates the 95 percent confidence interval, and the grey rectangle at the foot indicates the stimulus duration.}\label{fig:MasksData}
+The shaded region around the curve illustrates the 95\% confidence interval, and the grey rectangle at the foot indicates the stimulus duration.}\label{fig:MasksData}
 \end{figure}
@@
 Panels (c) and (d) show multivariate pattern classification accuracy for the same comparisons.
-Points at y = -8 and y = 25 indicate Bayes factor scores for comparisons between ERPs (a,b) and comparing classification accuracy to chance (50 percent correct; c,d).}\label{fig:MasksMVPA}
+Points at y = -8 and y = 25 indicate Bayes factor scores for comparisons between ERPs (a,b) and comparing classification accuracy to chance (50\% correct; c,d).}\label{fig:MasksMVPA}
 \end{figure}
@@
 Arguably making judgements of uncanniness is less appropriate for masks that are not intended to be realistic, though our data do qualitatively conform to the U-shaped function expected by the uncanny valley hypothesis.
-The pattern of d-prime scores (Figure \ref{fig:maskratings}d) was similar to those obtained in the main experiment (Figure \ref{fig:MasksData}b), with generally higher scores attributable to the unlimited inspection time permitted here.
+The pattern of d-prime scores (Figure \ref{fig:maskratings}d) was similar to those obtained in the main experiment (Figure \ref{fig:MasksData}b), with generally higher scores attributable to the unlimited inspection time permitted in this online follow-up experiment
 
@@
 Previous studies using these masks have demonstrated that they are difficult to distinguish from real faces (Sanders et al., 2017, 2019), including in applied settings such as simulated passport control (Robertson et al., 2020, 2024), and show large individual differences (Sanders \& Jenkins, 2018).
-Image analysis indicates that good identification performance of silicone masks is typically based on attention to the region below the eyes (Sanders \& Jenkins, 2018), however it is plausible that many observers are not explicitly aware of the cues they use to perform this judgement.
+Image analysis indicates that good identification performance for silicone masks is typically based on attention to the region below the eyes (Sanders \& Jenkins, 2018), however it is plausible that many observers are not explicitly aware of the cues they use to perform this judgement.
 This might contribute to both the early and late components identified in this study, and presumably also to the subjective sensation of `uncanniness' that is characteristic of the phenomenon.

### 2024-07-01 manuscript.Rmd
Fixed another osf download bug

@@
   osfproject <- osf_retrieve_node('uzbns')
-  osffiles <- osf_ls_files(osfproject)
+  osffiles <- osf_ls_files(osfproject,n_max=100)
   fid <- which(osffiles$name==filelist[f])
@@
   osfproject <- osf_retrieve_node('uzbns')
-  osffiles <- osf_ls_files(osfproject)
+  osffiles <- osf_ls_files(osfproject,n_max=100)
   fid <- which(osffiles$name=='GroupDataRobots.RData')
@@
   osfproject <- osf_retrieve_node('uzbns')
-  osffiles <- osf_ls_files(osfproject)
+  osffiles <- osf_ls_files(osfproject,n_max=100)
   fid <- which(osffiles$name=='GroupDataMasks.RData')

### 2024-09-21 manuscript.Rmd
Minor edits and changed references to numerical formatting

@@
 bibliography: references.bib
-csl: computers-in-human-behavior.csl
+csl: plos.csl
+author: |
+  | Shona Fitzpatrick$^1$, Ailish K. Byrne$^2$, Alex Headley$^1$, Jet G. Sanders$^3$,
+  | Helen Petrie$^4$, Rob Jenkins$^1$ & Daniel H. Baker$^{1,5}$
 ---
 
-[**Author information redacted for blind peer review**]
-
-<!-- author: | -->
-<!--   | Shona Fitzpatrick$^1$, Ailish K. Byrne$^2$, Alex Headley$^1$, Jet G. Sanders$^3$, -->
-<!--   | Helen Petrie$^4$, Rob Jenkins$^1$ & Daniel H. Baker$^{1,5}$ -->
-
-<!-- 1. Department of Psychology, University of York, York, UK -->
-<!-- 2. School of Medicine, Keele University, Newcastle-under-Lyme, Staffordshire, UK -->
-<!-- 3. Department of Psychological and Behavioural Science, London School of Economics, London, UK -->
-<!-- 4. Department of Computer Science, University of York, York, UK -->
-<!-- 5. Corresponding author, email: daniel.baker\@york.ac.uk -->
+1. Department of Psychology, University of York, York, UK
+2. School of Medicine, Keele University, Newcastle-under-Lyme, Staffordshire, UK
+3. Department of Psychological and Behavioural Science, London School of Economics, London, UK
+4. Department of Computer Science, University of York, York, UK
+5. Corresponding author, email: daniel.baker\@york.ac.uk
 
@@
 There are also event-related potential (ERP) signals associated with face and body stimuli, though their precise role is still debated [@Thierry2007; @Hong2022].
-It seems highly likely that 'uncanny' images will activate these same processes, yet it is unclear whether the sense of unease they produce occurs at bottom-up sensory stages or is modulated by more top-down cognitive factors.
+It seems highly likely that 'uncanny' images will activate these same processes, yet it is unclear whether the initial cause of the sense of unease they produce occurs at bottom-up sensory stages [@MacDorman2024; @MacDorman2016; @Moore2012] or is modulated by more top-down cognitive factors [@Gray2012; @Yam2021].
 
@@
 Row (b) shows a human face, a hyper-realistic silicone mask, and a Halloween mask, all against natural backgrounds.
-Images were taken from a variety of sources that permit reuse in academic contexts and in most cases were not part of the stimulus set from the experiments.
+Images shown here were taken from a variety of sources that permit reuse in academic contexts and in most cases were not part of the stimulus set from the experiments.
 The silicone mask image was taken by the authors, and was used in Experiment 2.", fig.align="center", out.width='80%', echo=FALSE}
@@
 A total of 29 participants completed Experiment 1 (12 male, 17 female), and 30 different participants completed Experiment 2 (7 male, 23 female).
+Participants were young adults with no history of neurological disorder.
 None of the participants had previously taken part in a study using these stimuli, and all were naïve to the hypotheses and wore their normal optical correction if required.
-Written informed consent was collected before each experiment began, and all procedures were approved by the Ethics committee of [**redacted for blind peer review**].
+Written informed consent was collected before each experiment began, and all procedures were approved by the Ethics committee of the Department of Psychology at the University of York.
 
@@
 In Experiment 1, the stimulus set consisted of a total of 90 images, evenly split between three categories: real faces, human-like robots, and mechanical robots.
-Images all showed the head and shoulders of the subject, had white backgrounds, and were sourced from the internet.
+Images all showed the head and shoulders of the subject, had white backgrounds, and were sourced from the Internet.
 In Experiment 2, the stimulus set (first described by @Sanders2019, but here including additional images) consisted of a total of 296 images, comprising real faces (148 images), people wearing silicone masks (74 images), and people wearing obvious masks of the sort typically worn for carnivals and Halloween celebrations (74 images).
@@
 These involved rating their perception of a subset of the stimuli (8 from each category), using items from the Godspeed questionnaire [@Bartneck2009].
+Items were selected that were expected to be most closely aligned to measuring the sensation of uncanniness.
 Inspection time was unlimited.
@@
 
-We performed univariate analyses by conducting Bayesian t-tests [@Rouder2009] between ERPs from pairs of conditions at each time point using a JZS prior, using signals pooled across electrodes P6, P8, PO6 and PO8.
+We performed univariate analyses by conducting Bayesian t-tests [@Rouder2009] between ERPs from pairs of conditions at each time point using a JZS prior, using signals pooled across electrodes P6, P8, PO6 and PO8, which are typically associated with visual responses to faces.
 The resulting Bayes factor score is a summary of the evidence in favour of either the null hypothesis (that the waveforms are equal) or the alternative hypothesis (that they differ).
@@
 Multivariate pattern analysis was conducted by training a linear support vector machine algorithm [LibSVM, @Chang2011] to discriminate between patterns of activity across electrodes at a specific time point.
+Previous work has indicated that EEG data do not typically require more complex nonlinear algorithms [@Grootswagers2017].
 The patterns came from the human face condition and one of the other conditions, for a single participant.
@@
 
-Raw data, processed data, and analysis scripts are freely available through the project repository at: [**redacted for blind peer review**] 
-<!-- https://doi.org/10.17605/OSF.IO/5NZ2H -->
+Raw data, processed data, and analysis scripts are freely available through the project repository at: https://doi.org/10.17605/OSF.IO/5NZ2H
 
@@
 ```{r RobotsData, fig.cap="Summary of response data and grand mean ERP for Experiment 1.
-Panel (a) shows d-prime scores for identifying images of human (blue), android (green) and robot (red) faces.
+Panel (a) shows d-prime scores for identifying images of human (blue diamonds), android (green squares) and robot (red circles) faces.
 Small points show individual participants, and the larger symbols with error bars indicate the group mean and bootstrapped 95\\% confidence intervals.
@@
 ```{r MasksData, fig.cap="Summary of response data and grand mean ERP for Experiment 2.
-Panel (a) shows d-prime scores for identifying images of human faces (blue), silicone masks (green) and Halloween masks (red).
+Panel (a) shows d-prime scores for identifying images of human faces (blue diamonds), silicone masks (green squares) and Halloween masks (red circles).
 Small points show individual participants, and the larger symbols with error bars indicate the group mean and bootstrapped 95\\% confidence intervals.
@@
 
-[**redacted for blind peer review**]
-<!-- SF was funded by a YorRobots Venables internship.
+SF was funded by a YorRobots Venables internship.
 JGS was funded by the Economic and Social Research Council (Studentship ES/J500215/1) and Prins Bernhard Cultuurfonds (grant E/30/30.13.0630/HVH/IE).
 Also supported by BBSRC grant BB/V007580/1 awarded to DHB.
--->
 

### 2024-09-21 manuscript.tex
Minor edits and changed references to numerical formatting

@@
 for robots and hyper-realistic masks}
-\author{}
-\date{\vspace{-2.5em}}
+\author{Shona Fitzpatrick\(^1\), Ailish K. Byrne\(^2\), Alex Headley\(^1\), Jet G. Sanders\(^3\),\\
+Helen Petrie\(^4\), Rob Jenkins\(^1\) \& Daniel H. Baker\(^{1,5}\)}
+\date{}
 
@@
 
-{[}\textbf{Author information redacted for blind peer review}{]}
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Department of Psychology, University of York, York, UK
+\item
+  School of Medicine, Keele University, Newcastle-under-Lyme, Staffordshire, UK
+\item
+  Department of Psychological and Behavioural Science, London School of Economics, London, UK
+\item
+  Department of Computer Science, University of York, York, UK
+\item
+  Corresponding author, email: daniel.baker@york.ac.uk
+\end{enumerate}
 
@@
 Many people report an aversion to entities that are superficially human-like, but on closer inspection turn out to be artificial.
-Examples include humanoid robots (androids), puppets, hyper-realistic masks (Sanders \& Jenkins, 2021), and computer-generated images or movies.
-The term `uncanny valley' (Mori, 1970; English translation in Mori et al., 2012) describes the idea that clearly human or clearly artificial entities do not evoke unease, whereas artificial entities that are human-like are disconcerting.
+Examples include humanoid robots (androids), puppets, hyper-realistic masks {[}1{]}, and computer-generated images or movies.
+The term `uncanny valley' {[}2,English translation in 3{]} describes the idea that clearly human or clearly artificial entities do not evoke unease, whereas artificial entities that are human-like are disconcerting.
 Understanding these experiences is increasingly important as artificial entities become more integrated into our everyday lives.
-However at present relatively little is known about the neural underpinnings of the uncanny valley effect (for a recent review, see Vaitonytė et al., 2023).
+However at present relatively little is known about the neural underpinnings of the uncanny valley effect {[}for a recent review, see 4{]}.
 
-Neural responses to faces and bodies in general are well-characterised, and there appear to be specialised brain regions devoted to both (reviewed in Hu et al., 2020).
-For example, areas of the occipital lobe (Gauthier et al., 2000) and fusiform gyrus (Kanwisher et al., 1997) respond more to faces than non-face stimuli, and sections of extrastriate cortex are responsive to bodies (Downing et al., 2001).
-There are also event-related potential (ERP) signals associated with face and body stimuli, though their precise role is still debated (Hong et al., 2022; Thierry et al., 2007).
-It seems highly likely that `uncanny' images will activate these same processes, yet it is unclear whether the sense of unease they produce occurs at bottom-up sensory stages or is modulated by more top-down cognitive factors.
+Neural responses to faces and bodies in general are well-characterised, and there appear to be specialised brain regions devoted to both {[}reviewed in 5{]}.
+For example, areas of the occipital lobe {[}6{]} and fusiform gyrus {[}7{]} respond more to faces than non-face stimuli, and sections of extrastriate cortex are responsive to bodies {[}8{]}.
+There are also event-related potential (ERP) signals associated with face and body stimuli, though their precise role is still debated {[}9,10{]}.
+It seems highly likely that `uncanny' images will activate these same processes, yet it is unclear whether the initial cause of the sense of unease they produce occurs at bottom-up sensory stages {[}11--13{]} or is modulated by more top-down cognitive factors {[}14,15{]}.
 
-One previous study by Saygin et al.
-(2012) measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
+One previous study by {[}16{]} measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
 They found repetition suppression effects\footnote{Repetition suppression is a phenomenon in which the neural response to repeated presentations of identical or similar stimuli is reduced relative to the response on the first presentation.} in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
 These effects were stronger than for movies of humans or mechanical robots performing the same actions.
-A more recent electroencephalography (EEG) study (Urgen et al., 2018) identified a difference in the N400 component\footnote{The N400 is an electromagnetic brain potential obtained 400ms after stimulus onset, typically over centro-parietal electrodes.
+A more recent electroencephalography (EEG) study {[}17{]} identified a difference in the N400 component\footnote{The N400 is an electromagnetic brain potential obtained 400ms after stimulus onset, typically over centro-parietal electrodes.
 It has been proposed to reflect the extent to which the stimulus presented was surprising or unexpected.} between dynamic and static conditions using the same stimuli.
-Although this difference was strongest over frontal electrodes, source reconstruction of the N400 itself suggested a left-lateralised source in the temporo-parietal cortex, consistent with the fMRI results (Saygin et al., 2012).
+Although this difference was strongest over frontal electrodes, source reconstruction of the N400 itself suggested a left-lateralised source in the temporo-parietal cortex, consistent with the fMRI results {[}16{]}.
 The authors interpret both of these findings as being due to the discrepancy between the human-like appearance and the clearly non-biological motion of the robot.
@@
 In the first experiment, the stimuli were still images of humans, machine-like robots, and human-like robots (see Figure \ref{fig:stimexamples}a).
-In the second experiment we aimed to generalise the finding by using images of people wearing no masks, wearing obvious masks (e.g.~Halloween masks), and wearing hyper-realistic silicone masks (Sanders et al., 2017) (see Figure \ref{fig:stimexamples}b).
+In the second experiment we aimed to generalise the finding by using images of people wearing no masks, wearing obvious masks (e.g.~Halloween masks), and wearing hyper-realistic silicone masks {[}18{]} (see Figure \ref{fig:stimexamples}b).
 Rather than focus on specific ERP components, we use a multivariate pattern classification approach to identify time windows in which information in the EEG signal can be used to distinguish between pairs of conditions.
@@
 Row (b) shows a human face, a hyper-realistic silicone mask, and a Halloween mask, all against natural backgrounds.
-Images were taken from a variety of sources that permit reuse in academic contexts and in most cases were not part of the stimulus set from the experiments.
+Images shown here were taken from a variety of sources that permit reuse in academic contexts and in most cases were not part of the stimulus set from the experiments.
 The silicone mask image was taken by the authors, and was used in Experiment 2.}\label{fig:stimexamples}
@@
 A total of 29 participants completed Experiment 1 (12 male, 17 female), and 30 different participants completed Experiment 2 (7 male, 23 female).
+Participants were young adults with no history of neurological disorder.
 None of the participants had previously taken part in a study using these stimuli, and all were naïve to the hypotheses and wore their normal optical correction if required.
-Written informed consent was collected before each experiment began, and all procedures were approved by the Ethics committee of {[}\textbf{redacted for blind peer review}{]}.
+Written informed consent was collected before each experiment began, and all procedures were approved by the Ethics committee of the Department of Psychology at the University of York.
 
@@
 In Experiment 1, the stimulus set consisted of a total of 90 images, evenly split between three categories: real faces, human-like robots, and mechanical robots.
-Images all showed the head and shoulders of the subject, had white backgrounds, and were sourced from the internet.
-In Experiment 2, the stimulus set (first described by Sanders et al.
-(2019), but here including additional images) consisted of a total of 296 images, comprising real faces (148 images), people wearing silicone masks (74 images), and people wearing obvious masks of the sort typically worn for carnivals and Halloween celebrations (74 images).
+Images all showed the head and shoulders of the subject, had white backgrounds, and were sourced from the Internet.
+In Experiment 2, the stimulus set (first described by {[}19{]}, but here including additional images) consisted of a total of 296 images, comprising real faces (148 images), people wearing silicone masks (74 images), and people wearing obvious masks of the sort typically worn for carnivals and Halloween celebrations (74 images).
 The backgrounds of these images were more heterogeneous, and showed the natural surroundings of the subject.
@@
 After the EEG experiment, participants also completed a series of questionnaires using the Qualtrics platform.
-These involved rating their perception of a subset of the stimuli (8 from each category), using items from the Godspeed questionnaire (Bartneck et al., 2009).
+These involved rating their perception of a subset of the stimuli (8 from each category), using items from the Godspeed questionnaire {[}20{]}.
+Items were selected that were expected to be most closely aligned to measuring the sensation of uncanniness.
 Inspection time was unlimited.
-Participants also provided demographic information (age, gender) and completed the GAToRS (Koverola et al., 2022) and AQ (Baron-Cohen et al., 2001) questionnaires, however the results of these additional questionnaires are not presented here.
+Participants also provided demographic information (age, gender) and completed the GAToRS {[}21{]} and AQ {[}22{]} questionnaires, however the results of these additional questionnaires are not presented here.
 
@@
 In the third block, stimuli doubled in size again, and subtended \(22\times30\) degrees.
-The rationale for the size manipulation was to investigate whether increasing levels of detail made the silicone masks more identifiable (Sanders et al., 2017, 2019).
+The rationale for the size manipulation was to investigate whether increasing levels of detail made the silicone masks more identifiable {[}18,19{]}.
 However as that is not the main focus of the current paper, and our preliminary analyses indicated no differences between size conditions, we collapse results across size conditions.
@@
 
-We analysed response data by calculating d-prime (\(d'\)) scores for each condition, derived from the hit rate and false alarm rate (Macmillan \& Creelman, 2005).
+We analysed response data by calculating d-prime (\(d'\)) scores for each condition, derived from the hit rate and false alarm rate {[}23{]}.
 For the human conditions, the hit rate was the proportion of human images correctly identified as human, and the false alarm rate was the proportion of robot or mask images that were incorrectly judged as being human.
@@
 EEG signals were recorded during each block and saved to disc for subsequent offline analysis.
-We used components of the EEGlab toolbox (Delorme \& Makeig, 2004) to import the data into Matlab and collate data across blocks.
-We then used Brainstorm (Tadel et al., 2011) to filter the data using a bandpass filter (0.5 to 30Hz), epoch by condition, and subtract a pre-trial baseline (the mean voltage for the 200ms before stimulus onset).
+We used components of the EEGlab toolbox {[}24{]} to import the data into Matlab and collate data across blocks.
+We then used Brainstorm {[}25{]} to filter the data using a bandpass filter (0.5 to 30Hz), epoch by condition, and subtract a pre-trial baseline (the mean voltage for the 200ms before stimulus onset).
 Five participants were excluded from the EEG analysis of each experiment due to excessive noise.
@@
 
-We performed univariate analyses by conducting Bayesian t-tests (Rouder et al., 2009) between ERPs from pairs of conditions at each time point using a JZS prior, using signals pooled across electrodes P6, P8, PO6 and PO8.
+We performed univariate analyses by conducting Bayesian t-tests {[}26{]} between ERPs from pairs of conditions at each time point using a JZS prior, using signals pooled across electrodes P6, P8, PO6 and PO8, which are typically associated with visual responses to faces.
 The resulting Bayes factor score is a summary of the evidence in favour of either the null hypothesis (that the waveforms are equal) or the alternative hypothesis (that they differ).
-We use the heuristics proposed by Jeffreys (1961) that Bayes factors \textgreater3 (\(log_{10}BF_{10}\) \textgreater{} 0.5) constitute some evidence supporting the alternative hypothesis, factors \textgreater10 (\(log_{10}BF_{10}\) \textgreater{} 1) constitute strong evidence, and factors \textgreater30 (\(log_{10}BF_{10}\) \textgreater{} 1.5) constitute very strong evidence.
+We use the heuristics proposed by {[}27{]} that Bayes factors \textgreater3 (\(log_{10}BF_{10}\) \textgreater{} 0.5) constitute some evidence supporting the alternative hypothesis, factors \textgreater10 (\(log_{10}BF_{10}\) \textgreater{} 1) constitute strong evidence, and factors \textgreater30 (\(log_{10}BF_{10}\) \textgreater{} 1.5) constitute very strong evidence.
 
-Multivariate pattern analysis was conducted by training a linear support vector machine algorithm (LibSVM, Chang \& Lin, 2011) to discriminate between patterns of activity across electrodes at a specific time point.
+Multivariate pattern analysis was conducted by training a linear support vector machine algorithm {[}LibSVM, 28{]} to discriminate between patterns of activity across electrodes at a specific time point.
+Previous work has indicated that EEG data do not typically require more complex nonlinear algorithms {[}29{]}.
 The patterns came from the human face condition and one of the other conditions, for a single participant.
@@
 
-Raw data, processed data, and analysis scripts are freely available through the project repository at: {[}\textbf{redacted for blind peer review}{]}
+Raw data, processed data, and analysis scripts are freely available through the project repository at: \url{https://doi.org/10.17605/OSF.IO/5NZ2H}
 
@@
 \caption{Summary of response data and grand mean ERP for Experiment 1.
-Panel (a) shows d-prime scores for identifying images of human (blue), android (green) and robot (red) faces.
+Panel (a) shows d-prime scores for identifying images of human (blue diamonds), android (green squares) and robot (red circles) faces.
 Small points show individual participants, and the larger symbols with error bars indicate the group mean and bootstrapped 95\% confidence intervals.
@@
 Pairwise comparisons of conditions are shown in Figure \ref{fig:RobotsMVPA}a,b.
-In general there is a tendency for the ERP response to human faces to diverge slightly from the other two conditions (Geiger \& Balas, 2021), however the evidence for this divergence was not compelling.
+In general there is a tendency for the ERP response to human faces to diverge slightly from the other two conditions {[}30{]}, however the evidence for this divergence was not compelling.
 Bayes factors exceeded 3 for only a small number of time points around 300-400ms in the comparison between human and robot images (see yellow bars at y = -8 in Figure \ref{fig:RobotsMVPA}a), but these differences were small considering the variance in the data.
@@
 \caption{Summary of response data and grand mean ERP for Experiment 2.
-Panel (a) shows d-prime scores for identifying images of human faces (blue), silicone masks (green) and Halloween masks (red).
+Panel (a) shows d-prime scores for identifying images of human faces (blue diamonds), silicone masks (green squares) and Halloween masks (red circles).
 Small points show individual participants, and the larger symbols with error bars indicate the group mean and bootstrapped 95\% confidence intervals.
@@
 The early time window when pattern classification is above chance corresponds approximately to the P100 and N170 components of the ERP.
-Similar early components have also been investigated in other ERP studies on the uncanny valley effect (Mustafa \& Magnor, 2016; Schindler et al., 2017), and comparing human and robot faces (Geiger \& Balas, 2021).
-This time window is unlikely to be modulated substantially by top-down influences, so we attribute the early component to image-based differences between stimulus categories (Coggan et al., 2016).
-ERP components in later time windows have also been studied in previous work (Cheetham et al., 2015; Mustafa et al., 2017; Urgen et al., 2018).
+Similar early components have also been investigated in other ERP studies on the uncanny valley effect {[}31,32{]}, and comparing human and robot faces {[}30{]}.
+This time window is unlikely to be modulated substantially by top-down influences, so we attribute the early component to image-based differences between stimulus categories {[}33{]}.
+ERP components in later time windows have also been studied in previous work {[}17,34,35{]}.
 Differences between stimulus categories at these times are more amenable to top-down influences, and most likely involve higher brain areas outside of occipital cortex.
@@
 Our use of hyper-realistic silicone masks is novel in the context of the study of uncanny valley effects.
-Previous studies using these masks have demonstrated that they are difficult to distinguish from real faces (Sanders et al., 2017, 2019), including in applied settings such as simulated passport control (Robertson et al., 2020, 2024), and show large individual differences (Sanders \& Jenkins, 2018).
-Image analysis indicates that good identification performance for silicone masks is typically based on attention to the region below the eyes (Sanders \& Jenkins, 2018), however it is plausible that many observers are not explicitly aware of the cues they use to perform this judgement.
+Previous studies using these masks have demonstrated that they are difficult to distinguish from real faces {[}18,19{]}, including in applied settings such as simulated passport control {[}36,37{]}, and show large individual differences {[}38{]}.
+Image analysis indicates that good identification performance for silicone masks is typically based on attention to the region below the eyes {[}38{]}, however it is plausible that many observers are not explicitly aware of the cues they use to perform this judgement.
 This might contribute to both the early and late components identified in this study, and presumably also to the subjective sensation of `uncanniness' that is characteristic of the phenomenon.
@@
 More generally, the advantage of measuring neural responses to `uncanny valley' stimuli is that, without requiring conscious awareness or behavioural responses, they can facilitate detection of near-human stimuli.
-These types of near-human stimuli are becoming increasingly common in impersonation and identity evasion cases (Sanders \& Jenkins, 2021).
+These types of near-human stimuli are becoming increasingly common in impersonation and identity evasion cases {[}1{]}.
 Simultaneously, we observe a growing market for reducing the uncanny valley effect for the benefit of android and robot integration.
@@
 
-{[}\textbf{redacted for blind peer review}{]}
+SF was funded by a YorRobots Venables internship.
+JGS was funded by the Economic and Social Research Council (Studentship ES/J500215/1) and Prins Bernhard Cultuurfonds (grant E/30/30.13.0630/HVH/IE).
+Also supported by BBSRC grant BB/V007580/1 awarded to DHB.
 
@@
 \phantomsection\label{refs}
-\begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-Baron-Cohen2001}
-Baron-Cohen, S., Wheelwright, S., Skinner, R., Martin, J., \& Clubley, E.
-(2001).
-The autism-spectrum quotient (AQ): Evidence from asperger syndrome/high-functioning autism, males and females, scientists and mathematicians.
-\emph{J Autism Dev Disord}, \emph{31}(1), 5--17.
-\url{https://doi.org/10.1023/a:1005653411471}
+\begin{CSLReferences}{0}{1}
+\bibitem[\citeproctext]{ref-Sanders2021}
+\CSLLeftMargin{1. }%
+\CSLRightInline{Sanders JG, Jenkins R.
+Realistic masks in the real world.
+In: Bindemann M, editor.
+{Forensic Face Matching: Research and Practice}.
+Oxford University Press; 2021.
+doi:\href{https://doi.org/10.1093/oso/9780198837749.003.0010}{10.1093/oso/9780198837749.003.0010}}
+
+\bibitem[\citeproctext]{ref-Mori1970}
+\CSLLeftMargin{2. }%
+\CSLRightInline{Mori M. The uncanny valley. Energy. 1970;7: 33--35. }
+
+\bibitem[\citeproctext]{ref-Mori2012}
+\CSLLeftMargin{3. }%
+\CSLRightInline{Mori M, MacDorman KF, Kageki N.
+The uncanny valley {[}from the field{]}.
+IEEE Robotics \& Automation Magazine.
+2012;19: 98--100.
+doi:\href{https://doi.org/10.1109/MRA.2012.2192811}{10.1109/MRA.2012.2192811}}
+
+\bibitem[\citeproctext]{ref-Vaitonyte2023}
+\CSLLeftMargin{4. }%
+\CSLRightInline{Vaitonytė J, Alimardani M, Louwerse MM.
+Scoping review of the neural evidence on the uncanny valley.
+Computers in Human Behavior Reports.
+2023;9: 100263.
+doi:\url{https://doi.org/10.1016/j.chbr.2022.100263}}
+
+\bibitem[\citeproctext]{ref-Hu2020}
+\CSLLeftMargin{5. }%
+\CSLRightInline{Hu Y, Baragchizadeh A, O'Toole AJ.
+Integrating faces and bodies: Psychological and neural perspectives on whole person perception.
+Neurosci Biobehav Rev.
+2020;112: 472--486.
+doi:\href{https://doi.org/10.1016/j.neubiorev.2020.02.021}{10.1016/j.neubiorev.2020.02.021}}
+
+\bibitem[\citeproctext]{ref-Gauthier2000}
+\CSLLeftMargin{6. }%
+\CSLRightInline{Gauthier I, Tarr MJ, Moylan J, Skudlarski P, Gore JC, Anderson AW.
+The fusiform "face area" is part of a network that processes faces at the individual level.
+J Cogn Neurosci.
+2000;12: 495--504.
+doi:\href{https://doi.org/10.1162/089892900562165}{10.1162/089892900562165}}
+
+\bibitem[\citeproctext]{ref-Kanwisher1997}
+\CSLLeftMargin{7. }%
+\CSLRightInline{Kanwisher N, McDermott J, Chun MM.
+The fusiform face area: A module in human extrastriate cortex specialized for face perception.
+J Neurosci.
+1997;17: 4302--11.
+doi:\href{https://doi.org/10.1523/JNEUROSCI.17-11-04302.1997}{10.1523/JNEUROSCI.17-11-04302.1997}}
+
+\bibitem[\citeproctext]{ref-Downing2001}
+\CSLLeftMargin{8. }%
+\CSLRightInline{Downing PE, Jiang Y, Shuman M, Kanwisher N.
+A cortical area selective for visual processing of the human body.
+Science.
+2001;293: 2470--3.
+doi:\href{https://doi.org/10.1126/science.1063414}{10.1126/science.1063414}}
+
+\bibitem[\citeproctext]{ref-Thierry2007}
+\CSLLeftMargin{9. }%
+\CSLRightInline{Thierry G, Martin CD, Downing P, Pegna AJ.
+Controlling for interstimulus perceptual variance abolishes N170 face selectivity.
+Nat Neurosci.
+2007;10: 505--11.
+doi:\href{https://doi.org/10.1038/nn1864}{10.1038/nn1864}}
+
+\bibitem[\citeproctext]{ref-Hong2022}
+\CSLLeftMargin{10. }%
+\CSLRightInline{Hong Y, Mayes MS, Munasinghe AP, Ratner KG.
+Scrutinizing whether mere group membership influences the N170 response to faces: Results from two preregistered event-related potential studies.
+J Cogn Neurosci.
+2022;34: 1999--2015.
+doi:\href{https://doi.org/10.1162/jocn_a_01887}{10.1162/jocn\_a\_01887}}
+
+\bibitem[\citeproctext]{ref-MacDorman2024}
+\CSLLeftMargin{11. }%
+\CSLRightInline{MacDorman KF.
+Does mind perception explain the uncanny valley?
+A meta-regression analysis and (de)humanization experiment.
+Computers in Human Behavior: Artificial Humans.
+2024;2: 100065.
+doi:\url{https://doi.org/10.1016/j.chbah.2024.100065}}
+
+\bibitem[\citeproctext]{ref-MacDorman2016}
+\CSLLeftMargin{12. }%
+\CSLRightInline{MacDorman KF, Chattopadhyay D.
+Reducing consistency in human realism increases the uncanny valley effect; increasing category uncertainty does not.
+Cognition.
+2016;146: 190--205.
+doi:\href{https://doi.org/10.1016/j.cognition.2015.09.019}{10.1016/j.cognition.2015.09.019}}
+
+\bibitem[\citeproctext]{ref-Moore2012}
+\CSLLeftMargin{13. }%
+\CSLRightInline{Moore RK.
+A bayesian explanation of the 'uncanny valley' effect and related psychological phenomena.
+Sci Rep.
+2012;2: 864.
+doi:\href{https://doi.org/10.1038/srep00864}{10.1038/srep00864}}
+
+\bibitem[\citeproctext]{ref-Gray2012}
+\CSLLeftMargin{14. }%
+\CSLRightInline{Gray K, Wegner DM.
+Feeling robots and human zombies: Mind perception and the uncanny valley.
+Cognition.
+2012;125: 125--30.
+doi:\href{https://doi.org/10.1016/j.cognition.2012.06.007}{10.1016/j.cognition.2012.06.007}}
+
+\bibitem[\citeproctext]{ref-Yam2021}
+\CSLLeftMargin{15. }%
+\CSLRightInline{Yam KC, Bigman Y, Gray K.
+Reducing the uncanny valley by dehumanizing humanoid robots.
+Computers in Human Behavior.
+2021;125: 106945.
+doi:\url{https://doi.org/10.1016/j.chb.2021.106945}}
+
+\bibitem[\citeproctext]{ref-Saygin2012}
+\CSLLeftMargin{16. }%
+\CSLRightInline{Saygin AP, Chaminade T, Ishiguro H, Driver J, Frith C.
+The thing that should not be: Predictive coding and the uncanny valley in perceiving human and humanoid robot actions.
+Soc Cogn Affect Neurosci.
+2012;7: 413--22.
+doi:\href{https://doi.org/10.1093/scan/nsr025}{10.1093/scan/nsr025}}
+
+\bibitem[\citeproctext]{ref-Urgen2018}
+\CSLLeftMargin{17. }%
+\CSLRightInline{Urgen BA, Kutas M, Saygin AP.
+Uncanny valley as a window into predictive processing in the social brain.
+Neuropsychologia.
+2018;114: 181--185.
+doi:\href{https://doi.org/10.1016/j.neuropsychologia.2018.04.027}{10.1016/j.neuropsychologia.2018.04.027}}
+
+\bibitem[\citeproctext]{ref-Sanders2017}
+\CSLLeftMargin{18. }%
+\CSLRightInline{Sanders JG, Ueda Y, Minemoto K, Noyes E, Yoshikawa S, Jenkins R.
+Hyper-realistic face masks: A new challenge in person identification.
+Cognitive Research: Principles and Implications.
+2017;2.
+doi:\href{https://doi.org/10.1186/s41235-017-0079-y}{10.1186/s41235-017-0079-y}}
+
+\bibitem[\citeproctext]{ref-Sanders2019}
+\CSLLeftMargin{19. }%
+\CSLRightInline{Sanders JG, Ueda Y, Yoshikawa S, Jenkins R.
+More human than human: A {Turing} test for photographed faces.
+Cogn Res Princ Implic.
+2019;4: 43.
+doi:\href{https://doi.org/10.1186/s41235-019-0197-9}{10.1186/s41235-019-0197-9}}
 
 \bibitem[\citeproctext]{ref-Bartneck2009}
-Bartneck, C., Kulić, D., Croft, E., \& Zoghbi, S.
-(2009).
+\CSLLeftMargin{20. }%
+\CSLRightInline{Bartneck C, Kulić D, Croft E, Zoghbi S.
 Measurement instruments for the anthropomorphism, animacy, likeability, perceived intelligence, and perceived safety of robots.
-\emph{International Journal of Social Robotics}, \emph{1}(1), 71--81.
-\url{https://doi.org/10.1007/s12369-008-0001-3}
+International Journal of Social Robotics.
+2009;1: 71--81.
+doi:\href{https://doi.org/10.1007/s12369-008-0001-3}{10.1007/s12369-008-0001-3}}
+
+\bibitem[\citeproctext]{ref-Koverola2022}
+\CSLLeftMargin{21. }%
+\CSLRightInline{Koverola M, Kunnari A, Sundvall J, Laakasuo M.
+General attitudes towards robots scale (GAToRS): A new instrument for social surveys.
+International Journal of Social Robotics.
+2022;14: 1559--1581.
+doi:\href{https://doi.org/10.1007/s12369-022-00880-3}{10.1007/s12369-022-00880-3}}
+
+\bibitem[\citeproctext]{ref-Baron-Cohen2001}
+\CSLLeftMargin{22. }%
+\CSLRightInline{Baron-Cohen S, Wheelwright S, Skinner R, Martin J, Clubley E.
+The autism-spectrum quotient (AQ): Evidence from {Asperger} syndrome/high-functioning autism, males and females, scientists and mathematicians.
+J Autism Dev Disord.
+2001;31: 5--17.
+doi:\href{https://doi.org/10.1023/a:1005653411471}{10.1023/a:1005653411471}}
+
+\bibitem[\citeproctext]{ref-Macmillan2005}
+\CSLLeftMargin{23. }%
+\CSLRightInline{Macmillan NA, Creelman CD. Detection theory: A user's guide. Psychology Press; 2005. }
+
+\bibitem[\citeproctext]{ref-Delorme2004}
+\CSLLeftMargin{24. }%
+\CSLRightInline{Delorme A, Makeig S.
+{EEGLAB}: An open source toolbox for analysis of single-trial {EEG} dynamics including independent component analysis.
+J Neurosci Methods.
+2004;134: 9--21.
+doi:\href{https://doi.org/10.1016/j.jneumeth.2003.10.009}{10.1016/j.jneumeth.2003.10.009}}
+
+\bibitem[\citeproctext]{ref-Tadel2011}
+\CSLLeftMargin{25. }%
+\CSLRightInline{Tadel F, Baillet S, Mosher JC, Pantazis D, Leahy RM.
+Brainstorm: A user-friendly application for MEG/EEG analysis.
+Comput Intell Neurosci.
+2011;2011: 879716.
+doi:\href{https://doi.org/10.1155/2011/879716}{10.1155/2011/879716}}
+
+\bibitem[\citeproctext]{ref-Rouder2009}
+\CSLLeftMargin{26. }%
+\CSLRightInline{Rouder JN, Speckman PL, Sun D, Morey RD, Iverson G.
+Bayesian t tests for accepting and rejecting the null hypothesis.
+Psychon Bull Rev.
+2009;16: 225--37.
+doi:\href{https://doi.org/10.3758/PBR.16.2.225}{10.3758/PBR.16.2.225}}
+
+\bibitem[\citeproctext]{ref-Jeffreys1961}
+\CSLLeftMargin{27. }%
+\CSLRightInline{Jeffreys H. Theory of probability. 3rd ed. Oxford University Press, Clarendon Press; 1961. }
 
 \bibitem[\citeproctext]{ref-Chang2011}
-Chang, C.-C., \& Lin, C.-J. (2011). {LIBSVM} : A library for support vector machines. \emph{ACM Transactions on Intelligent Systems and Technology}, \emph{2(27)}, 1--27.
+\CSLLeftMargin{28. }%
+\CSLRightInline{Chang C-C, Lin C-J. {LIBSVM} : A library for support vector machines. ACM Transactions on Intelligent Systems and Technology. 2011;2(27): 1--27. }
+
+\bibitem[\citeproctext]{ref-Grootswagers2017}
+\CSLLeftMargin{29. }%
+\CSLRightInline{Grootswagers T, Wardle SG, Carlson TA.
+Decoding dynamic brain patterns from evoked responses: A tutorial on multivariate pattern analysis applied to time series neuroimaging data.
+J Cogn Neurosci.
+2017;29: 677--697.
+doi:\href{https://doi.org/10.1162/jocn_a_01068}{10.1162/jocn\_a\_01068}}
+
+\bibitem[\citeproctext]{ref-Geiger2021}
+\CSLLeftMargin{30. }%
+\CSLRightInline{Geiger AR, Balas B.
+Robot faces elicit responses intermediate to human faces and objects at face-sensitive ERP components.
+Sci Rep.
+2021;11: 17890.
+doi:\href{https://doi.org/10.1038/s41598-021-97527-6}{10.1038/s41598-021-97527-6}}
+
+\bibitem[\citeproctext]{ref-Schindler2017}
+\CSLLeftMargin{31. }%
+\CSLRightInline{Schindler S, Zell E, Botsch M, Kissler J.
+Differential effects of face-realism and emotion on event-related brain potentials and their implications for the uncanny valley theory.
+Sci Rep.
+2017;7: 45003.
+doi:\href{https://doi.org/10.1038/srep45003}{10.1038/srep45003}}
+
+\bibitem[\citeproctext]{ref-Mustafa2016}
+\CSLLeftMargin{32. }%
+\CSLRightInline{Mustafa M, Magnor M.
+EEG based analysis of the perception of computer-generated faces.
+Proceedings of the 13th european conference on visual media production (CVMP 2016).
+ACM; 2016.
+doi:\href{https://doi.org/10.1145/2998559.2998563}{10.1145/2998559.2998563}}
+
+\bibitem[\citeproctext]{ref-Coggan2016}
+\CSLLeftMargin{33. }%
+\CSLRightInline{Coggan DD, Baker DH, Andrews TJ.
+The role of visual and semantic properties in the emergence of category-specific patterns of neural response in the human brain.
+eNeuro.
+2016;3.
+doi:\href{https://doi.org/10.1523/ENEURO.0158-16.2016}{10.1523/ENEURO.0158-16.2016}}
+
+\bibitem[\citeproctext]{ref-Mustafa2017}
+\CSLLeftMargin{34. }%
+\CSLRightInline{Mustafa M, Guthe S, Tauscher J-P, Goesele M, Magnor M.
+How human am i?: EEG-based evaluation of virtual characters.
+Proceedings of the 2017 CHI conference on human factors in computing systems.
+ACM; 2017.
+doi:\href{https://doi.org/10.1145/3025453.3026043}{10.1145/3025453.3026043}}
 
 \bibitem[\citeproctext]{ref-Cheetham2015}
-Cheetham, M., Wu, L., Pauli, P., \& Jancke, L.
-(2015).
+\CSLLeftMargin{35. }%
+\CSLRightInline{Cheetham M, Wu L, Pauli P, Jancke L.
 Arousal, valence, and the uncanny valley: Psychophysiological and self-report findings.
-\emph{Front Psychol}, \emph{6}, 981.
-\url{https://doi.org/10.3389/fpsyg.2015.00981}
+Front Psychol.
+2015;6: 981.
+doi:\href{https://doi.org/10.3389/fpsyg.2015.00981}{10.3389/fpsyg.2015.00981}}
 
-\bibitem[\citeproctext]{ref-Coggan2016}
-Coggan, D.
-D., Baker, D.
-H., \& Andrews, T.
-J.
-(2016).
-The role of visual and semantic properties in the emergence of category-specific patterns of neural response in the human brain.
-\emph{eNeuro}, \emph{3}(4).
-\url{https://doi.org/10.1523/ENEURO.0158-16.2016}
-
-\bibitem[\citeproctext]{ref-Delorme2004}
-Delorme, A., \& Makeig, S.
-(2004).
-{EEGLAB}: An open source toolbox for analysis of single-trial {EEG} dynamics including independent component analysis.
-\emph{J Neurosci Methods}, \emph{134}(1), 9--21.
-\url{https://doi.org/10.1016/j.jneumeth.2003.10.009}
-
-\bibitem[\citeproctext]{ref-Downing2001}
-Downing, P.
-E., Jiang, Y., Shuman, M., \& Kanwisher, N.
-(2001).
-A cortical area selective for visual processing of the human body.
-\emph{Science}, \emph{293}(5539), 2470--2473.
-\url{https://doi.org/10.1126/science.1063414}
-
-\bibitem[\citeproctext]{ref-Gauthier2000}
-Gauthier, I., Tarr, M.
-J., Moylan, J., Skudlarski, P., Gore, J.
-C., \& Anderson, A.
-W.
-(2000).
-The fusiform "face area" is part of a network that processes faces at the individual level.
-\emph{J Cogn Neurosci}, \emph{12}(3), 495--504.
-\url{https://doi.org/10.1162/089892900562165}
-
-\bibitem[\citeproctext]{ref-Geiger2021}
-Geiger, A.
-R., \& Balas, B.
-(2021).
-Robot faces elicit responses intermediate to human faces and objects at face-sensitive ERP components.
-\emph{Sci Rep}, \emph{11}(1), 17890.
-\url{https://doi.org/10.1038/s41598-021-97527-6}
-
-\bibitem[\citeproctext]{ref-Hong2022}
-Hong, Y., Mayes, M.
-S., Munasinghe, A.
-P., \& Ratner, K.
-G.
-(2022).
-Scrutinizing whether mere group membership influences the N170 response to faces: Results from two preregistered event-related potential studies.
-\emph{J Cogn Neurosci}, \emph{34}(11), 1999--2015.
-\url{https://doi.org/10.1162/jocn_a_01887}
-
-\bibitem[\citeproctext]{ref-Hu2020}
-Hu, Y., Baragchizadeh, A., \& O'Toole, A.
-J.
-(2020).
-Integrating faces and bodies: Psychological and neural perspectives on whole person perception.
-\emph{Neurosci Biobehav Rev}, \emph{112}, 472--486.
-\url{https://doi.org/10.1016/j.neubiorev.2020.02.021}
-
-\bibitem[\citeproctext]{ref-Jeffreys1961}
-Jeffreys, H. (1961). \emph{Theory of probability} (3rd ed.). Oxford University Press, Clarendon Press.
-
-\bibitem[\citeproctext]{ref-Kanwisher1997}
-Kanwisher, N., McDermott, J., \& Chun, M.
-M.
-(1997).
-The fusiform face area: A module in human extrastriate cortex specialized for face perception.
-\emph{J Neurosci}, \emph{17}(11), 4302--4311.
-\url{https://doi.org/10.1523/JNEUROSCI.17-11-04302.1997}
-
-\bibitem[\citeproctext]{ref-Koverola2022}
-Koverola, M., Kunnari, A., Sundvall, J., \& Laakasuo, M.
-(2022).
-General attitudes towards robots scale (GAToRS): A new instrument for social surveys.
-\emph{International Journal of Social Robotics}, \emph{14}(7), 1559--1581.
-\url{https://doi.org/10.1007/s12369-022-00880-3}
-
-\bibitem[\citeproctext]{ref-Macmillan2005}
-Macmillan, N. A., \& Creelman, C. D. (2005). \emph{Detection theory: A user's guide}. Psychology Press.
-
-\bibitem[\citeproctext]{ref-Mori1970}
-Mori, M. (1970). The uncanny valley. \emph{Energy}, \emph{7}, 33--35.
-
-\bibitem[\citeproctext]{ref-Mori2012}
-Mori, M., MacDorman, K.
-F., \& Kageki, N.
-(2012).
-The uncanny valley {[}from the field{]}.
-\emph{IEEE Robotics \& Automation Magazine}, \emph{19}(2), 98--100.
-\url{https://doi.org/10.1109/MRA.2012.2192811}
-
-\bibitem[\citeproctext]{ref-Mustafa2017}
-Mustafa, M., Guthe, S., Tauscher, J.-P., Goesele, M., \& Magnor, M.
-(2017, May).
-How human am i?: EEG-based evaluation of virtual characters.
-\emph{Proceedings of the 2017 CHI Conference on Human Factors in Computing Systems}.
-\url{https://doi.org/10.1145/3025453.3026043}
-
-\bibitem[\citeproctext]{ref-Mustafa2016}
-Mustafa, M., \& Magnor, M.
-(2016, December).
-EEG based analysis of the perception of computer-generated faces.
-\emph{Proceedings of the 13th European Conference on Visual Media Production (CVMP 2016)}.
-\url{https://doi.org/10.1145/2998559.2998563}
+\bibitem[\citeproctext]{ref-Robertson2020}
+\CSLLeftMargin{36. }%
+\CSLRightInline{Robertson DJ, Sanders JG, Towler A, Kramer RSS, Spowage J, Byrne A, et al.
+Hyper-realistic face masks in a live passport-checking task.
+Perception.
+2020;49: 298--309.
+doi:\href{https://doi.org/10.1177/0301006620904614}{10.1177/0301006620904614}}
 
 \bibitem[\citeproctext]{ref-Robertson2024}
-Robertson, D.
-J., Davis, J.
-P., Sanders, J.
-G., \& Towler, A.
-(2024).
+\CSLLeftMargin{37. }%
+\CSLRightInline{Robertson DJ, Davis JP, Sanders JG, Towler A.
 The super-recogniser advantage extends to the detection of hyper-realistic face masks.
-\emph{In Press}.
-\url{https://doi.org/10.31234/osf.io/u2kja}
-
-\bibitem[\citeproctext]{ref-Robertson2020}
-Robertson, D.
-J., Sanders, J.
-G., Towler, A., Kramer, R.
-S.
-S., Spowage, J., Byrne, A., Burton, A.
-M., \& Jenkins, R.
-(2020).
-Hyper-realistic face masks in a live passport-checking task.
-\emph{Perception}, \emph{49}(3), 298--309.
-\url{https://doi.org/10.1177/0301006620904614}
-
-\bibitem[\citeproctext]{ref-Rouder2009}
-Rouder, J.
-N., Speckman, P.
-L., Sun, D., Morey, R.
-D., \& Iverson, G.
-(2009).
-Bayesian t tests for accepting and rejecting the null hypothesis.
-\emph{Psychon Bull Rev}, \emph{16}(2), 225--237.
-\url{https://doi.org/10.3758/PBR.16.2.225}
+Applied Cognitive Psychology.
+2024;38: e4222.
+doi:\href{https://doi.org/10.1002/acp.4222}{10.1002/acp.4222}}
 
 \bibitem[\citeproctext]{ref-Sanders2018}
-Sanders, J. G., \& Jenkins, R. (2018). Individual differences in hyper-realistic mask detection. \emph{Cogn Res Princ Implic}, \emph{3}, 24. \url{https://doi.org/10.1186/s41235-018-0118-3}
-
-\bibitem[\citeproctext]{ref-Sanders2021}
-Sanders, J.
-G., \& Jenkins, R.
-(2021).
-Realistic masks in the real world.
-In M.
-Bindemann (Ed.), \emph{{Forensic Face Matching: Research and Practice}}.
-Oxford University Press.
-\url{https://doi.org/10.1093/oso/9780198837749.003.0010}
-
-\bibitem[\citeproctext]{ref-Sanders2017}
-Sanders, J.
-G., Ueda, Y., Minemoto, K., Noyes, E., Yoshikawa, S., \& Jenkins, R.
-(2017).
-Hyper-realistic face masks: A new challenge in person identification.
-\emph{Cognitive Research: Principles and Implications}, \emph{2}(1).
-\url{https://doi.org/10.1186/s41235-017-0079-y}
-
-\bibitem[\citeproctext]{ref-Sanders2019}
-Sanders, J.
-G., Ueda, Y., Yoshikawa, S., \& Jenkins, R.
-(2019).
-More human than human: A turing test for photographed faces.
-\emph{Cogn Res Princ Implic}, \emph{4}(1), 43.
-\url{https://doi.org/10.1186/s41235-019-0197-9}
-
-\bibitem[\citeproctext]{ref-Saygin2012}
-Saygin, A.
-P., Chaminade, T., Ishiguro, H., Driver, J., \& Frith, C.
-(2012).
-The thing that should not be: Predictive coding and the uncanny valley in perceiving human and humanoid robot actions.
-\emph{Soc Cogn Affect Neurosci}, \emph{7}(4), 413--422.
-\url{https://doi.org/10.1093/scan/nsr025}
-
-\bibitem[\citeproctext]{ref-Schindler2017}
-Schindler, S., Zell, E., Botsch, M., \& Kissler, J.
-(2017).
-Differential effects of face-realism and emotion on event-related brain potentials and their implications for the uncanny valley theory.
-\emph{Sci Rep}, \emph{7}, 45003.
-\url{https://doi.org/10.1038/srep45003}
-
-\bibitem[\citeproctext]{ref-Tadel2011}
-Tadel, F., Baillet, S., Mosher, J.
-C., Pantazis, D., \& Leahy, R.
-M.
-(2011).
-Brainstorm: A user-friendly application for MEG/EEG analysis.
-\emph{Comput Intell Neurosci}, \emph{2011}, 879716.
-\url{https://doi.org/10.1155/2011/879716}
-
-\bibitem[\citeproctext]{ref-Thierry2007}
-Thierry, G., Martin, C.
-D., Downing, P., \& Pegna, A.
-J.
-(2007).
-Controlling for interstimulus perceptual variance abolishes N170 face selectivity.
-\emph{Nat Neurosci}, \emph{10}(4), 505--511.
-\url{https://doi.org/10.1038/nn1864}
-
-\bibitem[\citeproctext]{ref-Urgen2018}
-Urgen, B.
-A., Kutas, M., \& Saygin, A.
-P.
-(2018).
-Uncanny valley as a window into predictive processing in the social brain.
-\emph{Neuropsychologia}, \emph{114}, 181--185.
-\url{https://doi.org/10.1016/j.neuropsychologia.2018.04.027}
-
-\bibitem[\citeproctext]{ref-Vaitonyte2023}
-Vaitonytė, J., Alimardani, M., \& Louwerse, M.
-M.
-(2023).
-Scoping review of the neural evidence on the uncanny valley.
-\emph{Computers in Human Behavior Reports}, \emph{9}, 100263.
-https://doi.org/\url{https://doi.org/10.1016/j.chbr.2022.100263}
+\CSLLeftMargin{38. }%
+\CSLRightInline{Sanders JG, Jenkins R.
+Individual differences in hyper-realistic mask detection.
+Cogn Res Princ Implic.
+2018;3: 24.
+doi:\href{https://doi.org/10.1186/s41235-018-0118-3}{10.1186/s41235-018-0118-3}}
 

### 2025-01-12 manuscript.Rmd
Fix autobuild
Implemented reviewer suggestions

@@
 In both experiments, human-like stimuli were harder to distinguish from real human faces than stimuli that were clearly not designed to mimic humans but contain facial features (mechanical robots and Halloween masks).
-Stimulus evoked potentials did not show convincing differences between faces and either androids or realistic masks when using traditional univariate statistical tests.
+Stimulus evoked potentials (electromagnetic brain responses) did not show convincing differences between faces and either androids or realistic masks when using traditional univariate statistical tests.
 However, a more sensitive multivariate analysis identified two regions of above-chance decoding, indicating neural differences in the response between human faces and androids/realistic masks.
@@
 However at present relatively little is known about the neural underpinnings of the uncanny valley effect [for a recent review, see @Vaitonyte2023].
+In particular, the root of the uncanny valley effect remains debated: does it arise primarily from bottom-up sensory conflicts, or from higher-level cognitive processes?
+Resolving this question is critical to understanding its fundamental mechanisms.
 
@@
 For example, areas of the occipital lobe [@Gauthier2000] and fusiform gyrus [@Kanwisher1997] respond more to faces than non-face stimuli, and sections of extrastriate cortex are responsive to bodies [@Downing2001].
-There are also event-related potential (ERP) signals associated with face and body stimuli, though their precise role is still debated [@Thierry2007; @Hong2022].
+There are also electromagnetic event-related potential (ERP) signals associated with face and body stimuli, though their precise role is still debated [@Thierry2007; @Hong2022].
 It seems highly likely that 'uncanny' images will activate these same processes, yet it is unclear whether the initial cause of the sense of unease they produce occurs at bottom-up sensory stages [@MacDorman2024; @MacDorman2016; @Moore2012] or is modulated by more top-down cognitive factors [@Gray2012; @Yam2021].
 
-One previous study by @Saygin2012 measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
+One previous study by @Saygin2012 measured functional magnetic resonance imaging (fMRI) responses to moving stimuli designed to elicit an uncanny valley effect.
 They found repetition suppression effects^[Repetition suppression is a phenomenon in which the neural response to repeated presentations of identical or similar stimuli is reduced relative to the response on the first presentation.] in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
@@
 
-Our aim was to further investigate neural correlates of the uncanny valley effect.
+Our aim was to further investigate neural correlates of the uncanny valley effect, with the expectation that increased understanding will aid efforts to generate more convincingly human robots and avatars in the future.
 We achieved this through two EEG experiments, in which we measured neural responses to static images.
+Although previous studies focus on dynamic stimuli, static images allow for a more precise investigation of the neural mechanisms underlying the uncanny valley effect, particularly by eliminating motion-related confounds.
 In the first experiment, the stimuli were still images of humans, machine-like robots, and human-like robots (see Figure \ref{fig:stimexamples}a).
@@
 Halloween masks), and wearing hyper-realistic silicone masks [@Sanders2017] (see Figure \ref{fig:stimexamples}b).
-Rather than focus on specific ERP components, we use a multivariate pattern classification approach to identify time windows in which information in the EEG signal can be used to distinguish between pairs of conditions.
+Rather than focus on specific ERP components, we use a multivariate pattern classification approach (a machine learning technique in which an algorithm is trained to decode the neural responses) to identify time windows in which information in the EEG signal can be used to distinguish between pairs of conditions.
 Our rationale is that timepoints where signals evoked by human faces can be distinguished from those evoked by human-like robots, or hyper-realistic masks, are candidates for a neural signature of the uncanny valley effect.
@@
 Images shown here were taken from a variety of sources that permit reuse in academic contexts and in most cases were not part of the stimulus set from the experiments.
-The silicone mask image was taken by the authors, and was used in Experiment 2.", fig.align="center", out.width='80%', echo=FALSE}
+The silicone mask image was taken by the authors (subject: RJ, image credit: JGS), and was used in Experiment 2.
+The individual in this manuscript has given written informed consent (as outlined in PLOS consent form) to publish these case details (i.e.
+this image).", fig.align="center", out.width='80%', echo=FALSE}
 
@@
 Written informed consent was collected before each experiment began, and all procedures were approved by the Ethics committee of the Department of Psychology at the University of York.
+Data collection for Experiment 1 ran from 14th July to 15th September 2022, and data collection for Experiment 2 ran from 12th October 2017 to 14th February 2018.
 
@@
 The backgrounds of these images were more heterogeneous, and showed the natural surroundings of the subject.
-In both experiments, images involved examples of both genders, and of varied ethnic backgrounds.
+While the image backgrounds differed across experiments, we hypothesize that the primary task was not affected, as participants focused on the foreground stimuli.
+In both experiments, images included examples of both genders, and of varied ethnic backgrounds.
 
@@
 After each response there was a random duration blank period with a mean duration of 1000ms and a standard deviation of 200ms.
+Durations were chosen to provide sufficient information for judgment while avoiding task fatigue.
+Randomized blank periods were designed to reduce carryover effects and prevent anticipatory biases.
 Each block lasted around 6 minutes.
@@
 We capped infinite d-prime values (which occur e.g.
-when the hit rate is 1) at an arbitrary ceiling of 5.
+when the hit rate is 1) at an arbitrary ceiling of 5 to prevent outliers from skewing the results, following established conventions in signal detection theory.
 We log transformed the reaction times (which typically have positive skew) and performed all averaging and statistical analysis on the logarithmic values.
@@
 Our attempts to clean up the data from these participants using independent components analysis were unsuccessful.
-Their behavioural data were unaffected, and therefore still included in the analysis.
+Their behavioural data were unaffected, and are therefore still included in the analysis.
 
@@
 The resulting Bayes factor score is a summary of the evidence in favour of either the null hypothesis (that the waveforms are equal) or the alternative hypothesis (that they differ).
-We use the heuristics proposed by @Jeffreys1961 that Bayes factors >3 ($log_{10}BF_{10}$ > 0.5) constitute some evidence supporting the alternative hypothesis, factors >10 ($log_{10}BF_{10}$ > 1) constitute strong evidence, and factors >30 ($log_{10}BF_{10}$ > 1.5) constitute very strong evidence.
-
-Multivariate pattern analysis was conducted by training a linear support vector machine algorithm [LibSVM, @Chang2011] to discriminate between patterns of activity across electrodes at a specific time point.
+We use the heuristics proposed by Jeffreys @Jeffreys1961 that Bayes factors >3 ($log_{10}BF_{10}$ > 0.5) constitute some evidence supporting the alternative hypothesis, factors >10 ($log_{10}BF_{10}$ > 1) constitute strong evidence, and factors >30 ($log_{10}BF_{10}$ > 1.5) constitute very strong evidence.
+
+Multivariate pattern analysis (MVPA) was conducted by training a linear support vector machine algorithm [LibSVM, @Chang2011] to discriminate between patterns of activity across electrodes at a specific time point.
+MVPA is a statistical technique that involves training a machine learning algorithm to identify patterns in data, and then testing its accuracy at classifying unseen data; in EEG analysis above-chance classification is considered evidence of distinct patterns of neural activity between two conditions.
 Previous work has indicated that EEG data do not typically require more complex nonlinear algorithms [@Grootswagers2017].
@@
 The difference between androids and humans ($log_{10}BF_{10} =$ `r round(log10(bfcontrasts[3]),digits=2)`) was also very substantial.
+The higher d' values for robots (Figure \ref{fig:RobotsData}a) could indicate that these stimuli are more visually salient.
 
@@
 Panel (c) shows the grand mean ERP across all participants and conditions, pooled across electrodes P6, P8, PO6 and PO8 (see inset).
+The P100 is a positive evoked potential occuring around 100ms after onset of a visual stimulus, associated with the initial (low level) visual response; the N170 is a negative potential at 170ms that is often associated with faces; the P200 is a further positive potential linked to attention and stimulus discrimination.
 The shaded region around the curve illustrates the 95\\% confidence interval, and the grey rectangle at the foot indicates the stimulus duration.", fig.align="center", echo=FALSE}
@@
 We also conducted multivariate pattern analysis independently at each time-point for the same two comparisons.
-The evoked responses for human and robot images caused sufficiently distinct patterns of voltages across the scalp that the pattern classifier could distinguish them from around 100 ms following stimulus onset, with accuracy up to `r round(100*max(meanMVPA[2,]),digits=0)`\% correct (see Figure \ref{fig:RobotsMVPA}c).
+The evoked responses for human and robot images caused sufficiently distinct patterns of voltages across the scalp that the pattern classifier could distinguish between them from around 100 ms following stimulus onset, with accuracy up to `r round(100*max(meanMVPA[2,]),digits=0)`\% correct (see Figure \ref{fig:RobotsMVPA}c).
 Bayes factors exceeded 30 for much of the time window between 100 and 800 ms, indicating that the decoding was meaningfully above chance performance (50\% correct).
@@
 Classification accuracy had an initial peak around 100ms that provided compelling evidence for above chance classification (BF>30), and a later region of above-chance classification between 500 and 700ms.
+The early time window likely reflects rapid processing of low-level visual features, such as edges or color contrasts, consistent with P100 and N170 components, whereas the later time window may involve higher-level cognitive processes, such as evaluating emotional content or judging authenticity.
 In the Discussion we speculate that these two time periods might correspond to distinct types of signal associated with the uncanny valley.
+More generally, the high classification accuracy for human vs.
+robot stimuli may be attributed to the salient mechanical elements of robots, whereas the lower accuracy for humanoids reflects their ambiguous human-like appearance, leading to confusion.
 
@@
 We also confirmed that android images were perceived more negatively than either human or robot images, and that silicone masks were perceived as more uncanny than human faces.
-The similarity in results across our two experiments is striking and constitutes an internal conceptual replication of our main findings.
+The similarity in results across our two experiments is striking and constitutes an internal conceptual replication of our main findings, suggesting that the neural characteristics of the uncanny valley effect are generalizable across stimulus categories.
 
 The early time window when pattern classification is above chance corresponds approximately to the P100 and N170 components of the ERP.
+The P100 is typically associated with low-level visual responses, and is affected by contrast and spatial frequency content of an image.
+The N170 component is most often associated with faces, though is also observed for other image categories, and there is still debate about its precise function [@Thierry2007; @Hong2022].
 Similar early components have also been investigated in other ERP studies on the uncanny valley effect [@Schindler2017; @Mustafa2016], and comparing human and robot faces [@Geiger2021].
 This time window is unlikely to be modulated substantially by top-down influences, so we attribute the early component to image-based differences between stimulus categories [@Coggan2016].
-ERP components in later time windows have also been studied in previous work [@Urgen2018; @Mustafa2017; @Cheetham2015].
+ERP components in later time windows have also been studied in previous work [@Urgen2018; @Mustafa2017; @Cheetham2015], and may reflect cognitive processing stages, such as determining whether a stimulus conforms to categorical expectations.
 Differences between stimulus categories at these times are more amenable to top-down influences, and most likely involve higher brain areas outside of occipital cortex.
@@
 
-Another increasingly common situation that triggers the 'uncanny valley' experience is in the domain of computer-generated images and movies.
+Another increasingly common situation that triggers the 'uncanny valley' experience is in the domain of computer-generated images and movies [@Moshel2022; @Gu2023].
 Artificial intelligence algorithms are now able to generate images and movies based on text prompts (for example "a picture of a girl flying a kite in a field") that often include human subjects.
@@
 These findings suggest the importance of both bottom up and top down influences on the subjective experience of the uncanny valley.
-
-# Acknowledgements
-
-SF was funded by a YorRobots Venables internship.
-JGS was funded by the Economic and Social Research Council (Studentship ES/J500215/1) and Prins Bernhard Cultuurfonds (grant E/30/30.13.0630/HVH/IE).
-Also supported by BBSRC grant BB/V007580/1 awarded to DHB.
+Future work might extend these findings to more dynamic stimuli, and explore potential applications for improving android and avatar generation.
 

### 2025-01-12 manuscript.tex
Fix autobuild
Implemented reviewer suggestions

@@
 However at present relatively little is known about the neural underpinnings of the uncanny valley effect {[}for a recent review, see 4{]}.
+In particular, the root of the uncanny valley effect remains debated: does it arise primarily from bottom-up sensory conflicts, or from higher-level cognitive processes?
+Resolving this question is critical to understanding its fundamental mechanisms.
 
@@
 For example, areas of the occipital lobe {[}6{]} and fusiform gyrus {[}7{]} respond more to faces than non-face stimuli, and sections of extrastriate cortex are responsive to bodies {[}8{]}.
-There are also event-related potential (ERP) signals associated with face and body stimuli, though their precise role is still debated {[}9,10{]}.
+There are also electromagnetic event-related potential (ERP) signals associated with face and body stimuli, though their precise role is still debated {[}9,10{]}.
 It seems highly likely that `uncanny' images will activate these same processes, yet it is unclear whether the initial cause of the sense of unease they produce occurs at bottom-up sensory stages {[}11--13{]} or is modulated by more top-down cognitive factors {[}14,15{]}.
 
-One previous study by {[}16{]} measured fMRI responses to moving stimuli designed to elicit an uncanny valley effect.
+One previous study by {[}16{]} measured functional magnetic resonance imaging (fMRI) responses to moving stimuli designed to elicit an uncanny valley effect.
 They found repetition suppression effects\footnote{Repetition suppression is a phenomenon in which the neural response to repeated presentations of identical or similar stimuli is reduced relative to the response on the first presentation.} in action-specific brain regions responding to movies of androids that had a biological appearance, but mechanical motion.
@@
 
-Our aim was to further investigate neural correlates of the uncanny valley effect.
+Our aim was to further investigate neural correlates of the uncanny valley effect, with the expectation that increased understanding will aid efforts to generate more convincingly human robots and avatars in the future.
 We achieved this through two EEG experiments, in which we measured neural responses to static images.
+Although previous studies focus on dynamic stimuli, static images allow for a more precise investigation of the neural mechanisms underlying the uncanny valley effect, particularly by eliminating motion-related confounds.
 In the first experiment, the stimuli were still images of humans, machine-like robots, and human-like robots (see Figure \ref{fig:stimexamples}a).
 In the second experiment we aimed to generalise the finding by using images of people wearing no masks, wearing obvious masks (e.g.~Halloween masks), and wearing hyper-realistic silicone masks {[}18{]} (see Figure \ref{fig:stimexamples}b).
-Rather than focus on specific ERP components, we use a multivariate pattern classification approach to identify time windows in which information in the EEG signal can be used to distinguish between pairs of conditions.
+Rather than focus on specific ERP components, we use a multivariate pattern classification approach (a machine learning technique in which an algorithm is trained to decode the neural responses) to identify time windows in which information in the EEG signal can be used to distinguish between pairs of conditions.
 Our rationale is that timepoints where signals evoked by human faces can be distinguished from those evoked by human-like robots, or hyper-realistic masks, are candidates for a neural signature of the uncanny valley effect.
@@
 Images shown here were taken from a variety of sources that permit reuse in academic contexts and in most cases were not part of the stimulus set from the experiments.
-The silicone mask image was taken by the authors, and was used in Experiment 2.}\label{fig:stimexamples}
+The silicone mask image was taken by the authors (subject: RJ, image credit: JGS), and was used in Experiment 2.
+The individual in this manuscript has given written informed consent (as outlined in PLOS consent form) to publish these case details (i.e.
+this image).}\label{fig:stimexamples}
 \end{figure}
@@
 For the robot and mask conditions, the hit rate was the proportion of robot/mask images correctly identified as not being human, and the false alarm rate was the proportion of human images that were incorrectly judged as being non-human (note that this means the false alarm rate was the same for the robot and android conditions, and for the silicone and Halloween mask conditions).
-We capped infinite d-prime values (which occur e.g.~when the hit rate is 1) at an arbitrary ceiling of 5.
+We capped infinite d-prime values (which occur e.g.~when the hit rate is 1) at an arbitrary ceiling of 5 to prevent outliers from skewing the results, following established conventions in signal detection theory.
 We log transformed the reaction times (which typically have positive skew) and performed all averaging and statistical analysis on the logarithmic values.
@@
 The resulting Bayes factor score is a summary of the evidence in favour of either the null hypothesis (that the waveforms are equal) or the alternative hypothesis (that they differ).
-We use the heuristics proposed by {[}27{]} that Bayes factors \textgreater3 (\(log_{10}BF_{10}\) \textgreater{} 0.5) constitute some evidence supporting the alternative hypothesis, factors \textgreater10 (\(log_{10}BF_{10}\) \textgreater{} 1) constitute strong evidence, and factors \textgreater30 (\(log_{10}BF_{10}\) \textgreater{} 1.5) constitute very strong evidence.
+We use the heuristics proposed by Jeffreys {[}27{]} that Bayes factors \textgreater3 (\(log_{10}BF_{10}\) \textgreater{} 0.5) constitute some evidence supporting the alternative hypothesis, factors \textgreater10 (\(log_{10}BF_{10}\) \textgreater{} 1) constitute strong evidence, and factors \textgreater30 (\(log_{10}BF_{10}\) \textgreater{} 1.5) constitute very strong evidence.
 
-Multivariate pattern analysis was conducted by training a linear support vector machine algorithm {[}LibSVM, 28{]} to discriminate between patterns of activity across electrodes at a specific time point.
+Multivariate pattern analysis (MVPA) was conducted by training a linear support vector machine algorithm {[}LibSVM, 28{]} to discriminate between patterns of activity across electrodes at a specific time point.
+MVPA is a statistical technique that involves training a machine learning algorithm to identify patterns in data, and then testing its accuracy at classifying unseen data; in EEG analysis above-chance classification is considered evidence of distinct patterns of neural activity between two conditions.
 Previous work has indicated that EEG data do not typically require more complex nonlinear algorithms {[}29{]}.
@@
 The difference between androids and humans (\(log_{10}BF_{10} =\) 5.58) was also very substantial.
+The higher d' values for robots (Figure \ref{fig:RobotsData}a) could indicate that these stimuli are more visually salient.
 
@@
 Panel (c) shows the grand mean ERP across all participants and conditions, pooled across electrodes P6, P8, PO6 and PO8 (see inset).
+The P100 is a positive evoked potential occuring around 100ms after onset of a visual stimulus, associated with the initial (low level) visual response; the N170 is a negative potential at 170ms that is often associated with faces; the P200 is a further positive potential linked to attention and stimulus discrimination.
 The shaded region around the curve illustrates the 95\% confidence interval, and the grey rectangle at the foot indicates the stimulus duration.}\label{fig:RobotsData}
@@
 We also conducted multivariate pattern analysis independently at each time-point for the same two comparisons.
-The evoked responses for human and robot images caused sufficiently distinct patterns of voltages across the scalp that the pattern classifier could distinguish them from around 100 ms following stimulus onset, with accuracy up to 72\% correct (see Figure \ref{fig:RobotsMVPA}c).
+The evoked responses for human and robot images caused sufficiently distinct patterns of voltages across the scalp that the pattern classifier could distinguish between them from around 100 ms following stimulus onset, with accuracy up to 72\% correct (see Figure \ref{fig:RobotsMVPA}c).
 Bayes factors exceeded 30 for much of the time window between 100 and 800 ms, indicating that the decoding was meaningfully above chance performance (50\% correct).
@@
 Classification accuracy had an initial peak around 100ms that provided compelling evidence for above chance classification (BF\textgreater30), and a later region of above-chance classification between 500 and 700ms.
+The early time window likely reflects rapid processing of low-level visual features, such as edges or color contrasts, consistent with P100 and N170 components, whereas the later time window may involve higher-level cognitive processes, such as evaluating emotional content or judging authenticity.
 In the Discussion we speculate that these two time periods might correspond to distinct types of signal associated with the uncanny valley.
+More generally, the high classification accuracy for human vs.~robot stimuli may be attributed to the salient mechanical elements of robots, whereas the lower accuracy for humanoids reflects their ambiguous human-like appearance, leading to confusion.
 
@@
 We also confirmed that android images were perceived more negatively than either human or robot images, and that silicone masks were perceived as more uncanny than human faces.
-The similarity in results across our two experiments is striking and constitutes an internal conceptual replication of our main findings.
+The similarity in results across our two experiments is striking and constitutes an internal conceptual replication of our main findings, suggesting that the neural characteristics of the uncanny valley effect are generalizable across stimulus categories.
 
 The early time window when pattern classification is above chance corresponds approximately to the P100 and N170 components of the ERP.
+The P100 is typically associated with low-level visual responses, and is affected by contrast and spatial frequency content of an image.
+The N170 component is most often associated with faces, though is also observed for other image categories, and there is still debate about its precise function {[}9,10{]}.
 Similar early components have also been investigated in other ERP studies on the uncanny valley effect {[}31,32{]}, and comparing human and robot faces {[}30{]}.
 This time window is unlikely to be modulated substantially by top-down influences, so we attribute the early component to image-based differences between stimulus categories {[}33{]}.
-ERP components in later time windows have also been studied in previous work {[}17,34,35{]}.
+ERP components in later time windows have also been studied in previous work {[}17,34,35{]}, and may reflect cognitive processing stages, such as determining whether a stimulus conforms to categorical expectations.
 Differences between stimulus categories at these times are more amenable to top-down influences, and most likely involve higher brain areas outside of occipital cortex.
@@
 
-Another increasingly common situation that triggers the `uncanny valley' experience is in the domain of computer-generated images and movies.
+Another increasingly common situation that triggers the `uncanny valley' experience is in the domain of computer-generated images and movies {[}39,40{]}.
 Artificial intelligence algorithms are now able to generate images and movies based on text prompts (for example ``a picture of a girl flying a kite in a field'') that often include human subjects.
@@
 These findings suggest the importance of both bottom up and top down influences on the subjective experience of the uncanny valley.
-
-\section{Acknowledgements}\label{acknowledgements}
-
-SF was funded by a YorRobots Venables internship.
-JGS was funded by the Economic and Social Research Council (Studentship ES/J500215/1) and Prins Bernhard Cultuurfonds (grant E/30/30.13.0630/HVH/IE).
-Also supported by BBSRC grant BB/V007580/1 awarded to DHB.
+Future work might extend these findings to more dynamic stimuli, and explore potential applications for improving android and avatar generation.
 
@@
 
+\bibitem[\citeproctext]{ref-Moshel2022}
+\CSLLeftMargin{39. }%
+\CSLRightInline{Moshel ML, Robinson AK, Carlson TA, Grootswagers T.
+Are you for real?
+Decoding realistic AI-generated faces from neural activity.
+Vision Res.
+2022;199: 108079.
+doi:\href{https://doi.org/10.1016/j.visres.2022.108079}{10.1016/j.visres.2022.108079}}
+
+\bibitem[\citeproctext]{ref-Gu2023}
+\CSLLeftMargin{40. }%
+\CSLRightInline{Gu Z, Jamison K, Sabuncu MR, Kuceyeski A.
+Human brain responses are modulated when exposed to optimized natural images or synthetically generated images.
+Commun Biol.
+2023;6: 1076.
+doi:\href{https://doi.org/10.1038/s42003-023-05440-7}{10.1038/s42003-023-05440-7}}
+
 \end{CSLReferences}

### 2025-03-19 manuscript.Rmd
Updated readme with citation information

@@
 output:
+  word_document: default
   bookdown::pdf_document2:
@@
     keep_tex: yes
-  word_document: default
   pdf_document:
